### 2018-01-26 paper/draft.tex
add some paper files

\documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{hyperref}

\begin{document}

\title{Direct Entropy Measurement in a Mesoscopic Quantum System}
\author{Nikolaus Hartman}
\email{nik.hartman@gmail.com}
\thanks{The raw data and Python code used for the figures and analysis can be found at \url{https://github.com/nikhartman/spin_entropy}}
\affiliation{University of British Columbia, Vanouver, BC, Canada}
\author{Saeed Fallahi}
\affiliation{Purdue University, Lafayette, IN, USA}
\author{Geoffrey C. Gardner}
\affiliation{Purdue University, Lafayette, IN, USA}
\author{Christian Olsen}
\affiliation{University of British Columbia, Vanouver, BC, Canada}
\author{Silvia Folk}
\affiliation{University of British Columbia, Vanouver, BC, Canada}
\author{Mohammad Samani}
\altaffiliation{The Hospital for Sick Children, Toronto, ON, Canada}
\altaffiliation{Fields Institute for Research in Mathematical Sciences, Toronto, ON, Canada}
\affiliation{University of British Columbia, Vanouver, BC, Canada}
\author{Michael Manfra}
\affiliation{Purdue University, Lafayette, IN, USA}
\author{Joshua Folk}
\affiliation{University of British Columbia, Vanouver, BC, Canada}
\date{\today}

\begin{abstract}

Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.  Such measurements are typically based on bulk properties, such as heat capacity, that are straightforward to observe in macroscopic samples but exceedingly difficult to access in mesoscopic systems, sometimes consisting of just a few electrons. Taking advantage of a well-known Maxwell relation, we realize a mesoscopic geometry in a GaAs heterostructure in which entropy-to-charge conversion enables an entropy measurement of quantum states down to the single electron level. As a demonstration of the efficacy of this method, the entropy of the first few-electron spin states in a gate-defined GaAs quantum dot are measured. The entropy of a single spin ($k_B \ln{2}$) is measured within 8\% accuracy, as is the entropy arising at the magnetic field-driven singlet-triplet crossing for two electrons.

\end{abstract}

\maketitle

%%%%%%% intro material %%%%%%%%%
The thermodynamic properties of electronic systems can offer important insights into the nature of their ground states, and probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.  Systems that are difficult to clearly identify through standard conductance measurements may be studied more in depth if a thermodynamic measurement can be made. For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, are exceedingly difficult to identify from conductance signatures. However, an entropy measurement could clearly distinguish Abelian from non-Abelian quasiparticles \cite{Cooper2009, Smirnov2015}.  Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}. A more direct test for the two-channel Kondo state would be a confirmation of its entropy ($\frac{1}{2} k_B \ln{2}$), that should remain down to arbitrarily low temperatures \cite{Alkurtass2016}.

%%% figure 1 %%%
\begin{figure}[!]
        \includegraphics[width=1.0\columnwidth]{../figures/figure_1_no-annotation.pdf}
        \caption{\label{fig:fig1}(a) Scanning electron micrograph of a device similar to the one measured, showing electrostatic gates (blue) used to define a circuit in the 2D electron gas. Grey gates are unused (grounded).  A \SI{1}{\milli\metre}-long channel is formed between the parallel gates running vertically down the image. The channel can be heated by driving current through the constriction on the left.  A 200nm diameter quantum dot is tunnel-coupled to the right side of the channel. Occupation of the dot is monitored by a capacitively-coupled charge sensor. Squares show the locations of ohmic contacts to the 2DEG. (b) Calculated charge sensor signal showing a single transition from $N \rightarrow N+1$ electrons at two temperatures ($T_{Red} > T_{Blue}$). (c) Change in the charge sensor signal with respect to temperature. The asymmetry in peak height arises from the shift in $V_0$ due to the change in entropy, $dS$, between the $N$ and $N+1$ electron states. In the case of $dS=0$, $dg$ is anti-symmetric about $V_0$.}
\end{figure}

While measurements of heat capacity are effective in probing the entropy of macroscopic 3D samples, the heat capacities of single electrons or quasiparticles are much too small to measure directly; even the 2D sheet of quasiparticles in $\nu = \frac{5}{2}$ fractional quantum Hall samples has a heat capacity that vanishes in comparison to the host crystal.  Rather than attempt to resolve such infinitesimal signals, the problem can be avoided by converting a change in entropy to changes in a more easily measured quantity, charge.  Our approach is analogous to the milestone of spin-to-charge conversion, first demonstrated in GaAs quantum dots in 2004, by which undetectably-small magnetic moments of a single spin were transformed into thepresence or absence of an electron charge, which is easily detected4 \cite{Elzerman2004, Ono2004}.

In order to accomplish this entropy to charge conversion, we make use of the Maxwell relation
%
\begin{align}
\label{eqn:max}
        \left(\frac{\partial \mu}{\partial T}\right)_{p,N} &= -\left(\frac{\partial S}{\partial N}\right)_{p,T}
\end{align}
%
that connects changes in entropy, $S$, (as well as particle number $N$ and temperature $T$) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control. The fixed pressure condition is met by working well below the Fermi temperature, $T_F \sim$\SI{5}{\kelvin}, where the pressure is simply the degeneracy pressure \cite{Landau1969}. Refs.~\onlinecite{Cooper2009} and ~\onlinecite{Ben-Shach2013} propose schemes to measure the entropy derivative, $\frac{\partial S}{\partial N}$, of the $\nu = \frac{5}{2}$ state via this Maxwell relation, detecting changes in the quasiparticle chemical potential with temperature.  Our work builds on these ideas to measure the entropy of the few-electron ground states of a quantum dot. Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states studied here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}. This work demonstrates a direct thermodyanmic measurement on a simple few-particle system; the method can be easily extended as a probe into the nature of more exotic systems ,such as topologically non-trivial Majorana and other non-Abelian states.

The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a realizes an electron reservoir (central region) in thermal equilibrium with a few-electron quantum dot coupled to its right side, where tunneling between the two is measured using a charge sensing QPC capacitively coupled to the dot \cite{Staring2007, Frolov2009, Thierschmann2015}. The number of electrons on the dot can be tuned using the gate voltage, $V_G$. An electron is added to an $N$ electron dot when the chemical potential to add an electron, $\mu_{N+1}$ (proportional to $V_G$), drops below the Fermi level of the reservoir, $E_F$.  Figure 1b illustrates a such a transition, as measured by the charge sensor conductance, as a function of $V_G$. The gate voltage corresponding to midpoint of the transition, $V_0$, marks the chemical potential where the probabilties of finding $N$ or $N+1$ electrons on the dot are equal. This transition is thermally broadened by the reservoir temperature $T_{res}$. Additionally, an entropy change from the $N$ to $N+1$ ground states of the dot can shift the midpoint of the transition, $V_0$, by changing the chemical potential on the dot as in Eq.~\ref{eqn:max}.  Detecting the shift in $V_0$ with respect to temperature (${\propto}\frac{\partial \mu}{\partial T}$), amounts to a measurement of the entropy difference $dS$ between the $N$ to $N+1$ ground states ($dN=1$).  In practice, the shift in $V_0$ is measured by oscillating $T_{res}$ and monitoring changes in $g_{sens}$ with a lockin amplifier.  Consider the charge transitions in Fig.~\ref{fig:fig1}b, if the warmer transition is not only broadened but shifted ($dS\neq0$), the change in $g_{sens}$ is asymmetric as shown in Fig.~\ref{fig:fig1}c; if the warmer transition is broadened but not shifted with respect to the cooler one ($dS=0$), the lineshape is anti-symmetric.

An explanation based on detailed balance is helpful in understanding how a shift in $\mu_{N+1}$ (relative to $E_F$) relates to entropy. Tunneling between the dot and reservoir is possible when the chemical potential to add an electron, $\mu_{N+1}$, is within ${\sim}3.5 k_B T$ of Fermi level of the reservoir. Away from that window, tunneling is suppressed due to a lack of available states in the reservoir. To illustrate how the tunnel rates, $\Gamma_{in}=\Gamma_{N\rightarrow N+1}$ and $\Gamma_{out}=\Gamma_{N+1\rightarrow N}$ depend on degeneracy, consider the filling of the first electron state. The 1-electron ground state has a degeneracy of 2 due to a single, unpaired spin-$\frac{1}{2}$; electrons tunneling into this state have both spin-up and -down states available. Conversely, an electron tunneling off of the dot must tunnel into a state with its same spin, that is, only half of the reservoir states are available to it. As a result, $\Gamma_{in} = 2\Gamma_{out}$ when $\mu_{N+1}=E_F$. Extending this logic to a general case gives the same results as derived from detailed balance \cite{Gustavsson2009}, 
%
\begin{align}
	\Gamma_{in} &=  g_{N+1} \Gamma f(E_F - \mu_{N+1}) \label{eqn:gin}\\
	\Gamma_{out} &= g_{N} \Gamma [1 - f(E_F - \mu_{N+1})] \label{eqn:gout}
\end{align}
%
where $\Gamma$ is a coupling constant and $g_{N/N+1}$ are the degeneracies of the $N$ and $N+1$ electron states.. The midpoint of the transition between the $N$ and $N+1$ electon states, measured by the charge sensor, occurs when the $\Gamma_{in} = \Gamma_{out}$. It is clear from Eqs.~\ref{eqn:gin} and \ref{eqn:gout}, that in the case $g_{N}=g_{N+1}$, $\Gamma_{in} = \Gamma_{out}$ when $\mu_{N+1} = E_F$. However, if the two occupation states differ in their degeneracy, the midpoint of the transition shifts away from $\mu_{N+1}=E_F$. Thermal broadening of the Fermi functions in Eqs.~\ref{eqn:gin} and \ref{eqn:gout} means that the chemical potential at which $\Gamma_{in} = \Gamma_{out}$ depends on $T$ as well as $g_{N/N+1}$. By measuring $dV_0$ ($d_\mu$) as a function of $dT$, the ratio $g_{N+1}/g_{N}$ can be determined, which is related to $dS$ through the Boltzmann entropy. The relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}.  The thermal technique presented here extends the measurement of entropy (degeneracy) to a wider set of applications, where the tunneling process may not be convenient or even possible to observe directly.

%%% fab/measurement details %%%
The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.   Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, then \SI{10}{\nano\metre} of $\mathrm{HfO_2}$ was deposited via atomic layer deposition to improve the gating stability to the device. Electron beam lithography followed by evaporation of \SI{20}{\nano\metre} of Ti/Au defined the fine gate structures, including the \SI{200}{\nano\metre} diameter quantum dots. The measurement was carried out in an dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.

%%%%%%%%%%  current edits end here  %%%%%%%%%%%%%

%%% figure 2 %%%
\begin{figure}[!]
        \includegraphics[width=1.0\columnwidth]{../figures/figure_2.pdf}
        \caption{\label{fig:fig2}(a) Charge sensor data for $N=0 \rightarrow 1$ at 100 and 160mK. Temperature is set by DC current through the QPC heater. (b) Derivative of the charge sensor signal with $dT \sim 60mK$. Fits to $dg$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a fucntion of mixing chamber temperature. The highlighted, linear region is where all the data discussed were measured. Fitting a straight line to this data, the lever arm $\alpha$ is calculated. (d) $\Theta$ as a function of DC current through the QPC heater. The linear fit is used to convert between $I_{heat}$ and $dT$, with $R_{QPC}$ fixed at 20$k\Omega$ (e) Change in entropy as a function of AC current through the QPC heater. Top axis shows corresponding $dT$. (f) Raw data from which $dS / k_B$ in (c), and the line cut in (b) were extracted.}
\end{figure}

To make a  measurement of the quantum dot entropy, the right dot was coupled to the reservoir on the source (left) side, with the drain (right) side of the dot closed. The charge sensing QPC  was tuned to a conductance of ${\sim}e^2/h$. A small DC voltage bias was applied and the measured current was used to calculate the sensor conductance.  Assuming the source barrier is in the limit where single electron transitions ($\Gamma_{In/Out}$) are only broadened by the temperature of the reservoir (discussed further in Fig. \ref{fig:fig2}c, the charge sensor conductance takes the form,
%
\begin{align}
\label{eqn:g}
        g_{sens}(V,\Theta) &= G_0 \tanh\left(\frac{V-V_0(\Theta)}{2\Theta}\right)  \\
                        &\quad + G_1\left[V-V_0(\Theta)\right] + G_2 \nonumber
\end{align}
%
where $\Theta = \frac{k_B T}{\alpha e}$, $\alpha$ is the lever arm for the quantum dot plunger gate, and $G_1$ is determined by the cross capacitance between the sensor gates and the plunger gate.

The temperature of the electron reservoir was varied by applying an AC current through the heating QPC on the left side of the channel. Fluctuations in $g_{sens}$ were measured at $2f_{Heat}$ using a lock-in amplifier; the temperature of the reservoir goes as $dT^2 \sim P^{AC}_{Heat} \sim \sin^2(2\omega t)$. Taking a derivative of Eq. \ref{eqn:g} with respect to temperature gives the change in conductance, $dg_{sens}$, as measured by the lock-in amplifier,
%
\begin{align}
\label{eqn:dg}
        dg_{sens}(V, \Theta) &\propto \left[ \frac{V-V_0(\Theta)}{2\Theta} + \delta \right]\times \\
        				      &\quad\cosh^{-2}\left(\frac{V-V_0(\Theta)}{2\Theta}\right) \nonumber
\end{align}
%
where $\delta=\frac{\partial V_0}{\partial \Theta}$. By using the lever arm to convert $V_0$ to chemical potential $\mu$, and recalling Eq. \ref{eqn:max}, the parameter $\delta$ can be related to the change in entropy,
%
\begin{align}
\label{eqn:delta}
        \delta &= \frac{\partial V_0}{\partial \Theta} = 
        \frac{1}{k_B} \frac{\partial \mu}{\partial T} = 
        -\frac{1}{k_B} \frac{\partial S}{\partial N}
\end{align}
%

The entropy measurement requires no further calibration to extract the desired results from the $dg$ fits. However, it is necessary to ensure that the range of temperatures and energies fit the analysis. To begin, the dot is depleted by tuning the plunger gate and identifying the empty dot using the charge sensor. Typical charge sensor curves for the $N=0 \rightarrow 1$ transision are shown in Fig. \ref{fig:fig2}. The width of the charge sensor signal, determined by fitting Eq. \ref{eqn:g}, is measured as a function of the mixing chamber temperature in Fig. \ref{fig:fig2}c). At a sufficiently high temperature, $T_{electron}=T_{MC}$, and the transition width is determined only by $T_{MC}$ (highlighted region in Fig. \ref{fig:fig2}c). A line fit to $\Theta = \frac{k_B T_{MC}}{\alpha e}$ is used to determine $\alpha$. The remainder of the measurements are performed in the linear region of Fig. \ref{fig:fig2}c at $T_{MC} = 100mK$, where Eqs. \ref{eqn:g} and \ref{eqn:dg} are valid. Fig. \ref{fig:fig2}d shows the calibration of $dT$ as a function of DC current through the QPC heater ($P_{Heat} = I^2_{Heat} R_{QPC}$). Using $\alpha$ to convert from $\Theta$ to $T_{electron}$, the linear fit Fig. \ref{fig:fig2}d gives the the conversion from $I_{Heat}$ to $dT$. To avoid thermally accessing excited states of the dot it must be true that $k_B dT \ll \Delta$ where $\Delta$ is the level spacing between the ground and first excited states; which holds for all transitions investigated.

Data in Fig. \ref{fig:fig2}b show the change in quantum dot entropy determined directly from the lock-in signal, $dg_{sens}$. Fits to Eq. \ref{eqn:dg} are shown for $\delta=0$ (dashed) and a best fit to $\delta$ (solid). It is clear from these fits, $\delta$ is necessary to properly fit the asymmetry in peak height, with the best fit being $\delta \approx \ln{2}$. This is easily understood from the Boltzmann entropy. For an N-electron macrostate on the quantum dot, entropy is given by,
%
\begin{align}
\label{eqn:S}
        S &= k_B \ln{\Omega}
\end{align}
%
where $\Omega$ is the number of microstates available. The number of microstates is equal to the spin degeneracy of the ground state. For the 0-1 transition, this gives $dS =  k_B\ln{2} - k_B \ln{1} = k_B\ln{2}$.

Because $\delta$ is a fit parameter independent of $dT$, it is possible to extract the same $\delta$ value for a range of $dT$ ($I^{AC}_{Heat}$). Fig. \ref{fig:fig2}e shows that $dS$, as determined from $dg_{sens}$ fits, remains constant over a range of $dT$. Looking at the vertical scale on the right side of Fig. \ref{fig:fig2}e, the same shift in chemical potential on the dot is given in units of gate voltage shift per unit temperature change. This illustrates why the lock-in measurement was utilized; device stability and small signals made it difficult for the entropy to be determined directly from $g_{sens}$ using DC heating.

%%% figure 3 %%%
\begin{figure}
        \includegraphics[width=1.0\columnwidth]{../figures/figure_3.pdf}
        \caption{\label{fig:fig3}(a) Transport data through the quantum dot showing the $N=0 \rightarrow 1$ transition. The first excited state, near $V_{SD}$ = \SI{1}{\milli\electronvolt}, is well-above all other energy scales in the measurement. Dashed line shows where data in (b) are taken. (b) Fixed bias transport data ($V_{SD}$ = \SI{700}{\micro\electronvolt}) showing fits to the Zeeman splitting of the ground state energy. (c) Change in entropy, extracted from $dg$ fits, as a function of parallel field. The $N=0 \rightarrow 1$ and $2 \rightarrow 3$ are overlaid here to show the behavior is the same at low parallel field. (d) and (e) show characteristic $dg$ traces from which the data in (c) were extracted.}
\end{figure}

Fig. \ref{fig:fig3}c shows $dS$ as a function of parallel field for the 0-1 (and 2-3) electron transitions. The spin-$\frac{1}{2}$ degeneracy of the 1-electron ground state is lifted as the field increases to \SI{\pm5}{\tesla}.  As the Zeeman splitting, measured directly in Fig. \ref{fig:fig2}b, lifts the spin degeneracy, the entropy of the 1-electron state goes to zero. The 2-3 electron transition behaves similarly at low fields.  The 2-electron ground state is the spin singlet, and the 3-electron ground state is same singlet with an additional unpaired electron, with degeneracy of 2, as in the 1-electron case. Below \SI{5}{\tesla} $g\mu_B B$ remains the largest energy scale, and no 3-electron excited states need be considered.

To understand the behavior of $dS$ as a function of magnetic field, Eq. \ref{eqn:S} can be rewritten as,
%
\begin{align}
\label{eqn:Sp}
        S &= k_B \sum_{i=\pm} p_{i}(B, T) \ln{ p_{i}(B,T) }
\end{align}
%
where $p_{i}(B, T)$ is the probabilty of the system being in the i$^{th}$ microstate at a given field and temperature. The 1 and 3-electron ground states have only a spin-$\frac{1}{2}$ degree of freedom at low field and $p_{i}(B, T)$ can be written as a two-level system,
%
\begin{align}
\label{eqn:p}
        p_{\pm}(B, T) &= \frac{1}{1+ e^{\mp \frac{g\mu_B B}{k_B T}}}
\end{align}
%
where $\pm$ represent the spin up/down states of the unpaired electron.

The dashed and solid lines in Fig \ref{fig:fig3}c show fits to $dS$ using Eqs. \ref{eqn:Sp} and \ref{eqn:p} for the 0-1 and 2-3 electron transitions, respectively. These fits allow for peak height, g-factor, and a vertical offset as free parameters; $T$ is fixed at the mixing chamber temperature. From these fits, $dS=0.92 \ln{2}$ and $g=-0.33$. The peak height, corresponding to $dS(B=0)$, deviates from the expected value because it is convoluted with the vertical offset, caused by the cross-capacitance between plunger and QPC gates. The discrepancy between $g$ and the result in Fig. \ref{fig:fig3}b, can be understood from the change in shape of the quantum dot when tuning between the open and closed drain configurations [citation?].

%%% figure 4 %%%
\begin{figure}
        \includegraphics[width=1.0\columnwidth]{../figures/figure_4.pdf}
        \caption{\label{fig:fig4}(a) (a) Transport data through the quantum dot showing the $N=1 \rightarrow 2$ transition. Singlet-triplet splitting is roughly \SI{300}{\micro\electronvolt} and depends on applied field. Dashed line shows where data in (b) are taken. (b) TFixed bias transport data ($V_{SD}$ = \SI{1250}{\micro\electronvolt}). The triplet level is split into T$_+$, T$_0$, and $T_{-}$ (not visible). At \SI[input-protect-tokens]{\sim 9}{\tesla} T$_+$ becomes degenerate with S. g-factor is determined using $T_0$ and $T_+$ fits. (c) Change in entropy, extracted from $dg$ fits, as a function of parallel field. As the field goes from 0 to 10T, entropy of the 2-electron state goes from $0  \rightarrow \ln{2}$, while the entropy of the 1-electron state goes from $\ln{2} \rightarrow 0$. (d), (e), and (f) show characteristic $dg$ traces from which the data in (c) was extracted.}
\end{figure}

The low field (\SI{<5}{\tesla}) results in Fig. \ref{fig:fig4}c can be understood as simply the inverse of Fig \ref{fig:fig3}c. The entropy of the 2-electron ground state remains $0$, in the spin-singlet state, and the entropy of the 1-electron ground state goes from $k_B\ln{2}$ to $0$ due to the Zeeman splitting seen in Fig. \ref{fig:fig3}b. At high field, the 1-electron ground state remains non-degenerate, while the 2-electron ground state picks up a degeneracy of 2 at \SI{9}{\tesla} as the singlet and triplet ($T_+$) levels cross. This confirms that the $dS$ signal can be related directly to a tunable degeneracy in the system. The same splittings in the quantum dot conductance data can be seen in Fig. \ref{fig:fig4}b.

The entropy signal for the 1-2 transition can be fit using Eq. \ref{eqn:p} as the probabilities for the 1-electron groundstates and the following probabilities for the 2-electron singlet-triplet states,
%
\begin{align}
\label{eqn:pst}
        p_{S/T}(B, T) &= \frac{1}{1+ e^{\mp \frac{g\mu_B B - \Delta_{ST}}{k_B T}}}
\end{align}
%
where $\Delta_{ST}$ is the singlet-triplet splitting. Looking at the width of the peaks in $dS$, it is clear that the g-factor changes, along with the singlet-triplet splitting, as the field is increased. Fitting the curve yields $g(B{=}0T)=-0.46$, $g(B{=}9T)=-0.31$, $\Delta_{ST}(B{=}9T)$ = \SI{240}{\micro\electronvolt}, $dS(B{=}0T) = 1.04\ln{2}$, and $dS(B{=}9T) = 1.01\ln{2}$. Each of these values is consistent with the dot transport data and the fits in Fig. \ref{fig:fig3}c.

The results presented in this work have confirmed the degeneracy of the few-electron ground states states, as calculated using only the spin degree of freedom. Magnetic field dependence of the entropy can be fit using simple spin statistics.  Additionally, a technique has been demonstrated to measure the entropy of few-particle states in mesoscopic devices. Future work may take advantage of this strategy to probe the statistics of non-trival electron and quasiparticle states.

%\acknowledgments
% Everyone I might acknowledge is currently an author. Consider moving someone here.

\bibliography{qdentropy}{}
\bibliographystyle{apsrev4-1}

\end{document}

### 2018-01-26 paper/draft.tex
edits...

@@
 
-%%%%%%%%%%  current edits end here  %%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-To make a  measurement of the quantum dot entropy, the right dot was coupled to the reservoir on the source (left) side, with the drain (right) side of the dot closed.
+%%% device setup %%%
+Using the gates on the right hand side of Fig~\ref{fig:fig1}a, the quantum dot was tuned such that there is a weak tunnel coupling to the reservoir on the source side with the drain side of the dot closed.
 The charge sensing QPC was tuned to a conductance of ${\sim}e^2/h$.
-A small DC voltage bias was applied and the measured current was used to calculate the sensor conductance.
+A small DC voltage bias was applied across the QPC and the measured current was used to calculate the sensor conductance.
+The reservoir temperature was controlled either by varying the fridge temperature or by Joule heating through the QPC on the left side of the channel.
+In the latter case, the QPC was fixed at \SI{20}{\kilo\ohms} and biased using an AC or DC current source.
+The Joule heating strategy gives fast control of the temperature (up to \SI{100}{\hertz}) while keeping the voltage drop across the reservoir negligably small.
+
+%%% figs 2a and b %%%
 Assuming the source barrier is in the limit where single electron transitions ($\Gamma_{In/Out}$) are only broadened by the temperature of the reservoir (discussed further in Fig.
@@
 
-The temperature of the electron reservoir was varied by applying an AC current through the heating QPC on the left side of the channel.
+%%% figs 2c and d%%%
 Fluctuations in $g_{sens}$ were measured at $2f_{Heat}$ using a lock-in amplifier; the temperature of the reservoir goes as $dT^2 \sim P^{AC}_{Heat} \sim \sin^2(2\omega t)$.

### 2018-01-27 paper/draft.tex
Josh edits of Jan 26

@@
 Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
-Such measurements are typically based on bulk properties, such as heat capacity, that are straightforward to observe in macroscopic samples but exceedingly difficult to access in mesoscopic systems, sometimes consisting of just a few electrons.
-Taking advantage of a well-known Maxwell relation, we realize a mesoscopic geometry in a GaAs heterostructure in which entropy-to-charge conversion enables an entropy measurement of quantum states down to the single electron level.
-As a demonstration of the efficacy of this method, the entropy of the first few-electron spin states in a gate-defined GaAs quantum dot are measured.
+Such measurements are typically based on bulk properties, such as heat capacity, that are straightforward to observe in macroscopic samples but exceedingly difficult to access in mesoscopic systems that may consist of just a few electrons.
+Taking advantage of a well-known Maxwell relation, we realize a protocol for entropy-to-charge conversation in a gate-defined GaAs quantum dot that enables an entropy measurement of the first three quantum states in to the dot.
 The entropy of a single spin ($k_B \ln{2}$) is measured within 8\% accuracy, as is the entropy arising at the magnetic field-driven singlet-triplet crossing for two electrons.
@@
 
-While measurements of heat capacity are effective in probing the entropy of macroscopic 3D samples, the heat capacities of single electrons or quasiparticles are much too small to measure directly; even the 2D sheet of quasiparticles in $\nu = \frac{5}{2}$ fractional quantum Hall samples has a heat capacity that vanishes in comparison to the host crystal.
-Rather than attempt to resolve such infinitesimal signals, the problem can be avoided by converting a change in entropy to changes in a more easily measured quantity, charge.
-Our approach is analogous to the milestone of spin-to-charge conversion, first demonstrated in GaAs quantum dots in 2004, by which undetectably-small magnetic moments of a single spin were transformed into thepresence or absence of an electron charge, which is easily detected4 \cite{Elzerman2004, Ono2004}.
+Entropy can be probed effectively in 3D macroscopic samples via measurements of heat capacity, but the heat capacities of single electrons or quasiparticles are much too small to measure directly; even the 2D sheet of quasiparticles in $\nu = \frac{5}{2}$ fractional quantum Hall samples has a heat capacity that vanishes in comparison to that of the host crystal.
+Rather than attempt to resolve such infinitesimal signals, the problem can be avoided by converting a change in entropy to changes in charge--a quantity that is easily detected at the single particle level.
+Our approach is analogous to the milestone of spin-to-charge conversion, first demonstrated in GaAs quantum dots in 2004, by which undetectably-small magnetic moments of a single spin were transformed into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
 
@@
 %
-that connects changes in entropy, $S$, (as well as particle number $N$ and temperature $T$) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control.
-The fixed pressure condition is met by working well below the Fermi temperature, $T_F \sim$\SI{5}{\kelvin}, where the pressure is simply the degeneracy pressure \cite{Landau1969}.
+that connects changes in entropy, $S$, (as well as particle number, $N$, and temperature, $T$) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control.
+The fixed pressure condition of Eq.~\ref{eqn:max} is effectively met by working well below the Fermi temperature, $T_F \sim$\SI{5}{\kelvin}, where the pressure is simply the degeneracy pressure \cite{Landau1969}.
 Refs.~\onlinecite{Cooper2009} and ~\onlinecite{Ben-Shach2013} propose schemes to measure the entropy derivative, $\frac{\partial S}{\partial N}$, of the $\nu = \frac{5}{2}$ state via this Maxwell relation, detecting changes in the quasiparticle chemical potential with temperature.
@@
 Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states studied here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-This work demonstrates a direct thermodyanmic measurement on a simple few-particle system; the method can be easily extended as a probe into the nature of more exotic systems ,such as topologically non-trivial Majorana and other non-Abelian states.
+Our experiment demonstrates a direct entropy measurement on a few-particle system; in the future, the method can be easily extended as a probe into the nature of more exotic systems, such as topologically non-trivial Majorana and other non-Abelian states.
 
-The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a realizes an electron reservoir (central region) in thermal equilibrium with a few-electron quantum dot coupled to its right side, where tunneling between the two is measured using a charge sensing QPC capacitively coupled to the dot \cite{Staring2007, Frolov2009, Thierschmann2015}.
-The number of electrons on the dot can be tuned using the gate voltage, $V_G$.
-An electron is added to an $N$ electron dot when the chemical potential to add an electron, $\mu_{N+1}$ (proportional to $V_G$), drops below the Fermi level of the reservoir, $E_F$.
-Figure 1b illustrates a such a transition, as measured by the charge sensor conductance, as a function of $V_G$.
-The gate voltage corresponding to midpoint of the transition, $V_0$, marks the chemical potential where the probabilties of finding $N$ or $N+1$ electrons on the dot are equal.
-This transition is thermally broadened by the reservoir temperature $T_{res}$.
-Additionally, an entropy change from the $N$ to $N+1$ ground states of the dot can shift the midpoint of the transition, $V_0$, by changing the chemical potential on the dot as in Eq.~\ref{eqn:max}.
+The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a realizes an electron reservoir (central region) in thermal equilibrium with a few-electron quantum dot coupled to its right side, whose occupation is measured using an adjacent charge sensing quantum point contact\cite{Staring2007, Frolov2009, Thierschmann2015}.
+The number of electrons on the dot can be tuned using the gate voltage, $V_G$, to control the chemical potential.
+An electron is added to an $N$ electron dot when the chemical potential to add an electron, $\mu_{N+1}$, drops below the Fermi level of the reservoir, $E_F$.
+Figure 1b illustrates a such a transition, showing the expected step in charge sensor conductance as a function of $V_G$ thermally broadened by the reservoir temperature $T_{res}$.
+The gate voltage corresponding to midpoint of the transition, $V_0$, marks the chemical potential where the probabilities of finding $N$ or $N+1$ electrons on the dot are equal.
+
+Any entropy change from the $N$ to $N+1$ ground states of the dot should shift the midpoint of the transition, $V_0$, by changing the chemical potential on the dot as in Eq.~\ref{eqn:max}.
 Detecting the shift in $V_0$ with respect to temperature (${\propto}\frac{\partial \mu}{\partial T}$), amounts to a measurement of the entropy difference $dS$ between the $N$ to $N+1$ ground states ($dN=1$).
-In practice, the shift in $V_0$ is measured by oscillating $T_{res}$ and monitoring changes in $g_{sens}$ with a lockin amplifier.
-Consider the charge transitions in Fig.~\ref{fig:fig1}b, if the warmer transition is not only broadened but shifted ($dS\neq0$), the change in $g_{sens}$ is asymmetric as shown in Fig.~\ref{fig:fig1}c; if the warmer transition is broadened but not shifted with respect to the cooler one ($dS=0$), the lineshape is anti-symmetric.
+In practice, the shift in $V_0$ with temperature is measured by oscillating $T_{res}$ and monitoring any resulting changes in $g_{sens}$ with a lockin amplifier.
+If the transition is broadened but not shifted due to heating ($dS=0$), an antisymmetric lineshape is expected from this lockin measurement.
+If the transition is not only broadened but also shifted ($dS\neq0$), the change in $g_{sens}$ due to heating will asymmetric, as shown in Fig.~\ref{fig:fig1}c, thus offering a clearly distinguishable signature of entropy for this single charge measurement.
 
-An explanation based on detailed balance is helpful in understanding how a shift in $\mu_{N+1}$ (relative to $E_F$) relates to entropy.
-Tunneling between the dot and reservoir is possible when the chemical potential to add an electron, $\mu_{N+1}$, is within ${\sim}3.5 k_B T$ of Fermi level of the reservoir.
-Away from that window, tunneling is suppressed due to a lack of available states in the reservoir.
-To illustrate how the tunnel rates, $\Gamma_{in}=\Gamma_{N\rightarrow N+1}$ and $\Gamma_{out}=\Gamma_{N+1\rightarrow N}$ depend on degeneracy, consider the filling of the first electron state.
-The 1-electron ground state has a degeneracy of 2 due to a single, unpaired spin-$\frac{1}{2}$; electrons tunneling into this state have both spin-up and -down states available.
-Conversely, an electron tunneling off of the dot must tunnel into a state with its same spin, that is, only half of the reservoir states are available to it.
+An explanation based on detailed balance is helpful in understanding how the shift in $\mu_{N+1}$ with respect to $E_F$ upon heating relates to entropy.
+In general, electrons tunnel back and forth between the dot and reservoir as long as $\mu_{N+1}$ is within thermal broadening of Fermi level, that is, as long as there are available states in both the dot and the reservoir.
+The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N\rightarrow N+1}$ and $\Gamma_{out}=\Gamma_{N+1\rightarrow N}$, depend on degeneracy of the $N$ and $N+1$ levels.
+Consider the filling of the first electron state at zero magnetic field, a state with a single, unpaired spin-$\frac{1}{2}$ and therefore a degeneracy of 2.
+An electron tunneling into this state has both spin-up and -down states available.
+Tunneling off, the electron (whether spin up or down) must tunnel into reservoir states with the spin, that is, only half of the reservoir states are available to it.
 As a result, $\Gamma_{in} = 2\Gamma_{out}$ when $\mu_{N+1}=E_F$.
@@
 %
-where $\Gamma$ is a coupling constant and $g_{N/N+1}$ are the degeneracies of the $N$ and $N+1$ electron states..
-The midpoint of the transition between the $N$ and $N+1$ electon states, measured by the charge sensor, occurs when the $\Gamma_{in} = \Gamma_{out}$.
-It is clear from Eqs.~\ref{eqn:gin} and \ref{eqn:gout}, that in the case $g_{N}=g_{N+1}$, $\Gamma_{in} = \Gamma_{out}$ when $\mu_{N+1} = E_F$.
-However, if the two occupation states differ in their degeneracy, the midpoint of the transition shifts away from $\mu_{N+1}=E_F$.
-Thermal broadening of the Fermi functions in Eqs.~\ref{eqn:gin} and \ref{eqn:gout} means that the chemical potential at which $\Gamma_{in} = \Gamma_{out}$ depends on $T$ as well as $g_{N/N+1}$.
-By measuring $dV_0$ ($d_\mu$) as a function of $dT$, the ratio $g_{N+1}/g_{N}$ can be determined, which is related to $dS$ through the Boltzmann entropy.
+%MAKE THIS ONE EQUATION
+
+where $\Gamma$ is a coupling constant, $f$ is the Fermi function, and $g_{N/N+1}$ are the degeneracies of the $N$ and $N+1$ electron states.
+
+The midpoint of the transition between the $N$ and $N+1$ electron states, measured by the charge sensor, occurs when the dot is occupied half the time, that is, when $\Gamma_{in} = \Gamma_{out}$.
+From Eqs.~\ref{eqn:ginout}, $\Gamma_{in} = \Gamma_{out}$ occurs when $\mu_{N+1} = E_F$ as long as $g_{N}=g_{N+1}$, but when $g_{N}<>g_{N+1}$ the midpoint of the transition shifts away from $\mu_{N+1}=E_F$ by an amount that depends on the broadening of the Fermi function and therefore on $T$.
+Thus, a measurement of how the midpoint of the transition (V_0) shifts with T allows a determination of the ratio $g_{N+1}/g_{N}$, which itself is related to $dS$ through the Boltzmann entropy formula, $S=k_B ln(g)$.
 The relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}.

### 2018-02-01 paper/draft.tex
add josh-edit into branch

@@
+% print and edit
+% edit figs 3 and 4 text
+% edit conclusion
+
 \documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
@@
 \begin{align}
-	\Gamma_{in} &=  g_{N+1} \Gamma f(E_F - \mu_{N+1}) \label{eqn:gin}\\
-	\Gamma_{out} &= g_{N} \Gamma [1 - f(E_F - \mu_{N+1})] \label{eqn:gout}
+	\Gamma_{in} &=  g_{N+1} \Gamma f(E_F - \mu_{N+1}) \label{eqn:rates}\\
+	\Gamma_{out} &= g_{N} \Gamma [1 - f(E_F - \mu_{N+1})] \nonumber
 \end{align}
 %
-%MAKE THIS ONE EQUATION
-
 where $\Gamma$ is a coupling constant, $f$ is the Fermi function, and $g_{N/N+1}$ are the degeneracies of the $N$ and $N+1$ electron states.
@@
 From Eqs.~\ref{eqn:ginout}, $\Gamma_{in} = \Gamma_{out}$ occurs when $\mu_{N+1} = E_F$ as long as $g_{N}=g_{N+1}$, but when $g_{N}<>g_{N+1}$ the midpoint of the transition shifts away from $\mu_{N+1}=E_F$ by an amount that depends on the broadening of the Fermi function and therefore on $T$.
-Thus, a measurement of how the midpoint of the transition (V_0) shifts with T allows a determination of the ratio $g_{N+1}/g_{N}$, which itself is related to $dS$ through the Boltzmann entropy formula, $S=k_B ln(g)$.
+Thus, a measurement of how the midpoint of the transition ($V_0$) shifts with T allows a determination of the ratio $g_{N+1}/g_{N}$, which itself is related to $dS$ through the Boltzmann entropy formula, $S=k_B ln(g)$.
 The relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}.
@@
 (b) Derivative of the charge sensor signal with $dT \sim 60mK$.
-Fits to $dg$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a fucntion of mixing chamber temperature.
+Fits to $dg$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a function of mixing chamber temperature.
 The highlighted, linear region is where all the data discussed were measured.
@@
 %%% device setup %%%
-Using the gates on the right hand side of Fig~\ref{fig:fig1}a, the quantum dot was tuned such that there is a weak tunnel coupling to the reservoir on the source side with the drain side of the dot closed.
-The charge sensing QPC was tuned to a conductance of ${\sim}e^2/h$.
+Using the gates on the right hand side of Fig~\ref{fig:fig1}a, the quantum dot was tuned such that it was tunnel coupled to the reservoir on the source side with the drain side closed.
+The charge sensing QPC was tuned to a conductance of ${\sim}e^2/h$, where it was found to be most sensitive as a charge detector.
 A small DC voltage bias was applied across the QPC and the measured current was used to calculate the sensor conductance.
-The reservoir temperature was controlled either by varying the fridge temperature or by Joule heating through the QPC on the left side of the channel.
-In the latter case, the QPC was fixed at \SI{20}{\kilo\ohms} and biased using an AC or DC current source.
-The Joule heating strategy gives fast control of the temperature (up to \SI{100}{\hertz}) while keeping the voltage drop across the reservoir negligably small.
+The reservoir temperature was controlled either by varying the mixing chamber temperature or by Joule heating through the QPC on the left side of the channel.
+In the latter case, the QPC was fixed at \SI{20}{\kilo\ohm} and biased with an AC or DC current source.
+The Joule heating setup gives fast control of the temperature (up to \SI{100}{\hertz}) while keeping the voltage drop across the reservoir negligibly small.
 
 %%% figs 2a and b %%%
-Assuming the source barrier is in the limit where single electron transitions ($\Gamma_{In/Out}$) are only broadened by the temperature of the reservoir (discussed further in Fig.
-\ref{fig:fig2}c, the charge sensor conductance takes the form,
+Fig.~\ref{fig:fig2}a shows the charge sensor conductance as the first electron is added to the dot by tuning $V_G$, at two different temperatures.
+The higher temperature transition curve is broadened by the increased temperature and shifted left due to the change in entropy (degeneracy)  between the empty and singly-occupied states.
+Assuming the source barrier is sufficiently large, $\Gamma_{in/out}$ are broadened only by the temperature of the reservoir and the conductance takes the form,
 %
@@
 where $\Theta = \frac{k_B T}{\alpha e}$, $\alpha$ is the lever arm for the quantum dot plunger gate, and $G_1$ is determined by the cross capacitance between the sensor gates and the plunger gate.
+Fits to this equation are seen in addition to the sensor data in Fig.~\ref{fig:fig2}a.
+From the fits the transition width in mV, $\Theta$, can be extracted.
+Fig.~\ref{fig:fig2}b $\Theta$ is plotted as a function of mixing chamber temperature, $T_{MC}$.
+From this plot it is clear that Eq.~\ref{eqn:g} holds when $T_{MC}\geq$\SI{100}{\milli\kelvin}.
+For this reason, the mixing chamber temperature remains mixed at \SI{100}{\milli\kelvin} for the remainder of this work.
+Fitting high temperature data in Fig.~\ref{fig:fig2} to the definition of $\Theta$ (with $T=T_{MC}$) yields $\alpha$, making it possible to convert from $V_G$ to $\mu$ directly.
 
 %%% figs 2c and d%%%
-Fluctuations in $g_{sens}$ were measured at $2f_{Heat}$ using a lock-in amplifier; the temperature of the reservoir goes as $dT^2 \sim P^{AC}_{Heat} \sim \sin^2(2\omega t)$.
+Data in Fig.~\ref{fig:fig2}c, and the corresponding fits, illustrate how entropy was measured at a single charge transition.
+Fluctuations in $g_{sens}$, $dg_{sens}$, were measured as $T_{electron}$ in the reservoir was varied using Joule heating with an AC current source ($f_{Heat}$\SI{48.7}{\hertz}).
+The change in $T_{electron}$ of the reservoir is given by $dT \sim I^{AC}_{Heat} \sim \sin^2(2\omega t)$.
+A calibration for $dT$, using $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
+To avoid thermally accessing excited states of the dot it must be true that $k_B dT \ll \Delta$ where $\Delta$ is the level spacing between the ground and first excited states; which holds for all transitions investigated.
+
+To acquire $dg_{sens}$, current fluctuations through the charge sensor were measured at $2f_{Heat}$ using a lockin amplifier.
 Taking a derivative of Eq.
-\ref{eqn:g} with respect to temperature gives the change in conductance, $dg_{sens}$, as measured by the lock-in amplifier,
+\ref{eqn:g} with respect to temperature gives the form of $dg_{sens}$ near a charge transition,
 %
@@
 where $\delta=\frac{\partial V_0}{\partial \Theta}$.
-By using the lever arm to convert $V_0$ to chemical potential $\mu$, and recalling Eq.
-\ref{eqn:max}, the parameter $\delta$ can be related to the change in entropy,
+Using the lever arm to convert $V_0$ to a chemical potential $\mu$, the parameter $\delta$ can be related to the change in entropy through Eq.~\ref{eqn:max},
 %
@@
         \frac{1}{k_B} \frac{\partial \mu}{\partial T} = 
-        -\frac{1}{k_B} \frac{\partial S}{\partial N}
+        -\frac{1}{k_B} \partial S
 \end{align}
 %
-
-The entropy measurement requires no further calibration to extract the desired results from the $dg$ fits.
-However, it is necessary to ensure that the range of temperatures and energies fit the analysis.
-To begin, the dot is depleted by tuning the plunger gate and identifying the empty dot using the charge sensor.
-Typical charge sensor curves for the $N=0 \rightarrow 1$ transision are shown in Fig.
-\ref{fig:fig2}.
-The width of the charge sensor signal, determined by fitting Eq.
-\ref{eqn:g}, is measured as a function of the mixing chamber temperature in Fig.
-\ref{fig:fig2}c).
-At a sufficiently high temperature, $T_{electron}=T_{MC}$, and the transition width is determined only by $T_{MC}$ (highlighted region in Fig.
-\ref{fig:fig2}c).
-A line fit to $\Theta = \frac{k_B T_{MC}}{\alpha e}$ is used to determine $\alpha$.
-The remainder of the measurements are performed in the linear region of Fig.
-\ref{fig:fig2}c at $T_{MC} = 100mK$, where Eqs.
-\ref{eqn:g} and \ref{eqn:dg} are valid.
-Fig.
-\ref{fig:fig2}d shows the calibration of $dT$ as a function of DC current through the QPC heater ($P_{Heat} = I^2_{Heat} R_{QPC}$).
-Using $\alpha$ to convert from $\Theta$ to $T_{electron}$, the linear fit Fig.
-\ref{fig:fig2}d gives the the conversion from $I_{Heat}$ to $dT$.
-To avoid thermally accessing excited states of the dot it must be true that $k_B dT \ll \Delta$ where $\Delta$ is the level spacing between the ground and first excited states; which holds for all transitions investigated.
-
-Data in Fig.
-\ref{fig:fig2}b show the change in quantum dot entropy determined directly from the lock-in signal, $dg_{sens}$.
-Fits to Eq.
-\ref{eqn:dg} are shown for $\delta=0$ (dashed) and a best fit to $\delta$ (solid).
-It is clear from these fits, $\delta$ is necessary to properly fit the asymmetry in peak height, with the best fit being $\delta \approx \ln{2}$.
-This is easily understood from the Boltzmann entropy.
-For an N-electron macrostate on the quantum dot, entropy is given by,
+Fits to Eq.~\ref{eqn:dg} are shown for $\delta=0$ and a best fit to $\delta$.
+From these fits it is clear $\delta\neq0$ is necessary to properly fit the asymmetry in peak height, with the best fit being $\delta \approx \ln{2}$.
+For an N-electron macrostate on the quantum dot, entropy is given by the Boltzmann entropy,
 %
@@
 %
-where $\Omega$ is the number of microstates available.
-The number of microstates is equal to the spin degeneracy of the ground state.
-For the 0-1 transition, this gives $dS =  k_B\ln{2} - k_B \ln{1} = k_B\ln{2}$.
+where $\Omega$ is the spin degeneracy of the ground state, equal to the number of microstates available. For the 0-1 transition, $dS =  k_B\ln{2} - k_B \ln{1} = k_B\ln{2}$.
 
-Because $\delta$ is a fit parameter independent of $dT$, it is possible to extract the same $\delta$ value for a range of $dT$ ($I^{AC}_{Heat}$).
-Fig.
-\ref{fig:fig2}e shows that $dS$, as determined from $dg_{sens}$ fits, remains constant over a range of $dT$.
-Looking at the vertical scale on the right side of Fig.
-\ref{fig:fig2}e, the same shift in chemical potential on the dot is given in units of gate voltage shift per unit temperature change.
-This illustrates why the lock-in measurement was utilized; device stability and small signals made it difficult for the entropy to be determined directly from $g_{sens}$ using DC heating.
+%%% fig 2e %%%
+Note that $\delta$ is a fit parameter independent of $dT$ and $\alpha$.
+Fig.~\ref{fig:fig2}e shows that $dS$, as determined from fits to $dg_{sens}$ data, remains constant over a range of $dT$ ($I^{AC}_{Heat}$).
+The vertical scale on the right side of Fig.
+\ref{fig:fig2}e, $\delta$ in units of gate voltage per unit temperature, illustrates the necessity of the lockin measurement; device stability and small signals made it difficult for $delta$ to be determined directly from $g_{sens}$ at different $T$.
 

### 2018-02-02 paper/draft.tex
heaps of edits

@@
-% print and edit
-% edit figs 3 and 4 text
-% edit conclusion
-
 \documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
@@
 An electron is added to an $N$ electron dot when the chemical potential to add an electron, $\mu_{N+1}$, drops below the Fermi level of the reservoir, $E_F$.
-Figure 1b illustrates a such a transition, showing the expected step in charge sensor conductance as a function of $V_G$ thermally broadened by the reservoir temperature $T_{res}$.
+Figure 1b illustrates a such a transition, showing the expected step in charge sensor conductance as a function of $V_G$ and thermal broadening by the reservoir temperature, $T_{res}$.
 The gate voltage corresponding to midpoint of the transition, $V_0$, marks the chemical potential where the probabilities of finding $N$ or $N+1$ electrons on the dot are equal.
@@
 If the transition is broadened but not shifted due to heating ($dS=0$), an antisymmetric lineshape is expected from this lockin measurement.
-If the transition is not only broadened but also shifted ($dS\neq0$), the change in $g_{sens}$ due to heating will asymmetric, as shown in Fig.~\ref{fig:fig1}c, thus offering a clearly distinguishable signature of entropy for this single charge measurement.
+If the transition is not only broadened but also shifted ($dS,d\mu\neq0$), the change in $g_{sens}$ due to heating will asymmetric, as shown in Fig.~\ref{fig:fig1}c, thus offering a clearly distinguishable signature of entropy for this single charge measurement.
 
-An explanation based on detailed balance is helpful in understanding how the shift in $\mu_{N+1}$ with respect to $E_F$ upon heating relates to entropy.
+An explanation based on detailed balance is helpful in understanding how the shift in $\mu_{N+1}$ (with respect to $E_F$) upon heating relates to entropy.
 In general, electrons tunnel back and forth between the dot and reservoir as long as $\mu_{N+1}$ is within thermal broadening of Fermi level, that is, as long as there are available states in both the dot and the reservoir.
-The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N\rightarrow N+1}$ and $\Gamma_{out}=\Gamma_{N+1\rightarrow N}$, depend on degeneracy of the $N$ and $N+1$ levels.
+The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N\rightarrow N+1}$ and $\Gamma_{out}=\Gamma_{N+1\rightarrow N}$, depend on degeneracy of the $N$ and $N+1$ ground states.
 Consider the filling of the first electron state at zero magnetic field, a state with a single, unpaired spin-$\frac{1}{2}$ and therefore a degeneracy of 2.
 An electron tunneling into this state has both spin-up and -down states available.
-Tunneling off, the electron (whether spin up or down) must tunnel into reservoir states with the spin, that is, only half of the reservoir states are available to it.
+Tunneling out, the electron (whether spin up or down) must tunnel into reservoir states with the same spin, that is, only half of the reservoir states are available.
 As a result, $\Gamma_{in} = 2\Gamma_{out}$ when $\mu_{N+1}=E_F$.
@@
 The midpoint of the transition between the $N$ and $N+1$ electron states, measured by the charge sensor, occurs when the dot is occupied half the time, that is, when $\Gamma_{in} = \Gamma_{out}$.
-From Eqs.~\ref{eqn:ginout}, $\Gamma_{in} = \Gamma_{out}$ occurs when $\mu_{N+1} = E_F$ as long as $g_{N}=g_{N+1}$, but when $g_{N}<>g_{N+1}$ the midpoint of the transition shifts away from $\mu_{N+1}=E_F$ by an amount that depends on the broadening of the Fermi function and therefore on $T$.
-Thus, a measurement of how the midpoint of the transition ($V_0$) shifts with T allows a determination of the ratio $g_{N+1}/g_{N}$, which itself is related to $dS$ through the Boltzmann entropy formula, $S=k_B ln(g)$.
+From Eq.~\ref{eqn:rates}, $\Gamma_{in} = \Gamma_{out}$ occurs when $\mu_{N+1} = E_F$ as long as $g_{N}=g_{N+1}$.
+When $g_{N}\neq g_{N+1}$, the midpoint of the transition shifts away from $\mu_{N+1}=E_F$ by an amount that depends on the broadening of the Fermi function, and therefore on $T$.
+Thus, a measurement of how the midpoint of the transition ($V_0$) shifts with T allows the ratio $g_{N+1}/g_{N}$ to be determined, which itself is related to $dS$ through the Boltzmann entropy formula, $S_{N}=k_{B} \ln{g_N}$.
 The relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}.
@@
 %%% device setup %%%
-Using the gates on the right hand side of Fig~\ref{fig:fig1}a, the quantum dot was tuned such that it was tunnel coupled to the reservoir on the source side with the drain side closed.
-The charge sensing QPC was tuned to a conductance of ${\sim}e^2/h$, where it was found to be most sensitive as a charge detector.
+Using the gates on the right side of Fig~\ref{fig:fig1}a, the quantum dot was tuned such that the source was tunnel coupled to the reservoir with the drain closed.
+The charge sensing QPC was tuned to a conductance of ${\sim}e^2/h$, where conductance was most sensitive to charge on the dot.
 A small DC voltage bias was applied across the QPC and the measured current was used to calculate the sensor conductance.
-The reservoir temperature was controlled either by varying the mixing chamber temperature or by Joule heating through the QPC on the left side of the channel.
+The reservoir temperature was controlled by varying the mixing chamber temperature or Joule heating through the QPC on the left side of the channel.
 In the latter case, the QPC was fixed at \SI{20}{\kilo\ohm} and biased with an AC or DC current source.
@@
 Fig.~\ref{fig:fig2}a shows the charge sensor conductance as the first electron is added to the dot by tuning $V_G$, at two different temperatures.
-The higher temperature transition curve is broadened by the increased temperature and shifted left due to the change in entropy (degeneracy)  between the empty and singly-occupied states.
+The higher temperature transition curve is noticeably broadened by the increased temperature.
 Assuming the source barrier is sufficiently large, $\Gamma_{in/out}$ are broadened only by the temperature of the reservoir and the conductance takes the form,
@@
 where $\Theta = \frac{k_B T}{\alpha e}$, $\alpha$ is the lever arm for the quantum dot plunger gate, and $G_1$ is determined by the cross capacitance between the sensor gates and the plunger gate.
-Fits to this equation are seen in addition to the sensor data in Fig.~\ref{fig:fig2}a.
-From the fits the transition width in mV, $\Theta$, can be extracted.
-Fig.~\ref{fig:fig2}b $\Theta$ is plotted as a function of mixing chamber temperature, $T_{MC}$.
-From this plot it is clear that Eq.~\ref{eqn:g} holds when $T_{MC}\geq$\SI{100}{\milli\kelvin}.
-For this reason, the mixing chamber temperature remains mixed at \SI{100}{\milli\kelvin} for the remainder of this work.
-Fitting high temperature data in Fig.~\ref{fig:fig2} to the definition of $\Theta$ (with $T=T_{MC}$) yields $\alpha$, making it possible to convert from $V_G$ to $\mu$ directly.
+The dependence of $V_0$ on $\Theta$ captures any shift in $\mu$ due to a change in entropy (degeneracy) across the transition.
+Fits to Eq.~\ref{eqn:g} are seen, in addition to the sensor data, in Fig.~\ref{fig:fig2}a.
+From these fits the transition width, $\Theta$, can be extracted.
+In Fig.~\ref{fig:fig2}b $\Theta$ is plotted as a function of mixing chamber temperature, $T_{MC}$.
+From this plot, it is clear that Eq.~\ref{eqn:g} holds when $T_{MC}\gtrsim$ \SI{100}{\milli\kelvin}.
+For this reason, the mixing chamber temperature remains fixed at \SI{100}{\milli\kelvin} for the remainder of this work.
+Fitting high temperature data in Fig.~\ref{fig:fig2} to the definition of $\Theta$ (with $T=T_{MC}$) yields $\alpha$, making it possible to convert from $V_G$ to $\mu$.
 
 %%% figs 2c and d%%%
-Data in Fig.~\ref{fig:fig2}c, and the corresponding fits, illustrate how entropy was measured at a single charge transition.
-Fluctuations in $g_{sens}$, $dg_{sens}$, were measured as $T_{electron}$ in the reservoir was varied using Joule heating with an AC current source ($f_{Heat}$\SI{48.7}{\hertz}).
-The change in $T_{electron}$ of the reservoir is given by $dT \sim I^{AC}_{Heat} \sim \sin^2(2\omega t)$.
+Data in Fig.~\ref{fig:fig2}c, and the corresponding fits, show how $dS$ was measured across a single charge transition.
+Fluctuations in $g_{sens}$, were measured as $T_{res}$ was varied using Joule heating with an AC current source ($f_{Heat} =$ \SI{48.7}{\hertz}).
+The change in $T_{res}$ is given by $dT \sim I^{AC}_{Heat} \sim \sin^2(2\omega t)$.
 A calibration for $dT$, using $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
@@
 \ref{fig:fig2}e, $\delta$ in units of gate voltage per unit temperature, illustrates the necessity of the lockin measurement; device stability and small signals made it difficult for $delta$ to be determined directly from $g_{sens}$ at different $T$.
+Without any additional calibration, it is possible to measure $dS$ directly from the lockin amplifier signal, $dg_{sens}$.
 
@@
 
+To confirm that the measured signal derives from the electron spin, the behavior of $dS$ is investigated as a function of parallel magnetic field.
 Fig.
-\ref{fig:fig3}c shows $dS$ as a function of parallel field for the 0-1 (and 2-3) electron transitions.
-The spin-$\frac{1}{2}$ degeneracy of the 1-electron ground state is lifted as the field increases to \SI{\pm5}{\tesla}.
-As the Zeeman splitting, measured directly in Fig.
-\ref{fig:fig2}b, lifts the spin degeneracy, the entropy of the 1-electron state goes to zero.
-The 2-3 electron transition behaves similarly at low fields.
-The 2-electron ground state is the spin singlet, and the 3-electron ground state is same singlet with an additional unpaired electron, with degeneracy of 2, as in the 1-electron case.
-Below \SI{5}{\tesla} $g\mu_B B$ remains the largest energy scale, and no 3-electron excited states need be considered.
+\ref{fig:fig3}c shows $dS$ as a function of applied field for the 0-1 and 2-3 electron transitions.
+The 2-electron ground state is a spin singlet, while the 3-electron ground state is same singlet with an additional unpaired electron, making the field-dependent behavior of these transitions identical where $g \mu_{B} B$ is less than the excited state energies.
+Zeeman splitting, measured directly in Fig.
+\ref{fig:fig2}b, lifts the spin degeneracy of the unpaired electrons and the entropy of the 1- and 3- electron ground states goes to zero.
 
-To understand the behavior of $dS$ as a function of magnetic field, Eq. \ref{eqn:S} can be rewritten as,
+The behavior of $dS$ as a function of magnetic field can be understood using the Gibbs entropy,
 %
@@
 %
-where $p_{i}(B, T)$ is the probabilty of the system being in the i$^{th}$ microstate at a given field and temperature.
-The 1 and 3-electron ground states have only a spin-$\frac{1}{2}$ degree of freedom at low field and $p_{i}(B, T)$ can be written as a two-level system,
+where $p_{i}(B, T)$ is the probability of the system being in the i$^{th}$ spin state at a given field and temperature.
+For states with a single unpaired electron, $p_{i}(B, T)$ can be written as a two-level system,
 %
@@
 where $\pm$ represent the spin up/down states of the unpaired electron.
-
-The dashed and solid lines in Fig \ref{fig:fig3}c show fits to $dS$ using Eqs.
-\ref{eqn:Sp} and \ref{eqn:p} for the 0-1 and 2-3 electron transitions, respectively.
-These fits allow for peak height, g-factor, and a vertical offset as free parameters; $T$ is fixed at the mixing chamber temperature.
-From these fits, $dS=0.92 \ln{2}$ and $g=-0.33$.
-The peak height, corresponding to $dS(B=0)$, deviates from the expected value because it is convoluted with the vertical offset, caused by the cross-capacitance between plunger and QPC gates.
-The discrepancy between $g$ and the result in Fig.
-\ref{fig:fig3}b, can be understood from the change in shape of the quantum dot when tuning between the open and closed drain configurations [citation?].
+Fits to Eqs.
+\ref{eqn:Sp} and \ref{eqn:p} are shown in Fig \ref{fig:fig3}c for the 0-1 and 2-3 electron transitions.
+The fits allow for peak height, g-factor, and a vertical offset as free parameters with $T$ fixed at $T_{MC}$.
+From these fits, $dS=0.92 \ln{2}$ and $g=-0.33$ for the 0-1 transition.
+Discrepancy between $g$ and the result shown in Fig.
+\ref{fig:fig3}b, is understood from the change in shape of the quantum dot when tuning between the $g_{dot}$ and $g_{sens}$ measurements.
 
@@
 
-The low field (\SI{<5}{\tesla}) results in Fig.
-\ref{fig:fig4}c can be understood as simply the inverse of Fig \ref{fig:fig3}c.
-The entropy of the 2-electron ground state remains $0$, in the spin-singlet state, and the entropy of the 1-electron ground state goes from $k_B\ln{2}$ to $0$ due to the Zeeman splitting seen in Fig.
-\ref{fig:fig3}b.
-At high field, the 1-electron ground state remains non-degenerate, while the 2-electron ground state picks up a degeneracy of 2 at \SI{9}{\tesla} as the singlet and triplet ($T_+$) levels cross.
-This confirms that the $dS$ signal can be related directly to a tunable degeneracy in the system.
-The same splittings in the quantum dot conductance data can be seen in Fig.
-\ref{fig:fig4}b.
+The low field (\SI{<5}{\tesla}) data in Fig.
+\ref{fig:fig4}c for the 1-2 electron transition is understood as the inverse of Fig \ref{fig:fig3}c.
+The 2-electron ground state remains in the spin singlet state with zero entropy while 1-electron ground state goes from $k_B\ln{2}$ to $0$ due to Zeeman splitting.
+At high fields, the 1-electron ground state remains non-degenerate, while the 2-electron ground state becomes two-fold degenerate at \SI{9}{\tesla} where the singlet and triplet ($T_+$) states cross.
+The singlet-triplet crossing is seen clearly in Fig.~\ref{fig:fig4}b.
 
-The entropy signal for the 1-2 transition can be fit using Eq.
-\ref{eqn:p} as the probabilities for the 1-electron groundstates and the following probabilities for the 2-electron singlet-triplet states,
+The entropy for the 1-2 transition can be fit using Eq. \ref{eqn:p} as the probabilities for the 1-electron states and the following probabilities for the 2-electron singlet-triplet states,
 %
@@
 %
-where $\Delta_{ST}$ is the singlet-triplet splitting.
-Looking at the width of the peaks in $dS$, it is clear that the g-factor changes, along with the singlet-triplet splitting, as the field is increased.
+where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
 Fitting the curve yields $g(B{=}0T)=-0.46$, $g(B{=}9T)=-0.31$, $\Delta_{ST}(B{=}9T)$ = \SI{240}{\micro\electronvolt}, $dS(B{=}0T) = 1.04\ln{2}$, and $dS(B{=}9T) = 1.01\ln{2}$.
-Each of these values is consistent with the dot transport data and the fits in Fig.
-\ref{fig:fig3}c.
+Each of these values is consistent with data in Figs.~\ref{fig:fig4}a and b as well as previous GaAs dot measurements [cite why g should change in high field].
+This fitting confirms that the $dS$ signal can be related directly to a tunable degeneracy in the system.
 
-The results presented in this work have confirmed the degeneracy of the few-electron ground states states, as calculated using only the spin degree of freedom.
-Magnetic field dependence of the entropy can be fit using simple spin statistics.
-Additionally, a technique has been demonstrated to measure the entropy of few-particle states in mesoscopic devices.
-Future work may take advantage of this strategy to probe the statistics of non-trival electron and quasiparticle states.
+%%% conclusion %%%
+The results presented demonstrate a novel technique to measure the entropy of few-particle states in mesoscopic devices.
+The measurement was used to investigate the well-understood spin degeneracy of the few-electron ground states states in a GaAs quantum dot.
+The entropy signal is confirmed by tuning the entropy as a function of applied magnetic field.
+Future work may take advantage of this strategy to look for thermodyanmic signatures of non-trival electron and quasiparticle states, eliminating the uncertainty found in typical transport data.
 

### 2018-02-02 paper/draft.tex
quick edits to figure captions

@@
-\documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
+\documentclass[preprint,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
 
@@
 Grey gates are unused (grounded).
-A \SI{1}{\milli\metre}-long channel is formed between the parallel gates running vertically down the image.
-The channel can be heated by driving current through the constriction on the left.
-A 200nm diameter quantum dot is tunnel-coupled to the right side of the channel.
-Occupation of the dot is monitored by a capacitively-coupled charge sensor.
 Squares show the locations of ohmic contacts to the 2DEG.
+An electron reservoir is formed between the parallel gates running vertically down the image with a 200nm diameter quantum dot coupled to the right side.
+The channel can be heated by driving current through the quantum point contact on the left.
+Electrons tunneling between the reservoir and dot are measured with a capacitively-coupled charge sensor.
 (b) Calculated charge sensor signal showing a single transition from $N \rightarrow N+1$ electrons at two temperatures ($T_{Red} > T_{Blue}$).
 (c) Change in the charge sensor signal with respect to temperature.
-The asymmetry in peak height arises from the shift in $V_0$ due to the change in entropy, $dS$, between the $N$ and $N+1$ electron states.
+The asymmetry in peak height arises from the shift in $V_0$ which relates to a change in entropy between the $N$ and $N+1$ electron states.
 In the case of $dS=0$, $dg$ is anti-symmetric about $V_0$.}
@@
 Temperature is set by DC current through the QPC heater.
-(b) Derivative of the charge sensor signal with $dT \sim 60mK$.
+(b) Lockin measurement of $dg_{sens}$ with $dT \sim 60mK$.
 Fits to $dg$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a function of mixing chamber temperature.
-The highlighted, linear region is where all the data discussed were measured.
-Fitting a straight line to this data, the lever arm $\alpha$ is calculated.
+The highlighted, linear region is where the tunnel rates are determined only by temperature broadening.
+The lever arm $\alpha$ is calculated by fitting a straight line to this region.
 (d) $\Theta$ as a function of DC current through the QPC heater.
-The linear fit is used to convert between $I_{heat}$ and $dT$, with $R_{QPC}$ fixed at 20$k\Omega$ (e) Change in entropy as a function of AC current through the QPC heater.
+Linear fit is used to convert between $I_{heat}$ and $dT$, with $R_{QPC} = $ \SI{20}{\kilo\ohm} (e) Change in entropy as a function of AC current through the QPC heater.
 Top axis shows corresponding $dT$.
-(f) Raw data from which $dS / k_B$ in (c), and the line cut in (b) were extracted.}
+Right axis shows shift in $V_0$ per unit temperature.}
 \end{figure}
@@
         \caption{\label{fig:fig3}(a) Transport data through the quantum dot showing the $N=0 \rightarrow 1$ transition.
-The first excited state, near $V_{SD}$ = \SI{1}{\milli\electronvolt}, is well-above all other energy scales in the measurement.
-Dashed line shows where data in (b) are taken.
-(b) Fixed bias transport data ($V_{SD}$ = \SI{700}{\micro\electronvolt}) showing fits to the Zeeman splitting of the ground state energy.
-(c) Change in entropy, extracted from $dg$ fits, as a function of parallel field.
-The $N=0 \rightarrow 1$ and $2 \rightarrow 3$ are overlaid here to show the behavior is the same at low parallel field.
-(d) and (e) show characteristic $dg$ traces from which the data in (c) were extracted.}
+The first excited state, near $V_{SD} = $ \SI{1}{\milli\electronvolt}, is well-above all other energy scales in the measurement.
+Dashed line at $V_{SD}$ = \SI{700}{\micro\electronvolt} shows where data in (b) are taken.
+(b) Fixed bias transport data showing fits to the Zeeman splitting of the ground state energy from which $g = -0.44$ is extracted.
+(c) Change in entropy, determined from $dg$ fits at varying parallel magnetic field.
+The $N=0 \rightarrow 1$ and $2 \rightarrow 3$ data are overlaid here to show the similar behavior of these states at low field.
+(d) and (e) show characteristic $dg$ traces from which the data in (c) were extracted.
+These data points are show as large markers in (c)}
 \end{figure}
 
-To confirm that the measured signal derives from the electron spin, the behavior of $dS$ is investigated as a function of parallel magnetic field.
-Fig.
-\ref{fig:fig3}c shows $dS$ as a function of applied field for the 0-1 and 2-3 electron transitions.
+To confirm that the measured signal derives from the electron spin, the behavior of $dS$ was investigated as a function of parallel magnetic field.
+Fig.~\ref{fig:fig3}c shows $dS$ as a function of applied field for the 0-1 and 2-3 electron transitions.
 The 2-electron ground state is a spin singlet, while the 3-electron ground state is same singlet with an additional unpaired electron, making the field-dependent behavior of these transitions identical where $g \mu_{B} B$ is less than the excited state energies.
 Zeeman splitting, measured directly in Fig.
-\ref{fig:fig2}b, lifts the spin degeneracy of the unpaired electrons and the entropy of the 1- and 3- electron ground states goes to zero.
+\ref{fig:fig2}b, lifts the spin degeneracy of the unpaired electrons and the entropy of the 1- and 3- electron ground states goes to zero with increasing field
 
@@
 \begin{align}
-\label{eqn:Sp}
+\label{eqn:gibbs}
         S &= k_B \sum_{i=\pm} p_{i}(B, T) \ln{ p_{i}(B,T) }
@@
 %
-where $\pm$ represent the spin up/down states of the unpaired electron.
-Fits to Eqs.
-\ref{eqn:Sp} and \ref{eqn:p} are shown in Fig \ref{fig:fig3}c for the 0-1 and 2-3 electron transitions.
+where $\pm$ represent the spin up/down states.
+Fits to Eqs.~\ref{eqn:gibbs} and \ref{eqn:p} are shown in Fig \ref{fig:fig3}c for each transition.
 The fits allow for peak height, g-factor, and a vertical offset as free parameters with $T$ fixed at $T_{MC}$.
-From these fits, $dS=0.92 \ln{2}$ and $g=-0.33$ for the 0-1 transition.
+From these fits we find $dS(B=0)=0.92 \ln{2}$ and $g=-0.33$ for the 0-1 transition.
 Discrepancy between $g$ and the result shown in Fig.
-\ref{fig:fig3}b, is understood from the change in shape of the quantum dot when tuning between the $g_{dot}$ and $g_{sens}$ measurements.
+\ref{fig:fig3}b, is understood from the change in shape of the quantum dot when tuning between the $g_{dot}$ and $g_{sens}$ measurements [cite?].
+The entropy agrees well with the expected $k_{B} \ln{2}$ at zero-field and goes to zero as expected with $B_{\parallel}$
 
@@
 Singlet-triplet splitting is roughly \SI{300}{\micro\electronvolt} and depends on applied field.
-Dashed line shows where data in (b) are taken.
-(b) TFixed bias transport data ($V_{SD}$ = \SI{1250}{\micro\electronvolt}).
-The triplet level is split into T$_+$, T$_0$, and $T_{-}$ (not visible).
-At \SI[input-protect-tokens]{\sim 9}{\tesla} T$_+$ becomes degenerate with S.
-g-factor is determined using $T_0$ and $T_+$ fits.
-(c) Change in entropy, extracted from $dg$ fits, as a function of parallel field.
+Dashed line at $V_{SD}$ = \SI{1250}{\micro\electronvolt} shows where data in (b) are taken.
+(b) Fixed bias transport data in parallel field.
+The triplet level is split into $T_+$, $T_0$, and $T_{-}$ (not visible).
+At \SI[input-protect-tokens]{\sim 9}{\tesla} $T_+$ becomes degenerate with $S$.
+$g$ is determined using $T_0$ and $T_+$ fits.
+(c) Change in entropy, extracted from $dg$ fits at varying parallel field.
 As the field goes from 0 to 10T, entropy of the 2-electron state goes from $0  \rightarrow \ln{2}$, while the entropy of the 1-electron state goes from $\ln{2} \rightarrow 0$.
-(d), (e), and (f) show characteristic $dg$ traces from which the data in (c) was extracted.}
+Fit to this behavior (dashed) is described in the text (d), (e), and (f) show characteristic $dg$ traces from which the data in (c) were extracted.
+These data points are show as large markers in (c)}
 \end{figure}
@@
 \ref{fig:fig4}c for the 1-2 electron transition is understood as the inverse of Fig \ref{fig:fig3}c.
-The 2-electron ground state remains in the spin singlet state with zero entropy while 1-electron ground state goes from $k_B\ln{2}$ to $0$ due to Zeeman splitting.
-At high fields, the 1-electron ground state remains non-degenerate, while the 2-electron ground state becomes two-fold degenerate at \SI{9}{\tesla} where the singlet and triplet ($T_+$) states cross.
+The 2-electron ground state remains in the spin singlet state with zero entropy while 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
+At high fields, the 1-electron ground state remains non-degenerate, while the 2-electron ground state becomes two-fold degenerate at \SI{9}{\tesla} where the singlet ($S$) and triplet ($T_+$) states cross.
 The singlet-triplet crossing is seen clearly in Fig.~\ref{fig:fig4}b.
 
-The entropy for the 1-2 transition can be fit using Eq. \ref{eqn:p} as the probabilities for the 1-electron states and the following probabilities for the 2-electron singlet-triplet states,
+The entropy for the 1-2 transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities given by Eq.~\ref{eqn:p} for the 1-electron states and the following probabilities for the 2-electron singlet-triplet states,
 %
@@
 where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
-Fitting the curve yields $g(B{=}0T)=-0.46$, $g(B{=}9T)=-0.31$, $\Delta_{ST}(B{=}9T)$ = \SI{240}{\micro\electronvolt}, $dS(B{=}0T) = 1.04\ln{2}$, and $dS(B{=}9T) = 1.01\ln{2}$.
+Fitting the data in Fig.~\ref{fig:fig4}c we find $g(B{=}0T)=-0.46$, $g(B{=}9T)=-0.31$, $\Delta_{ST}(B{=}9T)$ = \SI{240}{\micro\electronvolt}, $dS(B{=}0T) = 1.04\ln{2}$, and $dS(B{=}9T) = 1.01\ln{2}$.
 Each of these values is consistent with data in Figs.~\ref{fig:fig4}a and b as well as previous GaAs dot measurements [cite why g should change in high field].
-This fitting confirms that the $dS$ signal can be related directly to a tunable degeneracy in the system.
+This fit confirms that the $dS$ signal can be related directly to a tunable degeneracy in the system.
 

### 2018-02-05 paper/draft.tex

@@
-\documentclass[preprint,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
+\documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
 
@@
 Squares show the locations of ohmic contacts to the 2DEG.
-An electron reservoir is formed between the parallel gates running vertically down the image with a 200nm diameter quantum dot coupled to the right side.
+An electron reservoir is formed between the parallel gates running vertically down the image, with a 200nm diameter quantum dot coupled to the right side.
 The channel can be heated by driving current through the quantum point contact on the left.
 Electrons tunneling between the reservoir and dot are measured with a capacitively-coupled charge sensor.
-(b) Calculated charge sensor signal showing a single transition from $N \rightarrow N+1$ electrons at two temperatures ($T_{Red} > T_{Blue}$).
+(b)  Charge sensor signal showing a single transition from $N \rightarrow N+1$ electrons at two temperatures ($T_{Red} > T_{Blue}$).
 (c) Change in the charge sensor signal with respect to temperature.
-The asymmetry in peak height arises from the shift in $V_0$ which relates to a change in entropy between the $N$ and $N+1$ electron states.
+The asymmetry in peak height arises from a shift in $V_0$ that would arise from a change in entropy between the $N$ and $N+1$ electron states.
 In the case of $dS=0$, $dg$ is anti-symmetric about $V_0$.}
@@
 The fixed pressure condition of Eq.~\ref{eqn:max} is effectively met by working well below the Fermi temperature, $T_F \sim$\SI{5}{\kelvin}, where the pressure is simply the degeneracy pressure \cite{Landau1969}.
-Refs.~\onlinecite{Cooper2009} and ~\onlinecite{Ben-Shach2013} propose schemes to measure the entropy derivative, $\frac{\partial S}{\partial N}$, of the $\nu = \frac{5}{2}$ state via this Maxwell relation, detecting changes in the quasiparticle chemical potential with temperature.
-Our work builds on these ideas to measure the entropy of the few-electron ground states of a quantum dot.
+
+This Maxwell relation forms the basis of two exciting proposals to measure the entropy derivative, $\frac{\partial S}{\partial N}$, of the $\nu = \frac{5}{2}$ state by detecting changes in the quasiparticle chemical potential with temperature, though these have not yet been realized in experiment \cite{Cooper2009,Ben-Shach2013}.
+Our work builds on these proposals to measure the entropy of the few-electron ground states of a quantum dot.
 Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states studied here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
@@
 
-The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a realizes an electron reservoir (central region) in thermal equilibrium with a few-electron quantum dot coupled to its right side, whose occupation is measured using an adjacent charge sensing quantum point contact\cite{Staring2007, Frolov2009, Thierschmann2015}.
-The number of electrons on the dot can be tuned using the gate voltage, $V_G$, to control the chemical potential.
-An electron is added to an $N$ electron dot when the chemical potential to add an electron, $\mu_{N+1}$, drops below the Fermi level of the reservoir, $E_F$.
-Figure 1b illustrates a such a transition, showing the expected step in charge sensor conductance as a function of $V_G$ and thermal broadening by the reservoir temperature, $T_{res}$.
+The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a uses electrostatic gates to realize an electron reservoir (central region; hereafter ``reservoir") in thermal and electrochemical equilibrium with a few-electron quantum dot (``dot") coupled to its right side.
+The occupation of the dot is measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Frolov2009, Thierschmann2015}.
+The $N+1^{\rm st}$ electron is added to an $N$ electron dot when the chemical potential, $\mu_{N+1}$, tuned by the gate voltage, $V_G$, drops below the Fermi level of the reservoir, $E_F$.
+
+Figure 1b illustrates a such a transition---a step in the charge sensor conductance as a function of $V_G$---thermally broadened by the reservoir temperature, $T_{res}$.
 The gate voltage corresponding to midpoint of the transition, $V_0$, marks the chemical potential where the probabilities of finding $N$ or $N+1$ electrons on the dot are equal.
-
-Any entropy change from the $N$ to $N+1$ ground states of the dot should shift the midpoint of the transition, $V_0$, by changing the chemical potential on the dot as in Eq.~\ref{eqn:max}.
-Detecting the shift in $V_0$ with respect to temperature (${\propto}\frac{\partial \mu}{\partial T}$), amounts to a measurement of the entropy difference $dS$ between the $N$ to $N+1$ ground states ($dN=1$).
-In practice, the shift in $V_0$ with temperature is measured by oscillating $T_{res}$ and monitoring any resulting changes in $g_{sens}$ with a lockin amplifier.
+%In practice, the shift in $V_0$ with temperature is measured by oscillating $T_{res}$ and monitoring any resulting changes in $g_{sens}$ with a lockin amplifier.
 If the transition is broadened but not shifted due to heating ($dS=0$), an antisymmetric lineshape is expected from this lockin measurement.
 If the transition is not only broadened but also shifted ($dS,d\mu\neq0$), the change in $g_{sens}$ due to heating will asymmetric, as shown in Fig.~\ref{fig:fig1}c, thus offering a clearly distinguishable signature of entropy for this single charge measurement.
+According to Eq.~\ref{eqn:max}, the chemical potential and therefore $V_0$ shifts with temperature by an amount that is proportional to the entropy difference between the $N$ to $N+1$ ground states ($\delta S_{N\rightarrow N+1}$ for $\delta N=1$).
+This shift is the quantity probed directly in the experiment described below; from these measurements the entropy of the first three energy levels in the quantum dot are built up, one by one.
+Before turning to the experiment in detail, it is helpful to consider the same physics from an alternate point of view.
 
-An explanation based on detailed balance is helpful in understanding how the shift in $\mu_{N+1}$ (with respect to $E_F$) upon heating relates to entropy.
-In general, electrons tunnel back and forth between the dot and reservoir as long as $\mu_{N+1}$ is within thermal broadening of Fermi level, that is, as long as there are available states in both the dot and the reservoir.
+The relation between entropy and a temperature-induced shift in $\mu_{N+1}$ (with respect to $E_F$) can also be understood in the language of detailed balance.
+Generically, the $N+1^{\rm st}$ electron tunnels back and forth between an $N$-electron dot and a reservoir as long as there are available states in both dot and reservoir, that is, as long as $\mu_{N+1}$ is within thermal broadening of $E_F$.
 The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N\rightarrow N+1}$ and $\Gamma_{out}=\Gamma_{N+1\rightarrow N}$, depend on degeneracy of the $N$ and $N+1$ ground states.
 Consider the filling of the first electron state at zero magnetic field, a state with a single, unpaired spin-$\frac{1}{2}$ and therefore a degeneracy of 2.
-An electron tunneling into this state has both spin-up and -down states available.
-Tunneling out, the electron (whether spin up or down) must tunnel into reservoir states with the same spin, that is, only half of the reservoir states are available.
+An electron tunneling in has both spin-up and -down states available.
+Tunneling out, the electron (whether spin-up or -down) must tunnel into reservoir states with the same spin, that is, only half of the reservoir states are available.
 As a result, $\Gamma_{in} = 2\Gamma_{out}$ when $\mu_{N+1}=E_F$.
-Extending this logic to a general case gives the same results as derived from detailed balance \cite{Gustavsson2009},
+Extending this logic to a general case gives the result derived from detailed balance \cite{Gustavsson2009},
 %
@@
 %
-where $\Gamma$ is a coupling constant, $f$ is the Fermi function, and $g_{N/N+1}$ are the degeneracies of the $N$ and $N+1$ electron states.
+where $\Gamma$ is a coupling constant, $f$ is the Fermi function, and $g_{N(N+1)}$ is the degeneracy of the $N(N+1)$ electron state.
 
-The midpoint of the transition between the $N$ and $N+1$ electron states, measured by the charge sensor, occurs when the dot is occupied half the time, that is, when $\Gamma_{in} = \Gamma_{out}$.
-From Eq.~\ref{eqn:rates}, $\Gamma_{in} = \Gamma_{out}$ occurs when $\mu_{N+1} = E_F$ as long as $g_{N}=g_{N+1}$.
-When $g_{N}\neq g_{N+1}$, the midpoint of the transition shifts away from $\mu_{N+1}=E_F$ by an amount that depends on the broadening of the Fermi function, and therefore on $T$.
-Thus, a measurement of how the midpoint of the transition ($V_0$) shifts with T allows the ratio $g_{N+1}/g_{N}$ to be determined, which itself is related to $dS$ through the Boltzmann entropy formula, $S_{N}=k_{B} \ln{g_N}$.
+The midpoint of the transition between the $N$ and $N+1$ electron states ($V_0$), as measured by the charge sensor, occurs when the dot is occupied half the time, that is, when $\Gamma_{in} = \Gamma_{out}$.
+From Eq.~\ref{eqn:rates}, $\Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N+1} = E_F$ when $g_{N}=g_{N+1}$, but shifts away when $g_{N}\neq g_{N+1}$ by an amount that depends on the broadening of the Fermi function, and therefore on $T$.
+A measurement of how $V_0$ shifts with T allows the ratio $g_{N+1}/g_{N}$ to be determined, which itself is related to $dS_{N\rightarrow N+1}$ through the Boltzmann entropy formula, $S_{N}=k_{B} \ln{g_N}$.
 The relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}.
-The thermal technique presented here extends the measurement of entropy (degeneracy) to a wider set of applications, where the tunneling process may not be convenient or even possible to observe directly.
+The thermal technique presented here extends the measurement of entropy (degeneracy) to a wider set of applications, where the tunneling process may not be convenient or even possible to observe in real-time.
 
 %%% fab/measurement details %%%
-The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.
-Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, then \SI{10}{\nano\metre} of $\mathrm{HfO_2}$ was deposited via atomic layer deposition to improve the gating stability to the device.
-Electron beam lithography followed by evaporation of \SI{20}{\nano\metre} of Ti/Au defined the fine gate structures, including the \SI{200}{\nano\metre} diameter quantum dots.
-The measurement was carried out in an dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.
 
@@
 %%% device setup %%%
-Using the gates on the right side of Fig~\ref{fig:fig1}a, the quantum dot was tuned such that the source was tunnel coupled to the reservoir with the drain closed.
-The charge sensing QPC was tuned to a conductance of ${\sim}e^2/h$, where conductance was most sensitive to charge on the dot.
-A small DC voltage bias was applied across the QPC and the measured current was used to calculate the sensor conductance.
-The reservoir temperature was controlled by varying the mixing chamber temperature or Joule heating through the QPC on the left side of the channel.
-In the latter case, the QPC was fixed at \SI{20}{\kilo\ohm} and biased with an AC or DC current source.
-The Joule heating setup gives fast control of the temperature (up to \SI{100}{\hertz}) while keeping the voltage drop across the reservoir negligibly small.
+We now turn to the details of the experiment.
+The quantum dot (Fig.~1a) was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
+The conductance of the charge sensor,  $g_{sens}$, was measured in a DC voltage biased configuration, and tuned to $g_{sens}{\sim}e^2/h$ where it was maximally sensitive to charge on the dot.
+The reservoir temperature could be rapidly controlled (up to at least  \SI{100}{\hertz}) by by Joule heating through the QPC on the left side (Fig.~1a), which was fixed at \SI{20}{\kilo\ohm} and biased with an AC or DC current source.
 
 %%% figs 2a and b %%%
-Fig.~\ref{fig:fig2}a shows the charge sensor conductance as the first electron is added to the dot by tuning $V_G$, at two different temperatures.
+The addition of the first electron to the dot was marked by a decrease in $g_{sens}$ that is well fit by the expected form for a thermally-broadened transition (Fig.~\ref{fig:fig2}a):
+%by tuning $V_G$, at two different temperatures.
 The higher temperature transition curve is noticeably broadened by the increased temperature.
 Assuming the source barrier is sufficiently large, $\Gamma_{in/out}$ are broadened only by the temperature of the reservoir and the conductance takes the form,
+
 %
@@
 %
-where $\Theta = \frac{k_B T}{\alpha e}$, $\alpha$ is the lever arm for the quantum dot plunger gate, and $G_1$ is determined by the cross capacitance between the sensor gates and the plunger gate.
-The dependence of $V_0$ on $\Theta$ captures any shift in $\mu$ due to a change in entropy (degeneracy) across the transition.
-Fits to Eq.~\ref{eqn:g} are seen, in addition to the sensor data, in Fig.~\ref{fig:fig2}a.
-From these fits the transition width, $\Theta$, can be extracted.
-In Fig.~\ref{fig:fig2}b $\Theta$ is plotted as a function of mixing chamber temperature, $T_{MC}$.
-From this plot, it is clear that Eq.~\ref{eqn:g} holds when $T_{MC}\gtrsim$ \SI{100}{\milli\kelvin}.
-For this reason, the mixing chamber temperature remains fixed at \SI{100}{\milli\kelvin} for the remainder of this work.
-Fitting high temperature data in Fig.~\ref{fig:fig2} to the definition of $\Theta$ (with $T=T_{MC}$) yields $\alpha$, making it possible to convert from $V_G$ to $\mu$.
+where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm that converts $V_G$ to quantum dot potentials, and $G_1$ is determined by the cross capacitance between the sensor and the plunger gate.
+The dependence of $V_0$ on $\Theta$ captures any shift in $\mu$ due to a change in entropy across the transition.
+%Fits to Eq.~\ref{eqn:g} are seen, in addition to the sensor data, in Fig.~\ref{fig:fig2}a.
+
+The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} follows the mixing chamber temperature, $T_{MC}$, down to below 100 mK (Fig.~\ref{fig:fig2}b)
+%; $\alpha$ can be calculated based on this linear trend in the high temperature limit.
+The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, with Joule heating giving reservoir temperatures up to \SI{160}{\milli\kelvin}, still cold enough that no orbital levels above the ground state were excited.
+%Fitting high temperature data in Fig.~\ref{fig:fig2} to the definition of $\Theta$ (with $T=T_{MC}$) yields $\alpha$, making it possible to convert from $V_G$ to $\mu$.
 
 %%% figs 2c and d%%%
-Data in Fig.~\ref{fig:fig2}c, and the corresponding fits, show how $dS$ was measured across a single charge transition.
-Fluctuations in $g_{sens}$, were measured as $T_{res}$ was varied using Joule heating with an AC current source ($f_{Heat} =$ \SI{48.7}{\hertz}).
-The change in $T_{res}$ is given by $dT \sim I^{AC}_{Heat} \sim \sin^2(2\omega t)$.
-A calibration for $dT$, using $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
-To avoid thermally accessing excited states of the dot it must be true that $k_B dT \ll \Delta$ where $\Delta$ is the level spacing between the ground and first excited states; which holds for all transitions investigated.
+The data in Fig.~\ref{fig:fig2}c, and corresponding fits, offer an example of how $dS_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ transition.
+A comparison of the 100 and 160 mK data in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as the temperature rises before the midpoint of the transition ($V_G-V_0<0$), whereas the conductance is higher in the warmer curve for $V_G-V_0>0$.
+Oscillating the reservoir temperature by $dT_{res}$ using an AC current, $I^{AC}_{Heat}$, through the heater QPC, while locking in to resultant oscillating $dg_{sens}$ yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
+The expected lineshape of such a curve is given by the derivative of Eq.
+\ref{eqn:g} with respect to temperature, expressed as $dg_{sens}$ due to a temperature change $dT$:
 
-To acquire $dg_{sens}$, current fluctuations through the charge sensor were measured at $2f_{Heat}$ using a lockin amplifier.
-Taking a derivative of Eq.
-\ref{eqn:g} with respect to temperature gives the form of $dg_{sens}$ near a charge transition,
+%If $V_0$ did not change with $T_{res}$, one would expect a perfectly antisymmetric lineshape.
+When $V_0$ changes with  $T_{res}$, on the other hand, as expected when there is an entropy change between the two charge states, the lineshape is not perfectly antisymmetric: this is the case shown in Fig.~\ref{fig:fig2}c.
+
 %
@@
 \label{eqn:dg}
-        dg_{sens}(V, \Theta) &\propto \left[ \frac{V-V_0(\Theta)}{2\Theta} + \delta \right]\times \\
-        				      &\quad\cosh^{-2}\left(\frac{V-V_0(\Theta)}{2\Theta}\right) \nonumber
+        dg_{sens}(V_G, \Theta) &\propto dT \left[ \frac{V_G-V_0}{2\Theta} +\delta \right]\times \\
+        				      &\quad\cosh^{-2}\left(\frac{V_G-V_0}{2\Theta}\right) \nonumber
 \end{align}
@@
 where $\delta=\frac{\partial V_0}{\partial \Theta}$.
-Using the lever arm to convert $V_0$ to a chemical potential $\mu$, the parameter $\delta$ can be related to the change in entropy through Eq.~\ref{eqn:max},
+Using the lever arm to convert $V_0$ to chemical potential, one sees that the parameter $\delta$ is simply the change in entropy scaled by Boltzmann's constant:
 %
@@
         \frac{1}{k_B} \frac{\partial \mu}{\partial T} = 
-        -\frac{1}{k_B} \partial S
+        -\frac{1}{k_B} \partial S_{N\rightarrow N+1}
 \end{align}
 %
-Fits to Eq.~\ref{eqn:dg} are shown for $\delta=0$ and a best fit to $\delta$.
-From these fits it is clear $\delta\neq0$ is necessary to properly fit the asymmetry in peak height, with the best fit being $\delta \approx \ln{2}$.
-For an N-electron macrostate on the quantum dot, entropy is given by the Boltzmann entropy,
-%
-\begin{align}
-\label{eqn:S}
-        S &= k_B \ln{\Omega}
-\end{align}
-%
-where $\Omega$ is the spin degeneracy of the ground state, equal to the number of microstates available. For the 0-1 transition, $dS =  k_B\ln{2} - k_B \ln{1} = k_B\ln{2}$.
 
-%%% fig 2e %%%
-Note that $\delta$ is a fit parameter independent of $dT$ and $\alpha$.
-Fig.~\ref{fig:fig2}e shows that $dS$, as determined from fits to $dg_{sens}$ data, remains constant over a range of $dT$ ($I^{AC}_{Heat}$).
-The vertical scale on the right side of Fig.
-\ref{fig:fig2}e, $\delta$ in units of gate voltage per unit temperature, illustrates the necessity of the lockin measurement; device stability and small signals made it difficult for $delta$ to be determined directly from $g_{sens}$ at different $T$.
-Without any additional calibration, it is possible to measure $dS$ directly from the lockin amplifier signal, $dg_{sens}$.
+From Eq.~\ref{eqn:dg}, $dg_{sens}(V_G)$ would perfectly antisymmetric around $V_0$ if $\partial S_{N\rightarrow N+1}$ were zero.
+Fits to the data in Fig.~\ref{fig:fig2}c illustrate clearly that $\partial S_{0\rightarrow 1}=0$ is inconsistent with the data;  the best fit is found for $\partial S_{0\rightarrow 1}=0.71\times k_B$.
+Indeed, this is what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate 1-electron state one expects $S_1=k_B\ln{2}$, giving $dS_{0\rightarrow 1}\equiv S_1 = S_0 =k_B\ln{2}$.%%% fig 2e %%%
+Note that $\delta$ is a fit parameter that is independent of $dT$ and $\alpha$.
+Fig.~\ref{fig:fig2}e shows that $dS$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $dT$ ($I^{AC}_{Heat}$).
+Although the extracted $\delta$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $dS$, is determined directly from the fit to $g_{sens}$ without any additional calibration.
+%The vertical scale on the right side of Fig.
+\ref{fig:fig2}e converts $\delta$ to units of gate voltage per unit temperature; the tiny magnitude of this signal  the necessity of the lockin measurement; device stability and small signals made it difficult for $delta$ to be determined directly from $g_{sens}$ at different $T$.
 
@@
 
-To confirm that the measured signal derives from the electron spin, the behavior of $dS$ was investigated as a function of parallel magnetic field.
-Fig.~\ref{fig:fig3}c shows $dS$ as a function of applied field for the 0-1 and 2-3 electron transitions.
-The 2-electron ground state is a spin singlet, while the 3-electron ground state is same singlet with an additional unpaired electron, making the field-dependent behavior of these transitions identical where $g \mu_{B} B$ is less than the excited state energies.
-Zeeman splitting, measured directly in Fig.
-\ref{fig:fig2}b, lifts the spin degeneracy of the unpaired electrons and the entropy of the 1- and 3- electron ground states goes to zero with increasing field
+Confirmation that the measured $dS$ derives from spin degeneracy can be seen in its evolution with in-plane magnetic field, $B_\parallel$.
+Figure \ref{fig:fig3}a [REMOVE PANELS AB] compares $dS(B_\parallel)$ for the 0-1 and 2-3 electron transitions.
+The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $dS_{0 \rightarrow 1}$ and $dS_{2 \rightarrow 3}$ correspond to transitions from total spin zero $(S_0=S_2=0)$ to total spin one-half, and one might expect identical field-dependent behaviors for $dS_{0\rightarrow 1}$ and $dS_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies.
 
-The behavior of $dS$ as a function of magnetic field can be understood using the Gibbs entropy,
+The entropies of 1- and 3-electron states are suppressed when the Zeeman splitting lifts the spin degeneracy of the unpaired electron, following the Gibbs entropy for a two-level system:
 %
@@
 \label{eqn:gibbs}
-        S &= k_B \sum_{i=\pm} p_{i}(B, T) \ln{ p_{i}(B,T) }
+        S &= k_B \sum_{i=\pm} p_{i}(B_\parallel, T) \ln{ p_{i}(B_\parallel,T) }
 \end{align}
 %
-where $p_{i}(B, T)$ is the probability of the system being in the i$^{th}$ spin state at a given field and temperature.
-For states with a single unpaired electron, $p_{i}(B, T)$ can be written as a two-level system,
-%
-\begin{align}
-\label{eqn:p}
-        p_{\pm}(B, T) &= \frac{1}{1+ e^{\mp \frac{g\mu_B B}{k_B T}}}
-\end{align}
-%
-where $\pm$ represent the spin up/down states.
-Fits to Eqs.~\ref{eqn:gibbs} and \ref{eqn:p} are shown in Fig \ref{fig:fig3}c for each transition.
-The fits allow for peak height, g-factor, and a vertical offset as free parameters with $T$ fixed at $T_{MC}$.
-From these fits we find $dS(B=0)=0.92 \ln{2}$ and $g=-0.33$ for the 0-1 transition.
-Discrepancy between $g$ and the result shown in Fig.
-\ref{fig:fig3}b, is understood from the change in shape of the quantum dot when tuning between the $g_{dot}$ and $g_{sens}$ measurements [cite?].
-The entropy agrees well with the expected $k_{B} \ln{2}$ at zero-field and goes to zero as expected with $B_{\parallel}$
+where $p_{\pm}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_{\parallel}}{k_B T}})^{-1}$ are the probabilities for the system to be in $+/-$ (up/down) spin states at a given field and temperature.
+Fits to the lineshape in Eqn.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, allowing for peak height, a vertical offset, and the ratio $g/T$ as free parameters.
+
+The entropy measurement agrees quantitatively with the expected $k_{B} \ln{2}$ at $B_\parallel=0$, collapsing to zero at high field when spin degeneracy is broken.
+Using a $T=T_{res}$ of 130 \SI{100}{\milli\kelvin} that is midway between the low ($T_{MC}$) and high ($T_{MC}+dT$) points of the temperature oscillation yields $g=0.43$ or $g=0.4$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions respectively, consistent with the value $g=-0.44$ expected for GaAs and measured via bias spectroscopy in a separate measurement (Figs.~\ref{fig:fig3}bc).
+At a qualitative level, the high-field crossover to a perfectly antisymmetric lineshape for $dg_{sens}(V_G)$ at the charge transition clearly indicates $\delta$ from Eqn.~\ref{eqn:dg} going to zero, corresponding to no entropy change between the two charge states (Figs.~\ref{fig:fig3}de).
 
@@
 
-The low field (\SI{<5}{\tesla}) data in Fig.
-\ref{fig:fig4}c for the 1-2 electron transition is understood as the inverse of Fig \ref{fig:fig3}c.
-The 2-electron ground state remains in the spin singlet state with zero entropy while 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
-At high fields, the 1-electron ground state remains non-degenerate, while the 2-electron ground state becomes two-fold degenerate at \SI{9}{\tesla} where the singlet ($S$) and triplet ($T_+$) states cross.
-The singlet-triplet crossing is seen clearly in Fig.~\ref{fig:fig4}b.
+The entropy of the 0 and 2-electron states are both zero at low magnetic field, so $dS$ for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}a) can be understood as the inverse of Fig \ref{fig:fig3}a as long as $B_\parallel$ is less than around \SI{5}{\tesla}.
+There, the 2-electron ground state remains in the spin singlet state with zero entropy while 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
+At higher field, the 1-electron ground state remains non-degenerate while the 2-electron ground state becomes two-fold degenerate where the singlet ($S$) and triplet ($T_+$) states cross.
+The singlet-triplet crossing is seen clearly around at \SI{9}{\tesla} in bias spectroscopy data for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}bc).
 
-The entropy for the 1-2 transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities given by Eq.~\ref{eqn:p} for the 1-electron states and the following probabilities for the 2-electron singlet-triplet states,
-%
-\begin{align}
-\label{eqn:pst}
-        p_{S/T}(B, T) &= \frac{1}{1+ e^{\mp \frac{g\mu_B B - \Delta_{ST}}{k_B T}}}
-\end{align}
-%
-where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
+The field-dependent entropy measurement for the 1-2 transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{S/T}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron singlet-triplet states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
 Fitting the data in Fig.~\ref{fig:fig4}c we find $g(B{=}0T)=-0.46$, $g(B{=}9T)=-0.31$, $\Delta_{ST}(B{=}9T)$ = \SI{240}{\micro\electronvolt}, $dS(B{=}0T) = 1.04\ln{2}$, and $dS(B{=}9T) = 1.01\ln{2}$.
@@
 
+\noindent \textbf{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.
+Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, then \SI{10}{\nano\metre} of $\mathrm{HfO_2}$ was deposited via atomic layer deposition to improve the gating stability to the device.
+Electron beam lithography followed by evaporation of \SI{20}{\nano\metre} of Ti/Au defined the fine gate structures, including the \SI{200}{\nano\metre} diameter quantum dots.
+The measurement was carried out in an dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.
+
+The conductance of the charge sensor was measured at a DC voltage bias of XXX uV, with the current read out directly or fed into a lockin amplifier.
+The temperature of the reservoir could be raised above $T_MC$ (to $T_MC + dT$) using a current biased through the left (heater) QPC.
+DC heating currents were used to calibrate heating efficiency in this mode, while AC currents at $f_{Heat} =$ \SI{48.7}{\hertz} yielded oscillations in $T_{res}$ at \SI{97.4}{\hertz}.
+Locking the current measurement through the sensor QPC into the second harmonic of $f_{Heat}$ thus provided a measurement of the variation of $g_{sens}$ with $dT$.
+A calibration for $dT$, using $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
+
 %\acknowledgments

### 2018-02-06 paper/draft.tex
some figure updates and a few revisions

@@
-\documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
+%%%% outstanding mysteries %%%%%
+% error bar on 0-1 peak height (mention in text)
+% can I cite someone as to why \Delta_ST changes with field
+% dS or \partial S?
+% why does \partial S/ \partial N
+
+\documentclass[preprint,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
 
@@
 \thanks{The raw data and Python code used for the figures and analysis can be found at \url{https://github.com/nikhartman/spin_entropy}}
-\affiliation{University of British Columbia, Vanouver, BC, Canada}
+\affiliation{University of British Columbia, Vancouver, BC, Canada}
 \author{Saeed Fallahi}
@@
 \author{Christian Olsen}
-\affiliation{University of British Columbia, Vanouver, BC, Canada}
+\affiliation{University of British Columbia, Vancouver, BC, Canada}
 \author{Silvia Folk}
-\affiliation{University of British Columbia, Vanouver, BC, Canada}
+\affiliation{University of British Columbia, Vancouver, BC, Canada}
 \author{Mohammad Samani}
@@
 \altaffiliation{Fields Institute for Research in Mathematical Sciences, Toronto, ON, Canada}
-\affiliation{University of British Columbia, Vanouver, BC, Canada}
+\affiliation{University of British Columbia, Vancouver, BC, Canada}
 \author{Michael Manfra}
@@
 \author{Joshua Folk}
-\affiliation{University of British Columbia, Vanouver, BC, Canada}
+\affiliation{University of British Columbia, Vancouver, BC, Canada}
 \date{\today}
@@
 
-Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
+%Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
 Such measurements are typically based on bulk properties, such as heat capacity, that are straightforward to observe in macroscopic samples but exceedingly difficult to access in mesoscopic systems that may consist of just a few electrons.
@@
 The asymmetry in peak height arises from a shift in $V_0$ that would arise from a change in entropy between the $N$ and $N+1$ electron states.
-In the case of $dS=0$, $dg$ is anti-symmetric about $V_0$.}
+In the case of $dS=0$, $dg_{sens}$ is anti-symmetric about $V_0$.}
 \end{figure}
@@
 (b) Lockin measurement of $dg_{sens}$ with $dT \sim 60mK$.
-Fits to $dg$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a function of mixing chamber temperature.
+Fits to $dg_{sens}$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a function of mixing chamber temperature.
 The highlighted, linear region is where the tunnel rates are determined only by temperature broadening.
@@
 (b) Fixed bias transport data showing fits to the Zeeman splitting of the ground state energy from which $g = -0.44$ is extracted.
-(c) Change in entropy, determined from $dg$ fits at varying parallel magnetic field.
+(c) Change in entropy, determined from $dg_{sens}$ fits at varying parallel magnetic field.
 The $N=0 \rightarrow 1$ and $2 \rightarrow 3$ data are overlaid here to show the similar behavior of these states at low field.
-(d) and (e) show characteristic $dg$ traces from which the data in (c) were extracted.
+(d) and (e) show characteristic $dg_{sens}$ traces from which the data in (c) were extracted.
 These data points are show as large markers in (c)}
@@
 $g$ is determined using $T_0$ and $T_+$ fits.
-(c) Change in entropy, extracted from $dg$ fits at varying parallel field.
+(c) Change in entropy, extracted from $dg_{sens}$ fits at varying parallel field.
 As the field goes from 0 to 10T, entropy of the 2-electron state goes from $0  \rightarrow \ln{2}$, while the entropy of the 1-electron state goes from $\ln{2} \rightarrow 0$.
-Fit to this behavior (dashed) is described in the text (d), (e), and (f) show characteristic $dg$ traces from which the data in (c) were extracted.
+Fit to this behavior (dashed) is described in the text (d), (e), and (f) show characteristic $dg_{sens}$ traces from which the data in (c) were extracted.
 These data points are show as large markers in (c)}
@@
 The field-dependent entropy measurement for the 1-2 transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{S/T}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron singlet-triplet states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
-Fitting the data in Fig.~\ref{fig:fig4}c we find $g(B{=}0T)=-0.46$, $g(B{=}9T)=-0.31$, $\Delta_{ST}(B{=}9T)$ = \SI{240}{\micro\electronvolt}, $dS(B{=}0T) = 1.04\ln{2}$, and $dS(B{=}9T) = 1.01\ln{2}$.
-Each of these values is consistent with data in Figs.~\ref{fig:fig4}a and b as well as previous GaAs dot measurements [cite why g should change in high field].
-This fit confirms that the $dS$ signal can be related directly to a tunable degeneracy in the system.
+The fit allows for an offset from $dS=0$, away from the degenerate points, to compensate for non-linearities in the charge sensor.
+From the fit we find the entropies at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are within 5\% of the expected values, $\mp k_B \ln{2}$.
+The extracted value of $g = 0.394$ from the low-field peak agrees well with the fit in Fig.~\ref{fig:fig3}a.
+At the high-field singlet-triplet degeneracy, $g = 0.586$ in the fit.
+This unexpected g-factor is explained by a shifting of the $T_{0}$ with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work.
+The high quality of this Gibbs entropy fit confirms $dS$ can be related directly to a tunable degeneracy in the system.
 
@@
 
-\noindent \textbf{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.
+\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.
 Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, then \SI{10}{\nano\metre} of $\mathrm{HfO_2}$ was deposited via atomic layer deposition to improve the gating stability to the device.
@@
 The temperature of the reservoir could be raised above $T_MC$ (to $T_MC + dT$) using a current biased through the left (heater) QPC.
-DC heating currents were used to calibrate heating efficiency in this mode, while AC currents at $f_{Heat} =$ \SI{48.7}{\hertz} yielded oscillations in $T_{res}$ at \SI{97.4}{\hertz}.
-Locking the current measurement through the sensor QPC into the second harmonic of $f_{Heat}$ thus provided a measurement of the variation of $g_{sens}$ with $dT$.
-A calibration for $dT$, using $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
+A calibration for $dT$ in this mode, using DC current bias $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
+Applying AC current at $f_{Heat} =$ \SI{48.7}{\hertz} yields oscillations in $T_{res}$ at $2f_{heat}$; to leading order $dT_{res} \sim P \sim \cos(2*(2 \pi f_{heat})t)$.
+Variations in $g_{sens}$ with $dT$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
 

### 2018-02-07 paper/draft.tex
nik edits on feb 6

@@
 
-\documentclass[preprint,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
+\documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
 
@@
 \email{nik.hartman@gmail.com}
-\thanks{The raw data and Python code used for the figures and analysis can be found at \url{https://github.com/nikhartman/spin_entropy}}
+\thanks{The raw data and Python code used for all figures and analysis can be found at \url{https://github.com/nikhartman/spin_entropy}}
 \affiliation{University of British Columbia, Vancouver, BC, Canada}
@@
 
-\begin{abstract}
-
+%\begin{abstract}
+%
 %Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
@@
 The entropy of a single spin ($k_B \ln{2}$) is measured within 8\% accuracy, as is the entropy arising at the magnetic field-driven singlet-triplet crossing for two electrons.
-
-\end{abstract}
+%
+%\end{abstract}
 
@@
 %%%%%%% intro material %%%%%%%%%
-The thermodynamic properties of electronic systems can offer important insights into the nature of their ground states, and probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.
+\textbf{The thermodynamic properties of electronic systems can offer important insights into the nature of their ground states, and probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.
 Systems that are difficult to clearly identify through standard conductance measurements may be studied more in depth if a thermodynamic measurement can be made.
@@
 Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}.
-A more direct test for the two-channel Kondo state would be a confirmation of its entropy ($\frac{1}{2} k_B \ln{2}$), that should remain down to arbitrarily low temperatures \cite{Alkurtass2016}.
+A more direct test for the two-channel Kondo state would be a confirmation of its entropy ($\frac{1}{2} k_B \ln{2}$), that should remain down to arbitrarily low temperatures \cite{Alkurtass2016}.}
 
@@
 Squares show the locations of ohmic contacts to the 2DEG.
-An electron reservoir is formed between the parallel gates running vertically down the image, with a 200nm diameter quantum dot coupled to the right side.
-The channel can be heated by driving current through the quantum point contact on the left.
+An electron reservoir is formed between the parallel gates running vertically down the image.
+The reservoir can be heated by driving current through the quantum point contact on the left.
+A 200nm diameter quantum dot is coupled to the right side of the channel.
 Electrons tunneling between the reservoir and dot are measured with a capacitively-coupled charge sensor.
-(b)  Charge sensor signal showing a single transition from $N \rightarrow N+1$ electrons at two temperatures ($T_{Red} > T_{Blue}$).
-(c) Change in the charge sensor signal with respect to temperature.
-The asymmetry in peak height arises from a shift in $V_0$ that would arise from a change in entropy between the $N$ and $N+1$ electron states.
-In the case of $dS=0$, $dg_{sens}$ is anti-symmetric about $V_0$.}
+(b) and (c) Charge sensor signal for a single transition from $N \rightarrow N+1$ electrons at two temperatures ($T_{Red} > T_{Blue}$) showing the two possible cases for $\frac{\partial \mu}{\partial T}$.}
 \end{figure}
@@
 Entropy can be probed effectively in 3D macroscopic samples via measurements of heat capacity, but the heat capacities of single electrons or quasiparticles are much too small to measure directly; even the 2D sheet of quasiparticles in $\nu = \frac{5}{2}$ fractional quantum Hall samples has a heat capacity that vanishes in comparison to that of the host crystal.
-Rather than attempt to resolve such infinitesimal signals, the problem can be avoided by converting a change in entropy to changes in charge--a quantity that is easily detected at the single particle level.
-Our approach is analogous to the milestone of spin-to-charge conversion, first demonstrated in GaAs quantum dots in 2004, by which undetectably-small magnetic moments of a single spin were transformed into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
+Rather than attempt to resolve such infinitesimal signals, the problem can be avoided by converting changes in entropy to changes in charge \textemdash a quantity that is easily detected at the single particle level.
+Our approach is analogous to the milestone of spin-to-charge conversion by which undetectably-small magnetic moments of a single spin were transformed into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
 
@@
 %
-that connects changes in entropy, $S$, (as well as particle number, $N$, and temperature, $T$) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control.
-The fixed pressure condition of Eq.~\ref{eqn:max} is effectively met by working well below the Fermi temperature, $T_F \sim$\SI{5}{\kelvin}, where the pressure is simply the degeneracy pressure \cite{Landau1969}.
+that connects changes in entropy, particle number, and temperature ($S$, $N$, and $T$, respectively) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control.
+The fixed pressure condition of Eq.~\ref{eqn:max} is effectively met by working well below the Fermi temperature, $T_F \sim$\SI{5}{\kelvin}, where degeneracy pressure dominates \cite{Landau1969}.
 
-This Maxwell relation forms the basis of two exciting proposals to measure the entropy derivative, $\frac{\partial S}{\partial N}$, of the $\nu = \frac{5}{2}$ state by detecting changes in the quasiparticle chemical potential with temperature, though these have not yet been realized in experiment \cite{Cooper2009,Ben-Shach2013}.
+The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two exciting theoretical proposals to measure the entropy derivative, $\frac{\partial S}{\partial N}$, of the $\nu = \frac{5}{2}$ state by detecting changes in the quasiparticle chemical potential with temperature \cite{Cooper2009,Ben-Shach2013}.
 Our work builds on these proposals to measure the entropy of the few-electron ground states of a quantum dot.
 Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states studied here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-Our experiment demonstrates a direct entropy measurement on a few-particle system; in the future, the method can be easily extended as a probe into the nature of more exotic systems, such as topologically non-trivial Majorana and other non-Abelian states.
+Our experiment demonstrates a direct entropy measurement is possible on a few-particle system.
+In the future, the method can be utilized as a probe into the nature of more exotic systems, such as topologically non-trivial Majorana and other non-Abelian states.
 
@@
 The occupation of the dot is measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Frolov2009, Thierschmann2015}.
-The $N+1^{\rm st}$ electron is added to an $N$ electron dot when the chemical potential, $\mu_{N+1}$, tuned by the gate voltage, $V_G$, drops below the Fermi level of the reservoir, $E_F$.
+An additional electron is added to an $N$ electron dot when the chemical potential, $\mu_{N+1}$, drops below the Fermi level of the reservoir, $E_F$.
+Figure 1b illustrates a such a transition \textemdash a step in the charge sensor conductance as a function of plunger gate voltage, $V_G$, which tunes the chemical potential on the dot, $\mu_{dot}$ \textemdash thermally broadened by the reservoir temperature, $T_{res}$.
+The gate voltage corresponding to midpoint of the transition, $V_0$, marks the chemical potential at which the probabilities of finding $N$ or $N+1$ electrons on the dot are equal.
 
-Figure 1b illustrates a such a transition---a step in the charge sensor conductance as a function of $V_G$---thermally broadened by the reservoir temperature, $T_{res}$.
-The gate voltage corresponding to midpoint of the transition, $V_0$, marks the chemical potential where the probabilities of finding $N$ or $N+1$ electrons on the dot are equal.
-%In practice, the shift in $V_0$ with temperature is measured by oscillating $T_{res}$ and monitoring any resulting changes in $g_{sens}$ with a lockin amplifier.
-If the transition is broadened but not shifted due to heating ($dS=0$), an antisymmetric lineshape is expected from this lockin measurement.
-If the transition is not only broadened but also shifted ($dS,d\mu\neq0$), the change in $g_{sens}$ due to heating will asymmetric, as shown in Fig.~\ref{fig:fig1}c, thus offering a clearly distinguishable signature of entropy for this single charge measurement.
-According to Eq.~\ref{eqn:max}, the chemical potential and therefore $V_0$ shifts with temperature by an amount that is proportional to the entropy difference between the $N$ to $N+1$ ground states ($\delta S_{N\rightarrow N+1}$ for $\delta N=1$).
-This shift is the quantity probed directly in the experiment described below; from these measurements the entropy of the first three energy levels in the quantum dot are built up, one by one.
-Before turning to the experiment in detail, it is helpful to consider the same physics from an alternate point of view.
-
-The relation between entropy and a temperature-induced shift in $\mu_{N+1}$ (with respect to $E_F$) can also be understood in the language of detailed balance.
-Generically, the $N+1^{\rm st}$ electron tunnels back and forth between an $N$-electron dot and a reservoir as long as there are available states in both dot and reservoir, that is, as long as $\mu_{N+1}$ is within thermal broadening of $E_F$.
+The relation between entropy and a temperature-induced shift in $\mu_{N+1}$ (with respect to $E_F$) can be understood in the language of detailed balance.
+The $N+1^{\rm st}$ electron tunnels back and forth between an $N$-electron dot and a reservoir as long as there are available states in both dot and reservoir; true when $\mu_{N+1}$ is within thermal broadening of $E_F$.
 The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N\rightarrow N+1}$ and $\Gamma_{out}=\Gamma_{N+1\rightarrow N}$, depend on degeneracy of the $N$ and $N+1$ ground states.
-Consider the filling of the first electron state at zero magnetic field, a state with a single, unpaired spin-$\frac{1}{2}$ and therefore a degeneracy of 2.
-An electron tunneling in has both spin-up and -down states available.
+Consider the filling of the first electron state, which has a single, unpaired spin-$\frac{1}{2}$ and, therefore, a degeneracy of 2.
+An electron tunneling into the dot has both spin-up and -down states available.
 Tunneling out, the electron (whether spin-up or -down) must tunnel into reservoir states with the same spin, that is, only half of the reservoir states are available.
@@
 \begin{align}
-	\Gamma_{in} &=  g_{N+1} \Gamma f(E_F - \mu_{N+1}) \label{eqn:rates}\\
-	\Gamma_{out} &= g_{N} \Gamma [1 - f(E_F - \mu_{N+1})] \nonumber
+	\Gamma_{in} &=  g_{N+1} \Gamma f(E_F - \mu_{N+1}) \nonumber \\
+	\Gamma_{out} &= g_{N} \Gamma [1 - f(E_F - \mu_{N+1})] \label{eqn:rates}
 \end{align}
@@
 
-The midpoint of the transition between the $N$ and $N+1$ electron states ($V_0$), as measured by the charge sensor, occurs when the dot is occupied half the time, that is, when $\Gamma_{in} = \Gamma_{out}$.
-From Eq.~\ref{eqn:rates}, $\Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N+1} = E_F$ when $g_{N}=g_{N+1}$, but shifts away when $g_{N}\neq g_{N+1}$ by an amount that depends on the broadening of the Fermi function, and therefore on $T$.
-A measurement of how $V_0$ shifts with T allows the ratio $g_{N+1}/g_{N}$ to be determined, which itself is related to $dS_{N\rightarrow N+1}$ through the Boltzmann entropy formula, $S_{N}=k_{B} \ln{g_N}$.
-The relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}.
-The thermal technique presented here extends the measurement of entropy (degeneracy) to a wider set of applications, where the tunneling process may not be convenient or even possible to observe in real-time.
+The midpoint of the transition between the $N$ and $N+1$ electron states ($V_0$), as measured by the charge sensor, occurs when $\Gamma_{in} = \Gamma_{out}$ and the dot is occupied half the time.
+From Eq.~\ref{eqn:rates}, $\Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N+1} = E_F$ when $g_{N}=g_{N+1}$.
+When $g_{N}\neq g_{N+1}$, $\mu_{N+1}$ shifts away from $E_F$ by an amount that depends on the broadening of the Fermi function, and therefore on $T$.
+A measurement of how $V_0$ shifts with T allows the ratio $g_{N+1}/g_{N}$ to be determined, which itself is related to $dS_{N\rightarrow N+1}$ through the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
 
-%%% fab/measurement details %%%
+Looking back to Eq.~\ref{eqn:max}, the shift in $\mu_{N+1}$, and therefore $V_0$, with temperature is proportional to the entropy difference between the $N$ to $N+1$ ground states ($\partial S_{N\rightarrow N+1}$ for $\partial N=1$).
+This shift, $\partial V_0$ as a function of $\partial T$, is the quantity probed directly in the experiment described below.
+From these measurements the entropies of the first three energy levels in the quantum dot are built up, one by one.
+While the relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}, the thermal technique presented in this work extends the measurement of entropy (degeneracy) to a wider set of applications, where the tunneling process may not be convenient, or even possible, to observe in real-time.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_2.pdf}
-        \caption{\label{fig:fig2}(a) Charge sensor data for $N=0 \rightarrow 1$ at 100 and 160mK.
-Temperature is set by DC current through the QPC heater.
-(b) Lockin measurement of $dg_{sens}$ with $dT \sim 60mK$.
+        \caption{\label{fig:fig2}(a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater.
+(b) Lock-in measurement of $dg_{sens}$ with $dT \sim 60mK$.
 Fits to $dg_{sens}$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a function of mixing chamber temperature.
-The highlighted, linear region is where the tunnel rates are determined only by temperature broadening.
+The highlighted region shows roughly where tunnel rates are determined only by temperature broadening.
 The lever arm $\alpha$ is calculated by fitting a straight line to this region.
 (d) $\Theta$ as a function of DC current through the QPC heater.
-Linear fit is used to convert between $I_{heat}$ and $dT$, with $R_{QPC} = $ \SI{20}{\kilo\ohm} (e) Change in entropy as a function of AC current through the QPC heater.
+Fit is used to convert between $I_{heat}$ and $dT$, with $R_{QPC} = $ \SI{20}{\kilo\ohm} (e) Change in entropy as a function of AC current through the QPC heater.
 Top axis shows corresponding $dT$.
-Right axis shows shift in $V_0$ per unit temperature.}
+Right axis shows shift in $\partial V_0$ per unit temperature.}
 \end{figure}
@@
 %%% device setup %%%
-We now turn to the details of the experiment.
-The quantum dot (Fig.~1a) was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
-The conductance of the charge sensor,  $g_{sens}$, was measured in a DC voltage biased configuration, and tuned to $g_{sens}{\sim}e^2/h$ where it was maximally sensitive to charge on the dot.
-The reservoir temperature could be rapidly controlled (up to at least  \SI{100}{\hertz}) by by Joule heating through the QPC on the left side (Fig.~1a), which was fixed at \SI{20}{\kilo\ohm} and biased with an AC or DC current source.
+To proceed with the entropy measurement, the quantum dot (Fig.~\ref{fig:fig1}a) was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
+The conductance of the charge sensor,  $g_{sens}$, was measured in a DC voltage biased configuration, and tuned to $g_{sens}{\sim}e^2/h$ where it was most sensitive to charge on the dot.
+The reservoir temperature could be rapidly controlled (up to at least  \SI{100}{\hertz}) by Joule heating through the QPC on the left side (Fig.~\ref{fig:fig1}a), which was fixed at \SI{20}{\kilo\ohm} and biased with an AC or DC current source.
 
@@
 The addition of the first electron to the dot was marked by a decrease in $g_{sens}$ that is well fit by the expected form for a thermally-broadened transition (Fig.~\ref{fig:fig2}a):
-%by tuning $V_G$, at two different temperatures.
-The higher temperature transition curve is noticeably broadened by the increased temperature.
-Assuming the source barrier is sufficiently large, $\Gamma_{in/out}$ are broadened only by the temperature of the reservoir and the conductance takes the form,
-
 %
@@
 %
-where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm that converts $V_G$ to quantum dot potentials, and $G_1$ is determined by the cross capacitance between the sensor and the plunger gate.
+where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm that converts $V_G$ to $\mu_{dot}$, and $G_1$ is determined by the cross capacitance between the charge sensor and plunger gate.
 The dependence of $V_0$ on $\Theta$ captures any shift in $\mu$ due to a change in entropy across the transition.
-%Fits to Eq.~\ref{eqn:g} are seen, in addition to the sensor data, in Fig.~\ref{fig:fig2}a.
 
-The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} follows the mixing chamber temperature, $T_{MC}$, down to below 100 mK (Fig.~\ref{fig:fig2}b)
-%; $\alpha$ can be calculated based on this linear trend in the high temperature limit.
-The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, with Joule heating giving reservoir temperatures up to \SI{160}{\milli\kelvin}, still cold enough that no orbital levels above the ground state were excited.
-%Fitting high temperature data in Fig.~\ref{fig:fig2} to the definition of $\Theta$ (with $T=T_{MC}$) yields $\alpha$, making it possible to convert from $V_G$ to $\mu$.
+The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} follows the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
+The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work with Joule heating giving reservoir temperatures up to \SI{250}{\milli\kelvin}.
+Measurements of $\partial S$ are made at $dT_{res} = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
 
@@
 A comparison of the 100 and 160 mK data in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as the temperature rises before the midpoint of the transition ($V_G-V_0<0$), whereas the conductance is higher in the warmer curve for $V_G-V_0>0$.
-Oscillating the reservoir temperature by $dT_{res}$ using an AC current, $I^{AC}_{Heat}$, through the heater QPC, while locking in to resultant oscillating $dg_{sens}$ yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
-The expected lineshape of such a curve is given by the derivative of Eq.
-\ref{eqn:g} with respect to temperature, expressed as $dg_{sens}$ due to a temperature change $dT$:
-
-%If $V_0$ did not change with $T_{res}$, one would expect a perfectly antisymmetric lineshape.
-When $V_0$ changes with  $T_{res}$, on the other hand, as expected when there is an entropy change between the two charge states, the lineshape is not perfectly antisymmetric: this is the case shown in Fig.~\ref{fig:fig2}c.
-
+Oscillating the reservoir temperature by $dT_{res}$ using an AC current, $I^{AC}_{Heat}$, measuring oscillations in $g_{sens}$ with a lock in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
+The expected lineshape of such a curve is given by the derivative of Eq.~\ref{eqn:g} with respect to temperature, expressed as $dg_{sens}$ due to a temperature change $dT$:
 %
@@
 \label{eqn:dg}
-        dg_{sens}(V_G, \Theta) &\propto dT \left[ \frac{V_G-V_0}{2\Theta} +\delta \right]\times \\
-        				      &\quad\cosh^{-2}\left(\frac{V_G-V_0}{2\Theta}\right) \nonumber
+        dg_{sens}(V_G, \Theta) &\propto dT \left[ \frac{V_G-V_{0}(\Theta)}{2\Theta} +\delta \right]\times \\
+        				      &\quad\cosh^{-2}\left(\frac{V_G-V_{0}(\Theta)}{2\Theta}\right) \nonumber
 \end{align}
@@
 where $\delta=\frac{\partial V_0}{\partial \Theta}$.
-Using the lever arm to convert $V_0$ to chemical potential, one sees that the parameter $\delta$ is simply the change in entropy scaled by Boltzmann's constant:
+Using the lever arm to convert $V_0$ to chemical potential, the parameter $\delta$ is expressed as the change in entropy scaled by Boltzmann's constant:
 %
@@
 
-From Eq.~\ref{eqn:dg}, $dg_{sens}(V_G)$ would perfectly antisymmetric around $V_0$ if $\partial S_{N\rightarrow N+1}$ were zero.
+From Eqs.~\ref{eqn:dg} and \ref{eqn:delta}, $dg_{sens}(V_G)$ would be perfectly antisymmetric around $V_0$ if $\partial S_{N\rightarrow N+1}$ were zero.
 Fits to the data in Fig.~\ref{fig:fig2}c illustrate clearly that $\partial S_{0\rightarrow 1}=0$ is inconsistent with the data;  the best fit is found for $\partial S_{0\rightarrow 1}=0.71\times k_B$.
-Indeed, this is what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate 1-electron state one expects $S_1=k_B\ln{2}$, giving $dS_{0\rightarrow 1}\equiv S_1 = S_0 =k_B\ln{2}$.%%% fig 2e %%%
-Note that $\delta$ is a fit parameter that is independent of $dT$ and $\alpha$.
+Indeed, this is what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate 1-electron state one expects $S_1=k_B\ln{2}$, giving $dS_{0\rightarrow 1}\equiv S_1 = S_0 =k_B\ln{2}$.
 Fig.~\ref{fig:fig2}e shows that $dS$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $dT$ ($I^{AC}_{Heat}$).
 Although the extracted $\delta$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $dS$, is determined directly from the fit to $g_{sens}$ without any additional calibration.
-%The vertical scale on the right side of Fig.
-\ref{fig:fig2}e converts $\delta$ to units of gate voltage per unit temperature; the tiny magnitude of this signal  the necessity of the lockin measurement; device stability and small signals made it difficult for $delta$ to be determined directly from $g_{sens}$ at different $T$.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_3.pdf}
-        \caption{\label{fig:fig3}(a) Transport data through the quantum dot showing the $N=0 \rightarrow 1$ transition.
-The first excited state, near $V_{SD} = $ \SI{1}{\milli\electronvolt}, is well-above all other energy scales in the measurement.
-Dashed line at $V_{SD}$ = \SI{700}{\micro\electronvolt} shows where data in (b) are taken.
-(b) Fixed bias transport data showing fits to the Zeeman splitting of the ground state energy from which $g = -0.44$ is extracted.
-(c) Change in entropy, determined from $dg_{sens}$ fits at varying parallel magnetic field.
+        \caption{\label{fig:fig3}(a) Change in entropy, determined from $dg_{sens}$ fits at varying parallel magnetic field.
 The $N=0 \rightarrow 1$ and $2 \rightarrow 3$ data are overlaid here to show the similar behavior of these states at low field.
-(d) and (e) show characteristic $dg_{sens}$ traces from which the data in (c) were extracted.
-These data points are show as large markers in (c)}
+(b) and (c) show characteristic $dg_{sens}$ traces from which the data in (c) were extracted.
+These data points are show as large markers in (c).
+(e) Bias spectroscopy data for $N=0 \rightarrow 1$ transition.
+Dashed line at $V_{SD}$ = \SI{700}{\micro\electronvolt} shows where data in (f) are taken.
+(f) Fixed bias data showing fits to the Zeeman splitting of the ground state (dashed lines) from which $g = -0.44$ is extracted.}
 \end{figure}
@@
 Confirmation that the measured $dS$ derives from spin degeneracy can be seen in its evolution with in-plane magnetic field, $B_\parallel$.
-Figure \ref{fig:fig3}a [REMOVE PANELS AB] compares $dS(B_\parallel)$ for the 0-1 and 2-3 electron transitions.
-The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $dS_{0 \rightarrow 1}$ and $dS_{2 \rightarrow 3}$ correspond to transitions from total spin zero $(S_0=S_2=0)$ to total spin one-half, and one might expect identical field-dependent behaviors for $dS_{0\rightarrow 1}$ and $dS_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies.
+Figure \ref{fig:fig3}a compares $dS(B_\parallel)$ for the 0-1 and 2-3 electron transitions.
+The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $dS_{0 \rightarrow 1}$ and $dS_{2 \rightarrow 3}$ correspond to transitions from total spin zero $(S_0=S_2=0)$ to total spin one-half.One expects identical field-dependent behaviors for $dS_{0\rightarrow 1}$ and $dS_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies.
 
@@
 where $p_{\pm}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_{\parallel}}{k_B T}})^{-1}$ are the probabilities for the system to be in $+/-$ (up/down) spin states at a given field and temperature.
-Fits to the lineshape in Eqn.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, allowing for peak height, a vertical offset, and the ratio $g/T$ as free parameters.
+Fits to the lineshape in Eqn.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, allowing for peak height and the ratio $g/T$ as free parameters.
 
-The entropy measurement agrees quantitatively with the expected $k_{B} \ln{2}$ at $B_\parallel=0$, collapsing to zero at high field when spin degeneracy is broken.
-Using a $T=T_{res}$ of 130 \SI{100}{\milli\kelvin} that is midway between the low ($T_{MC}$) and high ($T_{MC}+dT$) points of the temperature oscillation yields $g=0.43$ or $g=0.4$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions respectively, consistent with the value $g=-0.44$ expected for GaAs and measured via bias spectroscopy in a separate measurement (Figs.~\ref{fig:fig3}bc).
-At a qualitative level, the high-field crossover to a perfectly antisymmetric lineshape for $dg_{sens}(V_G)$ at the charge transition clearly indicates $\delta$ from Eqn.~\ref{eqn:dg} going to zero, corresponding to no entropy change between the two charge states (Figs.~\ref{fig:fig3}de).
+The entropy measurement yields $\partial S(B=0) = (0.933 \pm 000) k_B \ln{2}$, which agrees quantitatively with the expected $k_{B} \ln{2}$, collapsing to zero at high field where spin degeneracy is broken.
+At a qualitative level, Figs.~\ref{fig:fig3}b and c show the high-field crossover to a perfectly antisymmetric lineshape for $dg_{sens}(V_G)$; clearly indicating $\delta$ from Eqn.~\ref{eqn:dg} going to zero, corresponding to no entropy change between the two charge states.
+Using a $T=T_{res}$ of \SI{130}{\milli\kelvin} that is midway between the low ($T_{MC}$) and high ($T_{MC}+dT$) points of the temperature oscillation yields $g=-0.39$ or $g=-0.40$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions respectively.
+This is consistent with the value $g=-0.44$ expected for GaAs and measured via bias spectroscopy in Fig.~\ref{fig:fig3}e.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_4.pdf}
-        \caption{\label{fig:fig4}(a) (a) Transport data through the quantum dot showing the $N=1 \rightarrow 2$ transition.
-Singlet-triplet splitting is roughly \SI{300}{\micro\electronvolt} and depends on applied field.
-Dashed line at $V_{SD}$ = \SI{1250}{\micro\electronvolt} shows where data in (b) are taken.
-(b) Fixed bias transport data in parallel field.
-The triplet level is split into $T_+$, $T_0$, and $T_{-}$ (not visible).
+        \caption{\label{fig:fig4}(c) Change in entropy, extracted from $dg_{sens}$ fits at varying parallel field.
+Dashed line shows fit to Eq.~\ref{eqn:gibbs} (b), (c), and (d) show characteristic $dg_{sens}$ traces from which the data in (c) were extracted.
+These data points are show as large markers in (c).
+(e) Bias spectroscopy data for the $N=1 \rightarrow 2$ transition.
+Singlet-triplet splitting is \SI{316}{\micro\electronvolt}.
+Dashed line at $V_{SD}$ = \SI{1250}{\micro\electronvolt} shows where data in (f) are taken.
+(f) Fixed bias data in parallel field.
+Triplet level is split into $T_+$, $T_0$, and $T_{-}$ (not visible).
 At \SI[input-protect-tokens]{\sim 9}{\tesla} $T_+$ becomes degenerate with $S$.
-$g$ is determined using $T_0$ and $T_+$ fits.
-(c) Change in entropy, extracted from $dg_{sens}$ fits at varying parallel field.
-As the field goes from 0 to 10T, entropy of the 2-electron state goes from $0  \rightarrow \ln{2}$, while the entropy of the 1-electron state goes from $\ln{2} \rightarrow 0$.
-Fit to this behavior (dashed) is described in the text (d), (e), and (f) show characteristic $dg_{sens}$ traces from which the data in (c) were extracted.
-These data points are show as large markers in (c)}
+$g=40$ is determined using $T_0$ and $T_+$ fits (dashed).}
 \end{figure}
 
-The entropy of the 0 and 2-electron states are both zero at low magnetic field, so $dS$ for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}a) can be understood as the inverse of Fig \ref{fig:fig3}a as long as $B_\parallel$ is less than around \SI{5}{\tesla}.
+The $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}a) can be understood as the inverse of Fig \ref{fig:fig3}a, as long as $B_\parallel$ is less than around \SI{5}{\tesla}.
 There, the 2-electron ground state remains in the spin singlet state with zero entropy while 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
 At higher field, the 1-electron ground state remains non-degenerate while the 2-electron ground state becomes two-fold degenerate where the singlet ($S$) and triplet ($T_+$) states cross.
-The singlet-triplet crossing is seen clearly around at \SI{9}{\tesla} in bias spectroscopy data for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}bc).
+The singlet-triplet crossing is seen clearly around at \SI{9}{\tesla} in bias spectroscopy data for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}e).
 
@@
 From the fit we find the entropies at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are within 5\% of the expected values, $\mp k_B \ln{2}$.
-The extracted value of $g = 0.394$ from the low-field peak agrees well with the fit in Fig.~\ref{fig:fig3}a.
-At the high-field singlet-triplet degeneracy, $g = 0.586$ in the fit.
-This unexpected g-factor is explained by a shifting of the $T_{0}$ with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work.
+The extracted value of $g = 0.39$ from the low-field peak agrees well with the fit in Fig.~\ref{fig:fig3}a.
+At the high-field singlet-triplet degeneracy we find $g = 0.59$.
+This unexpected g-factor is explained by a shifting of the $T_{0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work [CITE].
 The high quality of this Gibbs entropy fit confirms $dS$ can be related directly to a tunable degeneracy in the system.
@@
 \paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.
-Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, then \SI{10}{\nano\metre} of $\mathrm{HfO_2}$ was deposited via atomic layer deposition to improve the gating stability to the device.
-Electron beam lithography followed by evaporation of \SI{20}{\nano\metre} of Ti/Au defined the fine gate structures, including the \SI{200}{\nano\metre} diameter quantum dots.
+Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability to the device.
+Fine gate structures, including the \SI{200}{\nano\metre} diameter quantum dots, were defined by electron beam lithography and deposition of \SI{20}{\nano\metre} Ti/Au.
 The measurement was carried out in an dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.
 
-The conductance of the charge sensor was measured at a DC voltage bias of XXX uV, with the current read out directly or fed into a lockin amplifier.
-The temperature of the reservoir could be raised above $T_MC$ (to $T_MC + dT$) using a current biased through the left (heater) QPC.
+The conductance of the charge sensor was measured at a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.
+The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + dT$) using a current biased through the left (heater) QPC.
 A calibration for $dT$ in this mode, using DC current bias $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
-Applying AC current at $f_{Heat} =$ \SI{48.7}{\hertz} yields oscillations in $T_{res}$ at $2f_{heat}$; to leading order $dT_{res} \sim P \sim \cos(2*(2 \pi f_{heat})t)$.
+Applying AC current at $f_{Heat} =$ \SI{48.7}{\hertz} yields oscillations in $T_{res}$ at $2f_{heat}$; to leading order $dT_{res} \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$.
 Variations in $g_{sens}$ with $dT$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.

### 2018-02-09 paper/draft.tex
change some figures. remove most of a paragraph.

@@
+% add citations for AFM papers (x2) for degeneracy measurements (vs T) and Beenakker (x1) for Gamma eqn
+
 %%%% outstanding mysteries %%%%%
@@
 % can I cite someone as to why \Delta_ST changes with field
-% dS or \partial S?
-% why does \partial S/ \partial N
 
@@
 
-%\begin{abstract}
-%
-%Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
+\begin{abstract}
+
+Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
 Such measurements are typically based on bulk properties, such as heat capacity, that are straightforward to observe in macroscopic samples but exceedingly difficult to access in mesoscopic systems that may consist of just a few electrons.
@@
 The entropy of a single spin ($k_B \ln{2}$) is measured within 8\% accuracy, as is the entropy arising at the magnetic field-driven singlet-triplet crossing for two electrons.
-%
-%\end{abstract}
+
+\end{abstract}
 
@@
 %%%%%%% intro material %%%%%%%%%
-\textbf{The thermodynamic properties of electronic systems can offer important insights into the nature of their ground states, and probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.
+The thermodynamic properties of electronic systems can offer important insights into the nature of their ground states, and probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.
 Systems that are difficult to clearly identify through standard conductance measurements may be studied more in depth if a thermodynamic measurement can be made.
@@
 Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}.
-A more direct test for the two-channel Kondo state would be a confirmation of its entropy ($\frac{1}{2} k_B \ln{2}$), that should remain down to arbitrarily low temperatures \cite{Alkurtass2016}.}
+A more direct test for the two-channel Kondo state would be a confirmation of its entropy ($\frac{1}{2} k_B \ln{2}$), that should remain down to arbitrarily low temperatures \cite{Alkurtass2016}.
 
@@
 Electrons tunneling between the reservoir and dot are measured with a capacitively-coupled charge sensor.
-(b) and (c) Charge sensor signal for a single transition from $N \rightarrow N+1$ electrons at two temperatures ($T_{Red} > T_{Blue}$) showing the two possible cases for $\frac{\partial \mu}{\partial T}$.}
+(b) and (c) Charge sensor signal for a single transition from $N-1 \rightarrow N$ electrons at two temperatures ($T_{Red} > T_{Blue}$) showing the two possible cases for $\frac{\partial \mu}{\partial T}$.}
 \end{figure}
@@
 that connects changes in entropy, particle number, and temperature ($S$, $N$, and $T$, respectively) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control.
-The fixed pressure condition of Eq.~\ref{eqn:max} is effectively met by working well below the Fermi temperature, $T_F \sim$\SI{5}{\kelvin}, where degeneracy pressure dominates \cite{Landau1969}.
+The fixed pressure condition of Eq.~\ref{eqn:max} is effectively met by working well below the Fermi temperature of the 2DEG, $T_F \sim$\SI{5}{\kelvin}, where degeneracy pressure dominates \cite{Landau1969}.
 
 The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two exciting theoretical proposals to measure the entropy derivative, $\frac{\partial S}{\partial N}$, of the $\nu = \frac{5}{2}$ state by detecting changes in the quasiparticle chemical potential with temperature \cite{Cooper2009,Ben-Shach2013}.
-Our work builds on these proposals to measure the entropy of the few-electron ground states of a quantum dot.
-Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states studied here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-Our experiment demonstrates a direct entropy measurement is possible on a few-particle system.
-In the future, the method can be utilized as a probe into the nature of more exotic systems, such as topologically non-trivial Majorana and other non-Abelian states.
+Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states investigated here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
+Applying the language of quantum dots to Eq.~\ref{eqn:max}, the shift in electrochemical potential, $\delta \mu$, with temperature is proportional to the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$).
+This shift, $\delta \mu$ as a function of $\delta T$, is the quantity probed directly in the experiment described below.
+From these measurements the entropies of the first three quantum dot levels are built up, demonstrating a direct entropy measurement is possible on a few-particle system.
+In the future, the method can be utilized to probe the nature of more exotic systems, such as topologically non-trivial Majorana and other non-Abelian states.
 
-The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a uses electrostatic gates to realize an electron reservoir (central region; hereafter ``reservoir") in thermal and electrochemical equilibrium with a few-electron quantum dot (``dot") coupled to its right side.
-The occupation of the dot is measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Frolov2009, Thierschmann2015}.
-An additional electron is added to an $N$ electron dot when the chemical potential, $\mu_{N+1}$, drops below the Fermi level of the reservoir, $E_F$.
-Figure 1b illustrates a such a transition \textemdash a step in the charge sensor conductance as a function of plunger gate voltage, $V_G$, which tunes the chemical potential on the dot, $\mu_{dot}$ \textemdash thermally broadened by the reservoir temperature, $T_{res}$.
-The gate voltage corresponding to midpoint of the transition, $V_0$, marks the chemical potential at which the probabilities of finding $N$ or $N+1$ electrons on the dot are equal.
+The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a uses electrostatic gates to realize an electron reservoir (central region; hereafter ``reservoir") in thermal and diffusive equilibrium with a few-electron quantum dot (``dot") coupled to its right side.
+The occupation of the dot is measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Thierschmann2015}.
+The $N$th is added to an $N-1$ electron dot when the electrochemical potential, $\mu_{N}$, drops below the Fermi level of the reservoir, $E_F$.
+Figure 1b illustrates a such a transition \textemdash a step in the charge sensor conductance as a function of plunger gate voltage, $V_G$, which tunes $\mu_{N}$ \textemdash thermally broadened by the reservoir temperature, $T_{res}$.
+The gate voltage corresponding to midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ or $N$ electrons on the dot are equal and the $N$th level is occupied half the time.
 
-The relation between entropy and a temperature-induced shift in $\mu_{N+1}$ (with respect to $E_F$) can be understood in the language of detailed balance.
-The $N+1^{\rm st}$ electron tunnels back and forth between an $N$-electron dot and a reservoir as long as there are available states in both dot and reservoir; true when $\mu_{N+1}$ is within thermal broadening of $E_F$.
-The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N\rightarrow N+1}$ and $\Gamma_{out}=\Gamma_{N+1\rightarrow N}$, depend on degeneracy of the $N$ and $N+1$ ground states.
+The relation between entropy and a temperature-induced shift in $\mu_{N})$ (with respect to $E_F$) can be understood in the language of detailed balance.
+The $N$th electron tunnels back and forth between an $N-1$-electron dot and reservoir as long as there are available states in both the dot and reservoir; true when $\mu_{N})$ is within thermal broadening of $E_F$.
+The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$, depend on degeneracy of the $N-1$ and $N$ ground states.
 Consider the filling of the first electron state, which has a single, unpaired spin-$\frac{1}{2}$ and, therefore, a degeneracy of 2.
@@
 Tunneling out, the electron (whether spin-up or -down) must tunnel into reservoir states with the same spin, that is, only half of the reservoir states are available.
-As a result, $\Gamma_{in} = 2\Gamma_{out}$ when $\mu_{N+1}=E_F$.
+As a result, $\Gamma_{in} = 2\Gamma_{out}$ when $\mu_{N}=E_F$.
 Extending this logic to a general case gives the result derived from detailed balance \cite{Gustavsson2009},
@@
 \begin{align}
-	\Gamma_{in} &=  g_{N+1} \Gamma f(E_F - \mu_{N+1}) \nonumber \\
-	\Gamma_{out} &= g_{N} \Gamma [1 - f(E_F - \mu_{N+1})] \label{eqn:rates}
+	\Gamma_{in} &=  g_{N} \Gamma f(E_F - \mu_{N}) \nonumber \\
+	\Gamma_{out} &= g_{N-1} \Gamma [1 - f(E_F - \mu_{N})] \label{eqn:rates}
 \end{align}
 %
-where $\Gamma$ is a coupling constant, $f$ is the Fermi function, and $g_{N(N+1)}$ is the degeneracy of the $N(N+1)$ electron state.
+where $\Gamma$ is a coupling constant, $f$ is the Fermi function, and $g_{N(N-1)}$ is the degeneracy of the $N(N-1)$ electron state.
 
-The midpoint of the transition between the $N$ and $N+1$ electron states ($V_0$), as measured by the charge sensor, occurs when $\Gamma_{in} = \Gamma_{out}$ and the dot is occupied half the time.
-From Eq.~\ref{eqn:rates}, $\Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N+1} = E_F$ when $g_{N}=g_{N+1}$.
-When $g_{N}\neq g_{N+1}$, $\mu_{N+1}$ shifts away from $E_F$ by an amount that depends on the broadening of the Fermi function, and therefore on $T$.
-A measurement of how $V_0$ shifts with T allows the ratio $g_{N+1}/g_{N}$ to be determined, which itself is related to $dS_{N\rightarrow N+1}$ through the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
-
-Looking back to Eq.~\ref{eqn:max}, the shift in $\mu_{N+1}$, and therefore $V_0$, with temperature is proportional to the entropy difference between the $N$ to $N+1$ ground states ($\partial S_{N\rightarrow N+1}$ for $\partial N=1$).
-This shift, $\partial V_0$ as a function of $\partial T$, is the quantity probed directly in the experiment described below.
-From these measurements the entropies of the first three energy levels in the quantum dot are built up, one by one.
-While the relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}, the thermal technique presented in this work extends the measurement of entropy (degeneracy) to a wider set of applications, where the tunneling process may not be convenient, or even possible, to observe in real-time.
+The midpoint of the transition between the $N-1$ and $N$ electron states ($V_{mid}$), occurs when $\Gamma_{in} = \Gamma_{out}$.
+From Eq.~\ref{eqn:rates}, $\Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N} = E_F$ when $g_{N-1}=g_{N}$.
+When $g_{N-1}\neq g_{N}$, $\mu_{N}$ shifts away from $E_F$ by an amount that depends on the broadening of the Fermi function, and therefore on $T$.
+A measurement of how $V_{mid}$ shifts with T allows the ratio $g_{N}/g_{N-1}$ to be determined, which itself is related to $\Delta S_{N-1\rightarrow N}$ through the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
+The relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}.
+The thermal technique presented in this work extends the measurement of entropy (degeneracy) to a wider set of applications, where the tunneling process may not be convenient, or even possible, to observe in real-time.
 
@@
         \caption{\label{fig:fig2}(a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater.
-(b) Lock-in measurement of $dg_{sens}$ with $dT \sim 60mK$.
+(b) Lock-in measurement of $dg_{sens}$ with $\delta T \sim 60mK$.
 Fits to $dg_{sens}$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a function of mixing chamber temperature.
@@
 (d) $\Theta$ as a function of DC current through the QPC heater.
-Fit is used to convert between $I_{heat}$ and $dT$, with $R_{QPC} = $ \SI{20}{\kilo\ohm} (e) Change in entropy as a function of AC current through the QPC heater.
-Top axis shows corresponding $dT$.
-Right axis shows shift in $\partial V_0$ per unit temperature.}
+Fit is used to convert between $I_{heat}$ and $\delta T$, with $R_{QPC} = $ \SI{20}{\kilo\ohm} (e) Change in entropy as a function of AC current through the QPC heater.
+Top axis shows corresponding $\delta T$.
+Right axis shows shift in $\delta V_{mid}$ per unit temperature.}
 \end{figure}
@@
 \label{eqn:g}
-        g_{sens}(V,\Theta) &= G_0 \tanh\left(\frac{V-V_0(\Theta)}{2\Theta}\right)  \\
-                        &\quad + G_1\left[V-V_0(\Theta)\right] + G_2 \nonumber
+        g_{sens}(V,\Theta) &= G_0 \tanh\left(\frac{V-V_{mid}(\Theta)}{2\Theta}\right)  \\
+                        &\quad + G_1\left[V-V_{mid}(\Theta)\right] + G_2 \nonumber
 \end{align}
 %
-where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm that converts $V_G$ to $\mu_{dot}$, and $G_1$ is determined by the cross capacitance between the charge sensor and plunger gate.
-The dependence of $V_0$ on $\Theta$ captures any shift in $\mu$ due to a change in entropy across the transition.
+where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm that converts $V_G$ to $\mu_{N}$, and $G_1$ is determined by the cross capacitance between the charge sensor and plunger gate.
+The dependence of $V_{mid}$ on $\Theta$ captures any shift in $\mu_{N}$ due to a change in entropy across the transition.
 
@@
 The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work with Joule heating giving reservoir temperatures up to \SI{250}{\milli\kelvin}.
-Measurements of $\partial S$ are made at $dT_{res} = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
+Measurements of $\Delta S$ are made at $\delta T_{res} = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
 
 %%% figs 2c and d%%%
-The data in Fig.~\ref{fig:fig2}c, and corresponding fits, offer an example of how $dS_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ transition.
-A comparison of the 100 and 160 mK data in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as the temperature rises before the midpoint of the transition ($V_G-V_0<0$), whereas the conductance is higher in the warmer curve for $V_G-V_0>0$.
-Oscillating the reservoir temperature by $dT_{res}$ using an AC current, $I^{AC}_{Heat}$, measuring oscillations in $g_{sens}$ with a lock in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
-The expected lineshape of such a curve is given by the derivative of Eq.~\ref{eqn:g} with respect to temperature, expressed as $dg_{sens}$ due to a temperature change $dT$:
+The data in Fig.~\ref{fig:fig2}c, and corresponding fits, offer an example of how $\Delta S_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ transition.
+A comparison of the 100 and 160 mK data in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as the temperature rises before the midpoint of the transition ($V_G-V_{mid}<0$), whereas the conductance is higher in the warmer curve for $V_G-V_{mid}>0$.
+Oscillating the reservoir temperature by $\delta T_{res}$ using an AC current, $I^{AC}_{Heat}$, while measuring oscillations in $g_{sens}$ with a lock in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
+The expected lineshape of such a curve is given by the derivative of Eq.~\ref{eqn:g} with respect to temperature, expressed as $dg_{sens}$ due to a temperature change $\delta T$:
 %
@@
 \label{eqn:dg}
-        dg_{sens}(V_G, \Theta) &\propto dT \left[ \frac{V_G-V_{0}(\Theta)}{2\Theta} +\delta \right]\times \\
-        				      &\quad\cosh^{-2}\left(\frac{V_G-V_{0}(\Theta)}{2\Theta}\right) \nonumber
+        dg_{sens}(V_G, \Theta) &\propto \delta T \left[ \frac{V_G-V_{0}(\Theta)}{2\Theta} +\delta \right]\times \\
+        				      &\quad\cosh^{-2}\left(\frac{V_G-V_{0}(\Theta)}{2\Theta}\right) + const. \nonumber
 \end{align}
 %
-where $\delta=\frac{\partial V_0}{\partial \Theta}$.
-Using the lever arm to convert $V_0$ to chemical potential, the parameter $\delta$ is expressed as the change in entropy scaled by Boltzmann's constant:
+where $\delta=\frac{\partial V_{mid}}{\partial \Theta}$.
+Using the lever arm to convert $V_{mid}$ to electrochemical potential, $\delta$ is expressed as the change in entropy (scaled by $k_B$) through Eq.~\ref{eqn:max}:
 %
@@
 \label{eqn:delta}
-        \delta &= \frac{\partial V_0}{\partial \Theta} = 
+        \delta &= \frac{\partial V_{mid}}{\partial \Theta} = 
         \frac{1}{k_B} \frac{\partial \mu}{\partial T} = 
-        -\frac{1}{k_B} \partial S_{N\rightarrow N+1}
+        -\frac{1}{k_B} \Delta S_{N-1\rightarrow N}
 \end{align}
@@
 
-From Eqs.~\ref{eqn:dg} and \ref{eqn:delta}, $dg_{sens}(V_G)$ would be perfectly antisymmetric around $V_0$ if $\partial S_{N\rightarrow N+1}$ were zero.
-Fits to the data in Fig.~\ref{fig:fig2}c illustrate clearly that $\partial S_{0\rightarrow 1}=0$ is inconsistent with the data;  the best fit is found for $\partial S_{0\rightarrow 1}=0.71\times k_B$.
-Indeed, this is what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate 1-electron state one expects $S_1=k_B\ln{2}$, giving $dS_{0\rightarrow 1}\equiv S_1 = S_0 =k_B\ln{2}$.
-Fig.~\ref{fig:fig2}e shows that $dS$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $dT$ ($I^{AC}_{Heat}$).
-Although the extracted $\delta$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $dS$, is determined directly from the fit to $g_{sens}$ without any additional calibration.
+From Eqs.~\ref{eqn:dg} and \ref{eqn:delta}, $dg_{sens}(V_G)$ would be perfectly antisymmetric around $V_{mid}$ if $\Delta S_{N-1\rightarrow N}$ were zero.
+Fits to the data in Fig.~\ref{fig:fig2}c illustrate clearly that $\Delta S_{0\rightarrow 1}=0$ is inconsistent with the data;  the best fit is found for $\Delta S_{0\rightarrow 1}=0.71\times k_B$.
+Indeed, this is what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate 1-electron state one expects $S_1=k_B\ln{2}$, giving $\Delta S_{0\rightarrow 1}\equiv S_1 = S_0 =k_B\ln{2}$.
+Fig.~\ref{fig:fig2}e shows that $\Delta S$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T$ ($I^{AC}_{Heat}$).
+Although the extracted $\delta$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $dg_{sens}$ without any additional calibration.
 
@@
 
-Confirmation that the measured $dS$ derives from spin degeneracy can be seen in its evolution with in-plane magnetic field, $B_\parallel$.
-Figure \ref{fig:fig3}a compares $dS(B_\parallel)$ for the 0-1 and 2-3 electron transitions.
-The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $dS_{0 \rightarrow 1}$ and $dS_{2 \rightarrow 3}$ correspond to transitions from total spin zero $(S_0=S_2=0)$ to total spin one-half.One expects identical field-dependent behaviors for $dS_{0\rightarrow 1}$ and $dS_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies.
+Confirmation that the measured $\Delta S$ derives from spin degeneracy can be seen in its evolution with in-plane magnetic field, $B_\parallel$.
+Figure \ref{fig:fig3}a compares $\Delta S(B_\parallel)$ for the 0-1 and 2-3 electron transitions.
+The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $\Delta S_{0 \rightarrow 1}$ and $\Delta S_{2 \rightarrow 3}$ correspond to transitions from total spin zero $(S_0=S_2=0)$ to total spin one-half.One expects identical field-dependent behaviors for $\Delta S_{0\rightarrow 1}$ and $\Delta S_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies.
 
@@
 
-The entropy measurement yields $\partial S(B=0) = (0.933 \pm 000) k_B \ln{2}$, which agrees quantitatively with the expected $k_{B} \ln{2}$, collapsing to zero at high field where spin degeneracy is broken.
+The entropy measurement yields $\Delta S(B=0) = (0.933 \pm 000) k_B \ln{2}$, which agrees quantitatively with the expected $k_{B} \ln{2}$, collapsing to zero at high field where spin degeneracy is broken.
 At a qualitative level, Figs.~\ref{fig:fig3}b and c show the high-field crossover to a perfectly antisymmetric lineshape for $dg_{sens}(V_G)$; clearly indicating $\delta$ from Eqn.~\ref{eqn:dg} going to zero, corresponding to no entropy change between the two charge states.
-Using a $T=T_{res}$ of \SI{130}{\milli\kelvin} that is midway between the low ($T_{MC}$) and high ($T_{MC}+dT$) points of the temperature oscillation yields $g=-0.39$ or $g=-0.40$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions respectively.
+Using a $T=T_{res}$ of \SI{130}{\milli\kelvin} that is midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T$) points of the temperature oscillation yields $g=-0.39$ and $g=-0.40$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
 This is consistent with the value $g=-0.44$ expected for GaAs and measured via bias spectroscopy in Fig.~\ref{fig:fig3}e.
@@
 The field-dependent entropy measurement for the 1-2 transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{S/T}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron singlet-triplet states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
-The fit allows for an offset from $dS=0$, away from the degenerate points, to compensate for non-linearities in the charge sensor.
+The fit allows for an offset from $\Delta S=0$, away from the degenerate points, to compensate for non-linearities in the charge sensor.
 From the fit we find the entropies at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are within 5\% of the expected values, $\mp k_B \ln{2}$.
@@
 This unexpected g-factor is explained by a shifting of the $T_{0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work [CITE].
-The high quality of this Gibbs entropy fit confirms $dS$ can be related directly to a tunable degeneracy in the system.
+The high quality of this Gibbs entropy fit confirms $\Delta S$ can be related directly to a tunable degeneracy in the system.
 
@@
 The conductance of the charge sensor was measured at a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.
-The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + dT$) using a current biased through the left (heater) QPC.
-A calibration for $dT$ in this mode, using DC current bias $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
-Applying AC current at $f_{Heat} =$ \SI{48.7}{\hertz} yields oscillations in $T_{res}$ at $2f_{heat}$; to leading order $dT_{res} \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$.
+The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + \delta T$) using a current biased through the left (heater) QPC.
+A calibration for $\delta T$ in this mode, using DC current bias $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
+Applying AC current at $f_{Heat} =$ \SI{48.7}{\hertz} yields oscillations in $T_{res}$ at $2f_{heat}$; to leading order $\delta T_{res} \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$.
 Variations in $g_{sens}$ with $dT$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
@@
 %\acknowledgments
-% Everyone I might acknowledge is currently an author. Consider moving someone here.
 

### 2018-02-10 paper/draft.tex
bring back abstract
Friday edits

@@
+% 2/8/2018
 % add citations for AFM papers (x2) for degeneracy measurements (vs T) and Beenakker (x1) for Gamma eqn
@@
 
-\begin{abstract}
-
-Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
+%\begin{abstract}
+%
+%Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
 Such measurements are typically based on bulk properties, such as heat capacity, that are straightforward to observe in macroscopic samples but exceedingly difficult to access in mesoscopic systems that may consist of just a few electrons.
@@
 %%%%%%% intro material %%%%%%%%%
-The thermodynamic properties of electronic systems can offer important insights into the nature of their ground states, and probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.
+\textbf{The thermodynamic properties of electronic systems offer important insights into the nature of their ground states, and can probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.
 Systems that are difficult to clearly identify through standard conductance measurements may be studied more in depth if a thermodynamic measurement can be made.
-For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, are exceedingly difficult to identify from conductance signatures.
-However, an entropy measurement could clearly distinguish Abelian from non-Abelian quasiparticles \cite{Cooper2009, Smirnov2015}.
-Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}.
+For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, are challenging  to identify from conductance signatures, but could be clearly distinguished from the Abelian case by an entropy measurement \cite{Cooper2009, Smirnov2015}.
+Such measurements are typically based on bulk properties, like heat capacity, that are straightforward to observe in macroscopic samples but difficult to access in mesoscopic systems that may consist of just a few electrons.
+Here, we develop a mesoscopic circuit that realizes a direct entropy measurement on the first, second, and third electron occupations in a GaAs quantum dot.
+The dot system is chosen for having well known entropy based on simple spin states\cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
+The precision of this technique, quantifying the entropy of a single spin 1/2 to within 3\% of the expected value ($k_B ln 2$), shows its potential for probing more exotic systems in the future, from Majorana states to non-Fermi liquid Kondo states that are clearly identified by a residual low-temperature entropy\cite{Alkurtass2016}.}
+%Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}.
 A more direct test for the two-channel Kondo state would be a confirmation of its entropy ($\frac{1}{2} k_B \ln{2}$), that should remain down to arbitrarily low temperatures \cite{Alkurtass2016}.
@@
 
-Entropy can be probed effectively in 3D macroscopic samples via measurements of heat capacity, but the heat capacities of single electrons or quasiparticles are much too small to measure directly; even the 2D sheet of quasiparticles in $\nu = \frac{5}{2}$ fractional quantum Hall samples has a heat capacity that vanishes in comparison to that of the host crystal.
+%Entropy can be probed effectively in 3D macroscopic samples via measurements of heat capacity, but the heat capacities of single electrons or quasiparticles are much too small to measure directly; even the 2D sheet of quasiparticles in $\nu = \frac{5}{2}$ fractional quantum Hall samples has a heat capacity that vanishes in comparison to that of the host crystal.
 Rather than attempt to resolve such infinitesimal signals, the problem can be avoided by converting changes in entropy to changes in charge \textemdash a quantity that is easily detected at the single particle level.
+
 Our approach is analogous to the milestone of spin-to-charge conversion by which undetectably-small magnetic moments of a single spin were transformed into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
-
-In order to accomplish this entropy to charge conversion, we make use of the Maxwell relation
+Instead, we perform an entropy-to-charge conversion, making use of the Maxwell relation
 %
@@
 that connects changes in entropy, particle number, and temperature ($S$, $N$, and $T$, respectively) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control.
-The fixed pressure condition of Eq.~\ref{eqn:max} is effectively met by working well below the Fermi temperature of the 2DEG, $T_F \sim$\SI{5}{\kelvin}, where degeneracy pressure dominates \cite{Landau1969}.
+The fixed pressure condition of Eq.~\ref{eqn:max} is met by working well below the Fermi temperature of the 2DEG, $T_F \sim$\SI{5}{\kelvin}, where degeneracy pressure dominates \cite{Landau1969}.
 
-The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two exciting theoretical proposals to measure the entropy derivative, $\frac{\partial S}{\partial N}$, of the $\nu = \frac{5}{2}$ state by detecting changes in the quasiparticle chemical potential with temperature \cite{Cooper2009,Ben-Shach2013}.
-Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states investigated here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-Applying the language of quantum dots to Eq.~\ref{eqn:max}, the shift in electrochemical potential, $\delta \mu$, with temperature is proportional to the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$).
-This shift, $\delta \mu$ as a function of $\delta T$, is the quantity probed directly in the experiment described below.
+The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to check for non-Abelian exchange of quasiparticles in the the $\nu = \frac{5}{2}$ state, measuring the entropy derivative, $\frac{\partial S}{\partial N}$, by detecting changes in the quasiparticle chemical potential with temperature \cite{Cooper2009,Ben-Shach2013}.
+%Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states investigated here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
+Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured by detecting the shift with temperature in the electrochemical potential for the $N$th electron on the dot, $\mu_N$, which changes the gate voltage needed to drive the $N-1$ to $N$ electron transition.
+%This shift, $\delta \mu$ as a function of $\delta T$, is the quantity probed directly in the experiment described below.
 From these measurements the entropies of the first three quantum dot levels are built up, demonstrating a direct entropy measurement is possible on a few-particle system.
@@
 The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a uses electrostatic gates to realize an electron reservoir (central region; hereafter ``reservoir") in thermal and diffusive equilibrium with a few-electron quantum dot (``dot") coupled to its right side.
-The occupation of the dot is measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Thierschmann2015}.
-The $N$th is added to an $N-1$ electron dot when the electrochemical potential, $\mu_{N}$, drops below the Fermi level of the reservoir, $E_F$.
-Figure 1b illustrates a such a transition \textemdash a step in the charge sensor conductance as a function of plunger gate voltage, $V_G$, which tunes $\mu_{N}$ \textemdash thermally broadened by the reservoir temperature, $T_{res}$.
-The gate voltage corresponding to midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ or $N$ electrons on the dot are equal and the $N$th level is occupied half the time.
+The reservoir temperature, $T_{res}$, could be rapidly (up to at least \SI{100}{\hertz}) elevated above the mixing chamber temperature, $T_{MC}$, by Joule heating through the QPC (``heater") on the left side.
+The occupation of the dot was measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Thierschmann2015}.
+Applying a more positive voltage to the gate adds the $N$th electron to the dot when $\mu_{N}$ drops below the Fermi level of the reservoir, $E_F$.
+Figure 1b illustrates such a transition \textemdash a step in the charge sensor conductance \textemdash thermally broadened by the reservoir temperature, $T_{res}$.
+The gate voltage corresponding to midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ or $N$ electrons on the dot are equal.
+When $\mu_N$ shifts with temperature, $V_{mid}$ also shifts (Fig.~1c); it is this signature that forms the basis of our experiment.%and the $N$th level is occupied half the time.
 
-The relation between entropy and a temperature-induced shift in $\mu_{N})$ (with respect to $E_F$) can be understood in the language of detailed balance.
-The $N$th electron tunnels back and forth between an $N-1$-electron dot and reservoir as long as there are available states in both the dot and reservoir; true when $\mu_{N})$ is within thermal broadening of $E_F$.
+The relation between entropy and any temperature-induced shift in $\mu_{N}$ with respect to $E_F$ can also be understood in the language of detailed balance.
+The $N$th electron tunnels back and forth between an $N-1$-electron dot and reservoir when there are available states in both the dot and reservoir, that is, when $\mu_{N}$ is within thermal broadening of $E_F$.
 The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$, depend on degeneracy of the $N-1$ and $N$ ground states.
-Consider the filling of the first electron state, which has a single, unpaired spin-$\frac{1}{2}$ and, therefore, a degeneracy of 2.
-An electron tunneling into the dot has both spin-up and -down states available.
+%Consider the filling of the first electron state, which has a single, unpaired spin-$\frac{1}{2}$ and, therefore, a degeneracy of 2.
+Consider, for example, an electron tunneling into an empty dot: both spin-up and -down states are available.
 Tunneling out, the electron (whether spin-up or -down) must tunnel into reservoir states with the same spin, that is, only half of the reservoir states are available.
@@
 
-The midpoint of the transition between the $N-1$ and $N$ electron states ($V_{mid}$), occurs when $\Gamma_{in} = \Gamma_{out}$.
-From Eq.~\ref{eqn:rates}, $\Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N} = E_F$ when $g_{N-1}=g_{N}$.
-When $g_{N-1}\neq g_{N}$, $\mu_{N}$ shifts away from $E_F$ by an amount that depends on the broadening of the Fermi function, and therefore on $T$.
-A measurement of how $V_{mid}$ shifts with T allows the ratio $g_{N}/g_{N-1}$ to be determined, which itself is related to $\Delta S_{N-1\rightarrow N}$ through the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
+The equal probability condition for $N-1/N$ at $V_{mid}$ corresponds to  incoming and outgoing rates being equal.
+From Eq.~\ref{eqn:rates}$, \Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N} = E_F$ as long as $g_{N-1}=g_{N}$, but to $\mu_{N} > E_F$ when $g_{N-1} > g_{N}$ and vice versa [Nik check inequalities].
+A measurement of how $V_{mid}$ shifts with temperature quantifies the ratio $g_{N}/g_{N-1}$, giving $\Delta S_{N-1\rightarrow N}$ via the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
 The relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}.
-The thermal technique presented in this work extends the measurement of entropy (degeneracy) to a wider set of applications, where the tunneling process may not be convenient, or even possible, to observe in real-time.
+The approach presented here confirms the thermodynamic equivalence of the rate measurement, and extends entropy measurements to a much wider set of applications where the tunneling process may not be possible to observe in real-time.
 
@@
 To proceed with the entropy measurement, the quantum dot (Fig.~\ref{fig:fig1}a) was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
-The conductance of the charge sensor, $g_{sens}$, was measured in a DC voltage biased configuration, and tuned to $g_{sens}{\sim}e^2/h$ where it was most sensitive to charge on the dot.
-The reservoir temperature could be rapidly controlled (up to at least \SI{100}{\hertz}) by Joule heating through the QPC on the left side (Fig.~\ref{fig:fig1}a), which was fixed at \SI{20}{\kilo\ohm} and biased with an AC or DC current source.
-
-%%% figs 2a and b %%%
+The conductance of the charge sensor was tuned to $g_{sens}{\sim}e^2/h$ where it was most sensitive to charge on the dot.
 The addition of the first electron to the dot was marked by a decrease in $g_{sens}$ that is well fit by the expected form for a thermally-broadened transition (Fig.~\ref{fig:fig2}a):
@@
 %
-where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm that converts $V_G$ to $\mu_{N}$, and $G_1$ is determined by the cross capacitance between the charge sensor and plunger gate.
-The dependence of $V_{mid}$ on $\Theta$ captures any shift in $\mu_{N}$ due to a change in entropy across the transition.
+where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm $\alpha\equiv\partial \mu_{N}/\partial V_G$, and $G_1$ is determined by the cross capacitance between the charge sensor and plunger gate.
+With no Joule heating through the heater, $\Theta$ was found to follow $T_{MC}$ down to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b), validating the approximation of thermal broadening used throughout this experiment.
 
-The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} follows the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
-The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work with Joule heating giving reservoir temperatures up to \SI{250}{\milli\kelvin}.
+%The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} follows the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
+The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T_{res}$ up to \SI{250}{\milli\kelvin}.
 Measurements of $\Delta S$ are made at $\delta T_{res} = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
@@
 The data in Fig.~\ref{fig:fig2}c, and corresponding fits, offer an example of how $\Delta S_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ transition.
-A comparison of the 100 and 160 mK data in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as the temperature rises before the midpoint of the transition ($V_G-V_{mid}<0$), whereas the conductance is higher in the warmer curve for $V_G-V_{mid}>0$.
-Oscillating the reservoir temperature by $\delta T_{res}$ using an AC current, $I^{AC}_{Heat}$, while measuring oscillations in $g_{sens}$ with a lock in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
+A comparison of the curves in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as temperature rises before the midpoint of the transition ($V_G-V_{mid}<0$), whereas $g_{sens}$ is higher in the warmer curve for $V_G-V_{mid}>0$.
+Oscillating the reservoir temperature by $\delta T_{res}$ using an AC current through the heater while measuring oscillations in $g_{sens}$ with a lock in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
 The expected lineshape of such a curve is given by the derivative of Eq.~\ref{eqn:g} with respect to temperature, expressed as $dg_{sens}$ due to a temperature change $\delta T$:
@@
 \label{eqn:dg}
-        dg_{sens}(V_G, \Theta) &\propto \delta T \left[ \frac{V_G-V_{0}(\Theta)}{2\Theta} +\delta \right]\times \\
-        				      &\quad\cosh^{-2}\left(\frac{V_G-V_{0}(\Theta)}{2\Theta}\right) + const. \nonumber
+        dg_{sens}(V_G, \Theta) &\propto \delta T \left[ \frac{V_G-V_{mid}(\Theta)}{2\Theta} +\delta \right]\times \\
+        				      &\quad\cosh^{-2}\left(\frac{V_G-V_{mid}(\Theta)}{2\Theta}\right) + const. \nonumber
 \end{align}
@@
 where $\delta=\frac{\partial V_{mid}}{\partial \Theta}$.
-Using the lever arm to convert $V_{mid}$ to electrochemical potential, $\delta$ is expressed as the change in entropy (scaled by $k_B$) through Eq.~\ref{eqn:max}:
+Using the lever arm to convert $V_{mid}$ to electrochemical potential, $\delta$ is just the change in entropy (scaled by $k_B$) through Eq.~\ref{eqn:max}:
 %
@@
 From Eqs.~\ref{eqn:dg} and \ref{eqn:delta}, $dg_{sens}(V_G)$ would be perfectly antisymmetric around $V_{mid}$ if $\Delta S_{N-1\rightarrow N}$ were zero.
-Fits to the data in Fig.~\ref{fig:fig2}c illustrate clearly that $\Delta S_{0\rightarrow 1}=0$ is inconsistent with the data;  the best fit is found for $\Delta S_{0\rightarrow 1}=0.71\times k_B$.
+The best fit of Eqs.~\ref{eqn:dg} and \ref{eqn:delta} to the data in Fig.~\ref{fig:fig2}c yields $\Delta S_{0\rightarrow 1}=0.71\times k_B$.
 Indeed, this is what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate 1-electron state one expects $S_1=k_B\ln{2}$, giving $\Delta S_{0\rightarrow 1}\equiv S_1 = S_0 =k_B\ln{2}$.
-Fig.~\ref{fig:fig2}e shows that $\Delta S$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T$ ($I^{AC}_{Heat}$).
-Although the extracted $\delta$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $dg_{sens}$ without any additional calibration.
+Fig.~\ref{fig:fig2}e shows that $\Delta S$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T_{res}$ ($I^{AC}_{Heat}$).
+Although the extracted $\delta$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $dg_{sens}$ without any additional calibration, and without knowing the precise value of $\delta T_{res}$.
 
@@
 Figure \ref{fig:fig3}a compares $\Delta S(B_\parallel)$ for the 0-1 and 2-3 electron transitions.
-The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $\Delta S_{0 \rightarrow 1}$ and $\Delta S_{2 \rightarrow 3}$ correspond to transitions from total spin zero $(S_0=S_2=0)$ to total spin one-half.One expects identical field-dependent behaviors for $\Delta S_{0\rightarrow 1}$ and $\Delta S_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies.
-
+The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $\Delta S_{0 \rightarrow 1}$ and $\Delta S_{2 \rightarrow 3}$ may be expected to correspond to transitions from total spin zero to total spin one-half.
+%One expects identical field-dependent behaviors for $\Delta S_{0\rightarrow 1}$ and $\Delta S_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies.
 The entropies of 1- and 3-electron states are suppressed when the Zeeman splitting lifts the spin degeneracy of the unpaired electron, following the Gibbs entropy for a two-level system:
@@
 where $p_{\pm}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_{\parallel}}{k_B T}})^{-1}$ are the probabilities for the system to be in $+/-$ (up/down) spin states at a given field and temperature.
-Fits to the lineshape in Eqn.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, allowing for peak height and the ratio $g/T$ as free parameters.
+Fits to the lineshape in Eqn.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, allowing for peak height and the ratio $g/T_{res}$ as free parameters.
 
-The entropy measurement yields $\Delta S(B=0) = (0.933 \pm 000) k_B \ln{2}$, which agrees quantitatively with the expected $k_{B} \ln{2}$, collapsing to zero at high field where spin degeneracy is broken.
-At a qualitative level, Figs.~\ref{fig:fig3}b and c show the high-field crossover to a perfectly antisymmetric lineshape for $dg_{sens}(V_G)$; clearly indicating $\delta$ from Eqn.~\ref{eqn:dg} going to zero, corresponding to no entropy change between the two charge states.
-Using a $T=T_{res}$ of \SI{130}{\milli\kelvin} that is midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T$) points of the temperature oscillation yields $g=-0.39$ and $g=-0.40$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
+The entropy measurements yield $\Delta S_{0 \rightarrow 1}=0.93\times k_B \ln{2}$ and $\Delta S_{2 \rightarrow 3}=0.98\times k_B \ln{2}$ at zero magnetic field, collapsing to zero at high field where spin degeneracy is broken.
+At a qualitative level, Figs.~\ref{fig:fig3}b and c show the crossover from asymmetric to antisymmetric as $\Delta S$ goes to zero at high field.
+Using a value for $T_{res}$ of \SI{130}{\milli\kelvin} that is midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T$) points of the temperature oscillation yields $g=-0.39$ and $g=-0.40$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
 This is consistent with the value $g=-0.44$ expected for GaAs and measured via bias spectroscopy in Fig.~\ref{fig:fig3}e.
@@
 
-The $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}a) can be understood as the inverse of Fig \ref{fig:fig3}a, as long as $B_\parallel$ is less than around \SI{5}{\tesla}.
-There, the 2-electron ground state remains in the spin singlet state with zero entropy while 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
-At higher field, the 1-electron ground state remains non-degenerate while the 2-electron ground state becomes two-fold degenerate where the singlet ($S$) and triplet ($T_+$) states cross.
+The $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}a) can be understood as the inverse of Fig \ref{fig:fig3}a for $B_\parallel$ less than \SI{5}{\tesla}.
+There, the 2-electron ground state remains in the spin singlet state ($S_2=0$) while the 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
+At higher field, the 1-electron ground state remains non-degenerate ($S_1=0$) while the 2-electron ground state becomes two-fold degenerate where the singlet ($S$) and triplet ($T_+$) states cross.
 The singlet-triplet crossing is seen clearly around at \SI{9}{\tesla} in bias spectroscopy data for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}e).
 
-The field-dependent entropy measurement for the 1-2 transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{S/T}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron singlet-triplet states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
+The field-dependent entropy measurement for the 1-2 transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{S/T}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
 The fit allows for an offset from $\Delta S=0$, away from the degenerate points, to compensate for non-linearities in the charge sensor.
-From the fit we find the entropies at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are within 5\% of the expected values, $\mp k_B \ln{2}$.
+From the fit we find the entropies at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are again within 5\% of the expected values, $\mp k_B \ln{2}$.
 The extracted value of $g = 0.39$ from the low-field peak agrees well with the fit in Fig.~\ref{fig:fig3}a.
 At the high-field singlet-triplet degeneracy we find $g = 0.59$.
-This unexpected g-factor is explained by a shifting of the $T_{0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work [CITE].
-The high quality of this Gibbs entropy fit confirms $\Delta S$ can be related directly to a tunable degeneracy in the system.
+This unexpectedly high g-factor can be explained by a shifting of the $T_{0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work [cite PHYSICAL REVIEW B 70, 235335 (2004)].
+The high quality of the Gibbs entropy fit confirms $\Delta S$ illustrates the tunable degeneracy in the system.
 
 %%% conclusion %%%
-The results presented demonstrate a novel technique to measure the entropy of few-particle states in mesoscopic devices.
-The measurement was used to investigate the well-understood spin degeneracy of the few-electron ground states states in a GaAs quantum dot.
-The entropy signal is confirmed by tuning the entropy as a function of applied magnetic field.
-Future work may take advantage of this strategy to look for thermodyanmic signatures of non-trival electron and quasiparticle states, eliminating the uncertainty found in typical transport data.
+In conclusion, we show that the entropy of few-particle states in mesoscopic devices can be measured directly.
+Using the well-understood spin degeneracy of  few-electron ground states states in a GaAs quantum dot for calibration, the entropy can be quantified within 5\% of the expected $k_B\ln{2}$.
+Future work may take advantage of this strategy to look for thermodynamic signatures of non-trival electron and quasiparticle states, eliminating the uncertainty found in typical transport data.
 
@@
 The conductance of the charge sensor was measured at a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.
-The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + \delta T$) using a current biased through the left (heater) QPC.
+The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + \delta T$) using AC or DC current biased through the left (heater) QPC, which was gate-tuned to \SI{20}{\kilo\ohm}.
 A calibration for $\delta T$ in this mode, using DC current bias $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
@@
 Variations in $g_{sens}$ with $dT$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
+
+The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
+The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T_{res}$ up to \SI{250}{\milli\kelvin}.
+Measurements of $\Delta S$ are made at $\delta T_{res} = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
 

### 2018-02-10 paper/draft.tex
not much changes

@@
-% 2/8/2018
+% 2/9/2018
 % add citations for AFM papers (x2) for degeneracy measurements (vs T) and Beenakker (x1) for Gamma eqn
@@
 
-\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.
+%\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.
 Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability to the device.
@@
 The measurement was carried out in an dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.
-
-The conductance of the charge sensor was measured at a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.
+%
+%The conductance of the charge sensor was measured at a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.
 The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + \delta T$) using AC or DC current biased through the left (heater) QPC, which was gate-tuned to \SI{20}{\kilo\ohm}.
@@
 Variations in $g_{sens}$ with $dT$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
-
-The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
+%
+%The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
 The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T_{res}$ up to \SI{250}{\milli\kelvin}.

### 2018-02-19 paper/draft.tex
so much matplotlib

--- 2018-02-10 paper/draft.tex
@@
-% 2/8/2018
-% add citations for AFM papers (x2) for degeneracy measurements (vs T) and Beenakker (x1) for Gamma eqn
+% double check \Theta calculations -- is the whole thing off by a factor of 2???
+% error bars on dS values from a single fit
 
-%%%% outstanding mysteries %%%%%
-% error bar on 0-1 peak height (mention in text)
-% can I cite someone as to why \Delta_ST changes with field
+% add mention about Fig 2d by rewording this sentence: 
+%"Although the extracted  can b e converted to gate-voltage-per-temperature units using a value for 
+%  measured separately (right axis of Fig. 2e), the entropy itself, S , is determined directly from the 
+%  t to dg_sens without any additional calibration, and without knowing the precise value of  T_res"
 
-\documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,pra,aps,superscriptaddress]{revtex4-1}
+% mention QPC heater in text when discussing Fig 2a -- define I_{heat} in here 
+% add equation and citation for fit in Fig 2d to caption
+% remove _{res} subscripts from temps
+% peak height --> "an added scaling parameter (dS(B=0))" when describing dS vs B fits
+
+\documentclass[twocolumn,showpacs,amsmath,amssymb,prl,aps,superscriptaddress]{revtex4-1}
 
@@
 \textbf{The thermodynamic properties of electronic systems offer important insights into the nature of their ground states, and can probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.
-Systems that are difficult to clearly identify through standard conductance measurements may be studied more in depth if a thermodynamic measurement can be made.
-For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, are challenging  to identify from conductance signatures, but could be clearly distinguished from the Abelian case by an entropy measurement \cite{Cooper2009, Smirnov2015}.
-Such measurements are typically based on bulk properties, like heat capacity, that are straightforward to observe in macroscopic samples but difficult to access in mesoscopic systems that may consist of just a few electrons.
-Here, we develop a mesoscopic circuit that realizes a direct entropy measurement on the first, second, and third electron occupations in a GaAs quantum dot.
-The dot system is chosen for having well known entropy based on simple spin states\cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-The precision of this technique, quantifying the entropy of a single spin 1/2 to within 3\% of the expected value ($k_B ln 2$), shows its potential for probing more exotic systems in the future, from Majorana states to non-Fermi liquid Kondo states that are clearly identified by a residual low-temperature entropy\cite{Alkurtass2016}.}
+Systems that are difficult to clearly identify through standard conductance measurements may be characterized more precisely with a thermodynamic measurement.
+For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, could be clearly distinguished from the Abelian case by an entropy measurement \cite{Cooper2009, Smirnov2015}.
+Such measurements are typically based on bulk properties, like heat capacity, that are straightforward to observe in macroscopic samples but difficult to access in mesoscopic systems that may consist of only a few electrons.
+Here, we develop a mesoscopic circuit to make a direct entropy measurement on the first, second, and third electron occupations in a GaAs quantum dot.
+This system is chosen for having well-known entropy based on simple spin states\cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
+The precision of this technique, quantifying the entropy of a single spin 1/2 to within 3\% of the expected value ($k_B\ln{2}$), shows its potential for probing more exotic systems, from Majorana states to non-Fermi liquid Kondo states, that are clearly identified by a residual low-temperature entropy\cite{Alkurtass2016}.}
 %Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}.
@@
 \begin{figure}[!]
-        \includegraphics[width=1.0\columnwidth]{../figures/figure_1_no-annotation.pdf}
+        \includegraphics[width=1.0\columnwidth]{../figures/figure_1_annotated.pdf}
         \caption{\label{fig:fig1}(a) Scanning electron micrograph of a device similar to the one measured, showing electrostatic gates (blue) used to define a circuit in the 2D electron gas.
@@
 Electrons tunneling between the reservoir and dot are measured with a capacitively-coupled charge sensor.
-(b) and (c) Charge sensor signal for a single transition from $N-1 \rightarrow N$ electrons at two temperatures ($T_{Red} > T_{Blue}$) showing the two possible cases for $\frac{\partial \mu}{\partial T}$.}
+(b) and (c) Charge sensor signal for a single transition from $N-1 \rightarrow N$ electrons at two temperatures ($T_{Red} > T_{Blue}$) showing two possible cases for $\frac{\partial \mu}{\partial T}$.}
 \end{figure}
@@
 that connects changes in entropy, particle number, and temperature ($S$, $N$, and $T$, respectively) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control.
-The fixed pressure condition of Eq.~\ref{eqn:max} is met by working well below the Fermi temperature of the 2DEG, $T_F \sim$\SI{5}{\kelvin}, where degeneracy pressure dominates \cite{Landau1969}.
+The fixed pressure condition of Eq.~\ref{eqn:max} is met by working well below the Fermi temperature of the 2DEG, $T_F \sim \SI{5}{\kelvin}$, where degeneracy pressure dominates \cite{Landau1969}.
 
-The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to check for non-Abelian exchange of quasiparticles in the the $\nu = \frac{5}{2}$ state, measuring the entropy derivative, $\frac{\partial S}{\partial N}$, by detecting changes in the quasiparticle chemical potential with temperature \cite{Cooper2009,Ben-Shach2013}.
+The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to measure non-Abelian exchange of quasiparticles in the the $\nu = \frac{5}{2}$ state, by detecting changes in the quasiparticle chemical potential with temperature, which are proportional to the entropy derivative, $\frac{\partial S}{\partial N}$ \cite{Cooper2009,Ben-Shach2013}.
 %Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states investigated here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured by detecting the shift with temperature in the electrochemical potential for the $N$th electron on the dot, $\mu_N$, which changes the gate voltage needed to drive the $N-1$ to $N$ electron transition.
+Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured through the shift with temperature in the electrochemical potential needed to add the $N$th electron to the dot, $\mu_N$; the gate voltage at which the $N-1$ to $N$ transition is observed shifts proportionally with $\mu_{N}$.
 %This shift, $\delta \mu$ as a function of $\delta T$, is the quantity probed directly in the experiment described below.
@@
 The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a uses electrostatic gates to realize an electron reservoir (central region; hereafter ``reservoir") in thermal and diffusive equilibrium with a few-electron quantum dot (``dot") coupled to its right side.
-The reservoir temperature, $T_{res}$, could be rapidly (up to at least \SI{100}{\hertz}) elevated above the mixing chamber temperature, $T_{MC}$, by Joule heating through the QPC (``heater") on the left side.
-The occupation of the dot was measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Thierschmann2015}.
+The reservoir temperature, $T_{res}$, could be rapidly (up to at least \SI{100}{\hertz}) increased above the mixing chamber temperature, $T_{MC}$, by Joule heating through the QPC (``heater") on the left side.
+The occupation of the dot was measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Thierschmann2015} [change these references/add additional].
 Applying a more positive voltage to the gate adds the $N$th electron to the dot when $\mu_{N}$ drops below the Fermi level of the reservoir, $E_F$.
-Figure 1b illustrates such a transition \textemdash a step in the charge sensor conductance \textemdash thermally broadened by the reservoir temperature, $T_{res}$.
+Figure 1b illustrates such a transition \textemdash a step in the charge sensor conductance \textemdash thermally broadened by the reservoir temperature.
 The gate voltage corresponding to midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ or $N$ electrons on the dot are equal.
@@
 %Consider the filling of the first electron state, which has a single, unpaired spin-$\frac{1}{2}$ and, therefore, a degeneracy of 2.
-Consider, for example, an electron tunneling into an empty dot: both spin-up and -down states are available.
-Tunneling out, the electron (whether spin-up or -down) must tunnel into reservoir states with the same spin, that is, only half of the reservoir states are available.
+Consider, for example, the first electron tunneling into an empty dot: both spin-up and -down states are available.
+Tunneling out, the electron (whether spin-up or -down) must tunnel into reservoir states with the same spin, that is, only half of the empty reservoir states are available.
 As a result, $\Gamma_{in} = 2\Gamma_{out}$ when $\mu_{N}=E_F$.
-Extending this logic to a general case gives the result derived from detailed balance \cite{Gustavsson2009},
+Extending this logic to a general case gives the result derived from detailed balance \cite{Gustavsson2009, Beenakker1991},
 %
@@
 The equal probability condition for $N-1/N$ at $V_{mid}$ corresponds to  incoming and outgoing rates being equal.
-From Eq.~\ref{eqn:rates}$, \Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N} = E_F$ as long as $g_{N-1}=g_{N}$, but to $\mu_{N} > E_F$ when $g_{N-1} > g_{N}$ and vice versa [Nik check inequalities].
-A measurement of how $V_{mid}$ shifts with temperature quantifies the ratio $g_{N}/g_{N-1}$, giving $\Delta S_{N-1\rightarrow N}$ via the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
-The relationship between degeneracies and tunnel rates was recently explored in a time-resolved measurement \cite{Hofmann2016}.
-The approach presented here confirms the thermodynamic equivalence of the rate measurement, and extends entropy measurements to a much wider set of applications where the tunneling process may not be possible to observe in real-time.
+From Eq.~\ref{eqn:rates}$, \Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N} = E_F$ as long as $g_{N-1}=g_{N}$, but to $\mu_{N} > E_F$ when $g_{N-1} > g_{N}$ and vice versa.
+The ratio $g_{N}/g_{N-1}$ is given by the shift in $V_{mid}$ with temperature, giving $\Delta S_{N-1\rightarrow N}$ via the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
+Previous works have explored the relationship between tunnel rates and degeneracy using AFM coupling and time-resolved transport spectroscopy \cite{Cockins2010, Bennett2010, Beckel2014, Hofmann2016}.
+The approach presented here illustrates the thermodynamic equivalent of the rate measurement, and extends entropy measurements to a wide set of applications where tunneling processes may not be possible to observe in real-time.
 
@@
         \caption{\label{fig:fig2}(a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater.
-(b) Lock-in measurement of $dg_{sens}$ with $\delta T \sim 60mK$.
+(b) Lock-in measurement of $dg_{sens}$ with $\delta T \sim \SI{60}{\milli\kelvin}$.
 Fits to $dg_{sens}$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a function of mixing chamber temperature.
@@
 (d) $\Theta$ as a function of DC current through the QPC heater.
-Fit is used to convert between $I_{heat}$ and $\delta T$, with $R_{QPC} = $ \SI{20}{\kilo\ohm} (e) Change in entropy as a function of AC current through the QPC heater.
+Fit is used to convert between $I_{heat}$ and $\delta T$, with $R_{QPC} = \SI{20}{\kilo\ohm}$ (e) Change in entropy as a function of AC current through the QPC heater.
 Top axis shows corresponding $\delta T$.
@@
 where $\delta=\frac{\partial V_{mid}}{\partial \Theta}$.
-Using the lever arm to convert $V_{mid}$ to electrochemical potential, $\delta$ is just the change in entropy (scaled by $k_B$) through Eq.~\ref{eqn:max}:
+Using the lever arm to convert $V_{mid}$ to electrochemical potential, $\delta$ is simply the change in entropy (scaled by $k_B$) through Eq.~\ref{eqn:max}:
 %
@@
 Dashed line at $V_{SD}$ = \SI{700}{\micro\electronvolt} shows where data in (f) are taken.
-(f) Fixed bias data showing fits to the Zeeman splitting of the ground state (dashed lines) from which $g = -0.44$ is extracted.}
+(f) Fixed bias data showing fits to Zeeman splitting of the ground state (dashed lines) from which $g = -0.44$ is extracted.}
 \end{figure}
@@
 Figure \ref{fig:fig3}a compares $\Delta S(B_\parallel)$ for the 0-1 and 2-3 electron transitions.
-The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $\Delta S_{0 \rightarrow 1}$ and $\Delta S_{2 \rightarrow 3}$ may be expected to correspond to transitions from total spin zero to total spin one-half.
+The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $\Delta S_{0 \rightarrow 1}$ and $\Delta S_{2 \rightarrow 3}$ are expected to correspond to transitions from total spin zero to total spin one-half.
 %One expects identical field-dependent behaviors for $\Delta S_{0\rightarrow 1}$ and $\Delta S_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies.
-The entropies of 1- and 3-electron states are suppressed when the Zeeman splitting lifts the spin degeneracy of the unpaired electron, following the Gibbs entropy for a two-level system:
+The entropies of the 1- and 3-electron states are suppressed when Zeeman splitting lifts the spin degeneracy of the unpaired electron.
+This behavior is described by the Gibbs entropy for a two-level system:
 %
@@
 %
-where $p_{\pm}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_{\parallel}}{k_B T}})^{-1}$ are the probabilities for the system to be in $+/-$ (up/down) spin states at a given field and temperature.
-Fits to the lineshape in Eqn.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, allowing for peak height and the ratio $g/T_{res}$ as free parameters.
+where $p_{\pm}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_{\parallel}}{k_B T}})^{-1}$ are the probabilities for the unpaired electron to be in the spin up/down states at a given field and temperature.
+Fits to Eq.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, allowing for peak height and the ratio $g/T_{res}$ as free parameters.
 
 The entropy measurements yield $\Delta S_{0 \rightarrow 1}=0.93\times k_B \ln{2}$ and $\Delta S_{2 \rightarrow 3}=0.98\times k_B \ln{2}$ at zero magnetic field, collapsing to zero at high field where spin degeneracy is broken.
-At a qualitative level, Figs.~\ref{fig:fig3}b and c show the crossover from asymmetric to antisymmetric as $\Delta S$ goes to zero at high field.
-Using a value for $T_{res}$ of \SI{130}{\milli\kelvin} that is midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T$) points of the temperature oscillation yields $g=-0.39$ and $g=-0.40$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
-This is consistent with the value $g=-0.44$ expected for GaAs and measured via bias spectroscopy in Fig.~\ref{fig:fig3}e.
+At a qualitative level, Figs.~\ref{fig:fig3}b and c show $dg_{sens}$ crossover from asymmetric to antisymmetric as $\Delta S$ goes to zero at high field.
+Using $T_{res} = \SI{130}{\milli\kelvin}$, midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T$) points of the temperature oscillation, yields $g=-0.39$ and $g=-0.40$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
+These are consistent with $g=-0.44$ expected for GaAs and measured via bias spectroscopy in Fig.~\ref{fig:fig3}e.
 
@@
 At \SI[input-protect-tokens]{\sim 9}{\tesla} $T_+$ becomes degenerate with $S$.
-$g=40$ is determined using $T_0$ and $T_+$ fits (dashed).}
+$g=-0.40$ is determined using $T_0$ and $T_+$ fits (dashed).}
 \end{figure}
 
-The $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}a) can be understood as the inverse of Fig \ref{fig:fig3}a for $B_\parallel$ less than \SI{5}{\tesla}.
-There, the 2-electron ground state remains in the spin singlet state ($S_2=0$) while the 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
-At higher field, the 1-electron ground state remains non-degenerate ($S_1=0$) while the 2-electron ground state becomes two-fold degenerate where the singlet ($S$) and triplet ($T_+$) states cross.
+The $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}a) can be understood as the inverse of Fig \ref{fig:fig3}a for $B_\parallel < \SI{5}{\tesla}$.
+There, the 2-electron ground state remains a spin singlet ($S_2=0$) while the 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
+At higher field, the 1-electron ground state remains non-degenerate ($S_1=0$) while the 2-electron ground state becomes two-fold degenerate where the spin singlet ($S$) and triplet ($T_+$) states cross.
 The singlet-triplet crossing is seen clearly around at \SI{9}{\tesla} in bias spectroscopy data for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}e).
@@
 At the high-field singlet-triplet degeneracy we find $g = 0.59$.
-This unexpectedly high g-factor can be explained by a shifting of the $T_{0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work [cite PHYSICAL REVIEW B 70, 235335 (2004)].
-The high quality of the Gibbs entropy fit confirms $\Delta S$ illustrates the tunable degeneracy in the system.
+This unexpectedly high g-factor can be explained by a shifting of the $T_{0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work \cite{Szafran2004}.
+The high quality of the Gibbs entropy fit confirms $\Delta S$ and illustrates a tunable degeneracy in the system.
 
@@
 In conclusion, we show that the entropy of few-particle states in mesoscopic devices can be measured directly.
-Using the well-understood spin degeneracy of  few-electron ground states states in a GaAs quantum dot for calibration, the entropy can be quantified within 5\% of the expected $k_B\ln{2}$.
+Using the well-understood spin degeneracy of  few-electron ground states states in a GaAs quantum dot for calibration, the entropy can be quantified within 5\% of the expected $\pm k_B\ln{2}$.
 Future work may take advantage of this strategy to look for thermodynamic signatures of non-trival electron and quasiparticle states, eliminating the uncertainty found in typical transport data.
@@
 Applying AC current at $f_{Heat} =$ \SI{48.7}{\hertz} yields oscillations in $T_{res}$ at $2f_{heat}$; to leading order $\delta T_{res} \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$.
-Variations in $g_{sens}$ with $dT$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
+Variations in $g_{sens}$ with $\delta T$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
 

### 2018-02-19 data_tools.py

@@ -78,8 +78,9 @@ def shiftedColorMap(cmap, start=0, midpoint=0.5, stop=1.0, name='shiftedcmap'):
 
     return newcmap
 
-def add_subplot_id(ax, id_lttr, loc, fontsize=18):
-    ax.text(*loc, '({0:s})'.format(id_lttr), transform=ax.transAxes, fontsize=fontsize)
+def add_subplot_id(ax, id_lttr, loc, fontsize=16):
+    ax.text(*loc, r'{0:s}'.format(id_lttr), transform=ax.transAxes, 
+            fontsize=fontsize, fontweight='bold')
 
 #########################
 ### DATA MANIPULATION ###
@@ -304,7 +305,6 @@ def i_sense_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, 
 def di_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, fix = None, span = None):
     
     def di_dataset(params, i, xx):
-        """ Weak localization peak fitting function. Adapted from Igor code. """
         
         x0 = params['x0_{0:d}'.format(i)]
         theta = params['theta_{0:d}'.format(i)]
@@ -316,7 +316,7 @@ def di_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, fix =
     
     def di_objective(params, xx, zz, idx0, idx1):
         """ calculate total residual for fits to several data sets held
-            in a 2-D array, and modeled by Gaussian functions"""
+            in a 2-D array """
         
         n,m = zz.shape
         resid = []

### 2018-02-19 paper/draft.tex
even more matplotlib
fixing some factors of 2

@@
+%%% variables %%%
+
 % double check \Theta calculations -- is the whole thing off by a factor of 2???
+
+%%% plotting stuff %%%
+
 % error bars on dS values from a single fit
+
+%%% text stuff %%%
 
@@
 This system is chosen for having well-known entropy based on simple spin states\cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-The precision of this technique, quantifying the entropy of a single spin 1/2 to within 3\% of the expected value ($k_B\ln{2}$), shows its potential for probing more exotic systems, from Majorana states to non-Fermi liquid Kondo states, that are clearly identified by a residual low-temperature entropy\cite{Alkurtass2016}.}
+The precision of this technique, quantifying the entropy of a single spin $\frac{1}{2}$ to within 5\% of the expected value ($k_B\ln{2}$), shows its future potential for probing more exotic systems, from Majorana states to non-Fermi liquid Kondo states, that are clearly identified by a residual low-temperature entropy\cite{Alkurtass2016}.}
 %Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}.
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_1_annotated.pdf}
-        \caption{\label{fig:fig1}(a) Scanning electron micrograph of a device similar to the one measured, showing electrostatic gates (blue) used to define a circuit in the 2D electron gas.
-Grey gates are unused (grounded).
+        \caption{\label{fig:fig1}(a) Scanning electron micrograph of a device similar to the one measured, showing electrostatic gates (gold) used to define a circuit in a 2D electron gas (2DEG).
+Grey gates are grounded.
 Squares show the locations of ohmic contacts to the 2DEG.
-An electron reservoir is formed between the parallel gates running vertically down the image.
+An electron reservoir is formed between the parallel gates running vertically down the image, with a quantum dot coupled to the right side.
 The reservoir can be heated by driving current through the quantum point contact on the left.
-A 200nm diameter quantum dot is coupled to the right side of the channel.
 Electrons tunneling between the reservoir and dot are measured with a capacitively-coupled charge sensor.
-(b) and (c) Charge sensor signal for a single transition from $N-1 \rightarrow N$ electrons at two temperatures ($T_{Red} > T_{Blue}$) showing two possible cases for $\frac{\partial \mu}{\partial T}$.}
+(b) and (c) Simulated charge sensor signal for a transition from $N-1 \rightarrow N$ electrons at two temperatures ($T_{Red} > T_{Blue}$), showing two possible cases for $\frac{\partial S}{\partial N}$.}
 \end{figure}
@@
 
-Our approach is analogous to the milestone of spin-to-charge conversion by which undetectably-small magnetic moments of a single spin were transformed into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
+Our approach is analogous to the milestone of spin-to-charge conversion achieved over a decade ago, by which unmeasurably-small magnetic moments of a single spin were detected indirectly by transforming into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
 Instead, we perform an entropy-to-charge conversion, making use of the Maxwell relation
@@
 %Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states investigated here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured through the shift with temperature in the electrochemical potential needed to add the $N$th electron to the dot, $\mu_N$; the gate voltage at which the $N-1$ to $N$ transition is observed shifts proportionally with $\mu_{N}$.
+Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured through the shift with temperature in the electrochemical potential, $\mu_N$, needed to add the $N$th electron to the dot; the gate voltage at which the $N-1$ to $N$ transition is observed shifts linearly with $\mu_{N}$.
 %This shift, $\delta \mu$ as a function of $\delta T$, is the quantity probed directly in the experiment described below.
@@
 Figure 1b illustrates such a transition \textemdash a step in the charge sensor conductance \textemdash thermally broadened by the reservoir temperature.
-The gate voltage corresponding to midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ or $N$ electrons on the dot are equal.
+The gate voltage corresponding to the midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ or $N$ electrons on the dot are equal.
 When $\mu_N$ shifts with temperature, $V_{mid}$ also shifts (Fig.~1c); it is this signature that forms the basis of our experiment.%and the $N$th level is occupied half the time.
@@
         \caption{\label{fig:fig2}(a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater.
-(b) Lock-in measurement of $dg_{sens}$ with $\delta T \sim \SI{60}{\milli\kelvin}$.
-Fits to $dg_{sens}$ are shown with $\delta$ as a free parameter (solid) and $\delta=0$ (dashed) (c) Transition width, $\Theta$, as a function of mixing chamber temperature.
-The highlighted region shows roughly where tunnel rates are determined only by temperature broadening.
+(b) Lock-in measurement of $\delta g_{sens}$ with $\delta T = \SI{32}{\milli\kelvin}$.
+Fits to $\delta g_{sens}$ are shown with $\epsilon$ as a free parameter (solid) or fixed at $\epsilon=0$ (dashed) (c) Transition width, $\Theta$, was linear in $T_{MC}$ above 100 mK.
 The lever arm $\alpha$ is calculated by fitting a straight line to this region.
-(d) $\Theta$ as a function of DC current through the QPC heater.
-Fit is used to convert between $I_{heat}$ and $\delta T$, with $R_{QPC} = \SI{20}{\kilo\ohm}$ (e) Change in entropy as a function of AC current through the QPC heater.
+(d) $\Theta$ grows DC current through the QPC heater.
+Fit is used to convert between $I_{heat}$ and $\delta T$, with $R_{QPC} = \SI{20}{\kilo\ohm}$ [CITATION OF FIT] (e) Change in entropy as a function of AC current through the QPC heater [IN GENERAL I DO NOT LIKE RESTATING AXES OF GRAPHS IN CAPTIONS].
 Top axis shows corresponding $\delta T$.
-Right axis shows shift in $\delta V_{mid}$ per unit temperature.}
+Right axis shows shift in $V_{mid}$ per unit temperature.}
 \end{figure}
@@
 %
-where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm $\alpha\equiv\partial \mu_{N}/\partial V_G$, and $G_1$ is determined by the cross capacitance between the charge sensor and plunger gate.
-With no Joule heating through the heater, $\Theta$ was found to follow $T_{MC}$ down to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b), validating the approximation of thermal broadening used throughout this experiment.
+where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm $\alpha\equiv\partial \mu_{N}/\partial V_G$, and $G_1$ reflects the cross capacitance between the charge sensor and plunger gate.
+With no Joule heating through the heater, $\Theta$ followed $T_{MC}$ down to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b), validating the approximation of thermal broadening used throughout this experiment.
 
@@
 The data in Fig.~\ref{fig:fig2}c, and corresponding fits, offer an example of how $\Delta S_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ transition.
-A comparison of the curves in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as temperature rises before the midpoint of the transition ($V_G-V_{mid}<0$), whereas $g_{sens}$ is higher in the warmer curve for $V_G-V_{mid}>0$.
+A comparison of the curves in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as temperature rises immediately before the midpoint of the transition ($V_G-V_{mid}<0$), whereas $g_{sens}$ is higher in the warmer curve for $V_G-V_{mid}>0$.
 Oscillating the reservoir temperature by $\delta T_{res}$ using an AC current through the heater while measuring oscillations in $g_{sens}$ with a lock in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
-The expected lineshape of such a curve is given by the derivative of Eq.~\ref{eqn:g} with respect to temperature, expressed as $dg_{sens}$ due to a temperature change $\delta T$:
+The expected lineshape of such a curve is given by the derivative of Eq.~\ref{eqn:g} with respect to temperature, expressed as $\delta g_{sens}$ due to a temperature change $\delta T$:
 %
@@
 \label{eqn:dg}
-        dg_{sens}(V_G, \Theta) &\propto \delta T \left[ \frac{V_G-V_{mid}(\Theta)}{2\Theta} +\delta \right]\times \\
+        \delta g_{sens}(V_G, \Theta) &\propto -\delta T \left[ \frac{V_G-V_{mid}(\Theta)}{2\Theta} + \frac{\epsilon}{2} \right]\times \\
         				      &\quad\cosh^{-2}\left(\frac{V_G-V_{mid}(\Theta)}{2\Theta}\right) + const. \nonumber
@@
 %
-where $\delta=\frac{\partial V_{mid}}{\partial \Theta}$.
-Using the lever arm to convert $V_{mid}$ to electrochemical potential, $\delta$ is simply the change in entropy (scaled by $k_B$) through Eq.~\ref{eqn:max}:
+where $\epsilon=\frac{\partial V_{mid}}{\partial \Theta}$.
+Using the lever arm to convert $V_{mid}$ to electrochemical potential, $\epsilon$ is simply the change in entropy (scaled by $k_B$) through Eq.~\ref{eqn:max}:
 %
 \begin{align}
-\label{eqn:delta}
-        \delta &= \frac{\partial V_{mid}}{\partial \Theta} = 
+\label{eqn:epsilon}
+        \epsilon &= \frac{\partial V_{mid}}{\partial \Theta} = 
         \frac{1}{k_B} \frac{\partial \mu}{\partial T} = 
@@
 
-From Eqs.~\ref{eqn:dg} and \ref{eqn:delta}, $dg_{sens}(V_G)$ would be perfectly antisymmetric around $V_{mid}$ if $\Delta S_{N-1\rightarrow N}$ were zero.
-The best fit of Eqs.~\ref{eqn:dg} and \ref{eqn:delta} to the data in Fig.~\ref{fig:fig2}c yields $\Delta S_{0\rightarrow 1}=0.71\times k_B$.
-Indeed, this is what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate 1-electron state one expects $S_1=k_B\ln{2}$, giving $\Delta S_{0\rightarrow 1}\equiv S_1 = S_0 =k_B\ln{2}$.
+From Eqs.~\ref{eqn:dg} and \ref{eqn:delta}, $\delta g_{sens}(V_G)$ would be perfectly antisymmetric around $V_{mid}$ if $\Delta S_{N-1\rightarrow N}$ were zero, whereas the data in Fig.~\ref{fig:fig2}c is clearly not antisymmetric.
+A best fit to Eqs.~\ref{eqn:dg} and \ref{eqn:delta} yields $\Delta S_{0\rightarrow 1}=0.71\times k_B$.
+This is close to what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate one-electron state one expects $S_1=k_B\ln{2}$, giving $\Delta S_{0\rightarrow 1}\equiv S_1 - S_0 =k_B\ln{2}$.
 Fig.~\ref{fig:fig2}e shows that $\Delta S$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T_{res}$ ($I^{AC}_{Heat}$).
-Although the extracted $\delta$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $dg_{sens}$ without any additional calibration, and without knowing the precise value of $\delta T_{res}$.
+Although the extracted $\epsilon$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $\delta g_{sens}$ without any additional calibration, and without knowing the precise value of $\delta T_{res}$.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_3.pdf}
-        \caption{\label{fig:fig3}(a) Change in entropy, determined from $dg_{sens}$ fits at varying parallel magnetic field.
+        \caption{\label{fig:fig3}(a) Change in entropy, determined from $\delta g_{sens}$ fits at varying parallel magnetic field.
 The $N=0 \rightarrow 1$ and $2 \rightarrow 3$ data are overlaid here to show the similar behavior of these states at low field.
-(b) and (c) show characteristic $dg_{sens}$ traces from which the data in (c) were extracted.
+(b) and (c) show characteristic $\delta g_{sens}$ traces from which the data in (c) were extracted.
 These data points are show as large markers in (c).
@@
 The entropy measurements yield $\Delta S_{0 \rightarrow 1}=0.93\times k_B \ln{2}$ and $\Delta S_{2 \rightarrow 3}=0.98\times k_B \ln{2}$ at zero magnetic field, collapsing to zero at high field where spin degeneracy is broken.
-At a qualitative level, Figs.~\ref{fig:fig3}b and c show $dg_{sens}$ crossover from asymmetric to antisymmetric as $\Delta S$ goes to zero at high field.
+At a qualitative level, Figs.~\ref{fig:fig3}b and c show $\delta g_{sens}$ crossover from asymmetric to antisymmetric as $\Delta S$ goes to zero at high field.
 Using $T_{res} = \SI{130}{\milli\kelvin}$, midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T$) points of the temperature oscillation, yields $g=-0.39$ and $g=-0.40$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_4.pdf}
-        \caption{\label{fig:fig4}(c) Change in entropy, extracted from $dg_{sens}$ fits at varying parallel field.
-Dashed line shows fit to Eq.~\ref{eqn:gibbs} (b), (c), and (d) show characteristic $dg_{sens}$ traces from which the data in (c) were extracted.
+        \caption{\label{fig:fig4}(c) Change in entropy, extracted from $\delta g_{sens}$ fits at varying parallel field.
+Dashed line shows fit to Eq.~\ref{eqn:gibbs} (b), (c), and (d) show characteristic $\delta g_{sens}$ traces from which the data in (c) were extracted.
 These data points are show as large markers in (c).

### 2018-02-19 data_tools.py

@@ -165,13 +165,13 @@ def parabola(x, a, b, c):
 
 def i_sense(x, x0, theta, i0, i1, i2):
     """ fit to sensor current """
-    arg = (x-x0)/theta
+    arg = (x-x0)/(2*theta)
     return -i0*np.tanh(arg) + i1*(x-x0) + i2
 
-def di_sense_simple(x, x0, theta, di0, di2, delta):
+def di_sense_simple(x, x0, theta, di0, di2, epsilon):
     """ fit charge sensor lock in signal """
-    arg = (x-x0)/theta
-    return -(0.5)*di0*(arg+delta)*(np.cosh(arg)**-2) + di2
+    arg = (x-x0)/(2*theta)
+    return -1.0*di0*(arg+0.5*epsilon)*(np.cosh(arg)**-2) + di2
 
 def p_up(field, temp, g, de):
     return 1/(1+np.exp(-(g*MU_B*field-de)/(K_B*temp)))
@@ -310,9 +310,9 @@ def di_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, fix =
         theta = params['theta_{0:d}'.format(i)]
         di0 = params['di0_{0:d}'.format(i)]
         di2 = params['di2_{0:d}'.format(i)]
-        delta = params['delta_{0:d}'.format(i)]
+        epsilon = params['epsilon_{0:d}'.format(i)]
         
-        return di_sense_simple(xx, x0, theta, di0, di2, delta)
+        return di_sense_simple(xx, x0, theta, di0, di2, epsilon)
     
     def di_objective(params, xx, zz, idx0, idx1):
         """ calculate total residual for fits to several data sets held
@@ -354,7 +354,7 @@ def di_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, fix =
         ilow = np.zeros(n, dtype=np.int)
         ihigh = -1*np.ones(n, dtype=np.int)
     
-    columns = ['x0', 'theta', 'di0', 'di2', 'delta']
+    columns = ['x0', 'theta', 'di0', 'di2', 'epsilon']
     df = pd.DataFrame(columns=columns)
     
     # add constraints specified in the 'constrain' list
@@ -367,9 +367,9 @@ def di_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, fix =
             fit_params.add('x0_{0:d}'.format(i), value=centers[i], min=x0bounds[0], max=x0bounds[1])
[…]

### 2018-02-19 data_tools.py
more factors of 2

@@ -275,9 +275,10 @@ def i_sense_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, 
 
         for i in range(n):
             fit_params.add('x0_{0:d}'.format(i), value=centers[i], min=x0bounds[0], max=x0bounds[1])
-            fit_params.add('theta_{0:d}'.format(i), value=widths[i], min=0.2, max=10.0)
+            fit_params.add('theta_{0:d}'.format(i), value=widths[i], min=0.05, max=10.0)
             fit_params.add('i0_{0:d}'.format(i), 
-                            value=abs(z[i,ilow[i]:ihigh[i]].max()-z[i,ilow[i]:ihigh[i]].min()), min=0.001, max=10.0)
+                            value=abs(z[i,ilow[i]:ihigh[i]].max()-z[i,ilow[i]:ihigh[i]].min()),
+                            min=0.001, max=10.0)
             fit_params.add('i1_{0:d}'.format(i), value=0.1, min=0.0, max=10.0)
             fit_params.add('i2_{0:d}'.format(i), value=z[i,ilow[i]:ihigh[i]].mean(), min=0.0, max=20.0)
 
@@ -297,7 +298,7 @@ def i_sense_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, 
         for i in range(n):
             p0 = [centers[i], widths[i], abs(z[i,ilow[i]:ihigh[i]].max()-z[i,ilow[i]:ihigh[i]].min()),
                       0.1, z[i,ilow[i]:ihigh[i]].mean()]
-            bounds = [(x0bounds[0], 0.2, 0.001, 0.0, 0.0), (x0bounds[1], 10.0, 10.0, 10.0, 20.0)]
+            bounds = [(x0bounds[0], 0.05, 0.001, 0.0, 0.0), (x0bounds[1], 10.0, 10.0, 10.0, 20.0)]
             df.loc[i], _ = curve_fit(i_sense, x[i,ilow[i]:ihigh[i]], z[i,ilow[i]:ihigh[i]], p0=p0, bounds=bounds)
                           
     return df
@@ -365,7 +366,7 @@ def di_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, fix =
 
         for i in range(n):
[…]

### 2018-02-23 paper/draft.tex
change some markersizes. add error bars in text.

@@
-%%% variables %%%
-
-% double check \Theta calculations -- is the whole thing off by a factor of 2???
-
-%%% plotting stuff %%%
-
-% error bars on dS values from a single fit
-
-%%% text stuff %%%
-
-% add mention about Fig 2d by rewording this sentence: 
-%"Although the extracted  can b e converted to gate-voltage-per-temperature units using a value for 
-%  measured separately (right axis of Fig. 2e), the entropy itself, S , is determined directly from the 
-%  t to dg_sens without any additional calibration, and without knowing the precise value of  T_res"
-
-% mention QPC heater in text when discussing Fig 2a -- define I_{heat} in here 
-% add equation and citation for fit in Fig 2d to caption
-% remove _{res} subscripts from temps
-% peak height --> "an added scaling parameter (dS(B=0))" when describing dS vs B fits
-
 \documentclass[twocolumn,showpacs,amsmath,amssymb,prl,aps,superscriptaddress]{revtex4-1}
@@
 \thanks{The raw data and Python code used for all figures and analysis can be found at \url{https://github.com/nikhartman/spin_entropy}}
-\affiliation{University of British Columbia, Vancouver, BC, Canada}
-\author{Saeed Fallahi}
-\affiliation{Purdue University, Lafayette, IN, USA}
-\author{Geoffrey C. Gardner}
-\affiliation{Purdue University, Lafayette, IN, USA}
+	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
+	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
 \author{Christian Olsen}
-\affiliation{University of British Columbia, Vancouver, BC, Canada}
+	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
+	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
 \author{Silvia Folk}
-\affiliation{University of British Columbia, Vancouver, BC, Canada}
+	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
+	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
 \author{Mohammad Samani}
@@
 	\altaffiliation{Fields Institute for Research in Mathematical Sciences, Toronto, ON, Canada}
-\affiliation{University of British Columbia, Vancouver, BC, Canada}
+	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
+	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
+\author{Saeed Fallahi}
+	\affiliation{Department of Physics and Astronomy, Purdue University}
+	\affiliation{Station Q Purdue, Purdue University}
+	\affiliation{Birck Nanotechnology Center, Purdue University, West Lafayette, Indiana, USA}
+\author{Geoffrey C. Gardner}
+	\affiliation{Station Q Purdue, Purdue University}
+	\affiliation{Birck Nanotechnology Center, Purdue University, West Lafayette, Indiana, USA}
+    	\affiliation{School of Materials Engineering, Purdue University, West Lafayette, Indiana, USA}
 \author{Michael Manfra}
-\affiliation{Purdue University, Lafayette, IN, USA}
+	\affiliation{Department of Physics and Astronomy, Purdue University}
+	\affiliation{Station Q Purdue, Purdue University}
+	\affiliation{Birck Nanotechnology Center, Purdue University, West Lafayette, Indiana, USA}
+	\affiliation{School of Electrical and Computer Engineering,  Purdue University, West Lafayette, Indiana, USA}
+    	\affiliation{School of Materials Engineering, Purdue University, West Lafayette, Indiana, USA}
 \author{Joshua Folk}
-\affiliation{University of British Columbia, Vancouver, BC, Canada}
+\email{jfolk@physics.ubc.ca}
+	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
+	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
 \date{\today}
@@
 This system is chosen for having well-known entropy based on simple spin states\cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-The precision of this technique, quantifying the entropy of a single spin $\frac{1}{2}$ to within 5\% of the expected value ($k_B\ln{2}$), shows its future potential for probing more exotic systems, from Majorana states to non-Fermi liquid Kondo states, that are clearly identified by a residual low-temperature entropy\cite{Alkurtass2016}.}
-%Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}.
-A more direct test for the two-channel Kondo state would be a confirmation of its entropy ($\frac{1}{2} k_B \ln{2}$), that should remain down to arbitrarily low temperatures \cite{Alkurtass2016}.
+The precision of this technique, quantifying the entropy of a single spin-$\frac{1}{2}$ to within 5\% of the expected value ($k_B \ln{2}$), shows its future potential for probing more exotic systems, from Majorana states to non-Fermi liquid Kondo states, that are clearly identified by a residual low-temperature entropy\cite{Alkurtass2016}.}
 
@@
 
-%Entropy can be probed effectively in 3D macroscopic samples via measurements of heat capacity, but the heat capacities of single electrons or quasiparticles are much too small to measure directly; even the 2D sheet of quasiparticles in $\nu = \frac{5}{2}$ fractional quantum Hall samples has a heat capacity that vanishes in comparison to that of the host crystal.
-Rather than attempt to resolve such infinitesimal signals, the problem can be avoided by converting changes in entropy to changes in charge \textemdash a quantity that is easily detected at the single particle level.
-
 Our approach is analogous to the milestone of spin-to-charge conversion achieved over a decade ago, by which unmeasurably-small magnetic moments of a single spin were detected indirectly by transforming into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
@@
 The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to measure non-Abelian exchange of quasiparticles in the the $\nu = \frac{5}{2}$ state, by detecting changes in the quasiparticle chemical potential with temperature, which are proportional to the entropy derivative, $\frac{\partial S}{\partial N}$ \cite{Cooper2009,Ben-Shach2013}.
-%Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states investigated here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
 Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured through the shift with temperature in the electrochemical potential, $\mu_N$, needed to add the $N$th electron to the dot; the gate voltage at which the $N-1$ to $N$ transition is observed shifts linearly with $\mu_{N}$.
-%This shift, $\delta \mu$ as a function of $\delta T$, is the quantity probed directly in the experiment described below.
-From these measurements the entropies of the first three quantum dot levels are built up, demonstrating a direct entropy measurement is possible on a few-particle system.
-In the future, the method can be utilized to probe the nature of more exotic systems, such as topologically non-trivial Majorana and other non-Abelian states.
 
 The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a uses electrostatic gates to realize an electron reservoir (central region; hereafter ``reservoir") in thermal and diffusive equilibrium with a few-electron quantum dot (``dot") coupled to its right side.
-The reservoir temperature, $T_{res}$, could be rapidly (up to at least \SI{100}{\hertz}) increased above the mixing chamber temperature, $T_{MC}$, by Joule heating through the QPC (``heater") on the left side.
+The reservoir temperature, $T$, could be rapidly (up to at least \SI{100}{\hertz}) increased above the mixing chamber temperature, $T_{MC}$, by Joule heating through the QPC (``heater") on the left side.
 The occupation of the dot was measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Thierschmann2015} [change these references/add additional].
@@
 The gate voltage corresponding to the midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ or $N$ electrons on the dot are equal.
-When $\mu_N$ shifts with temperature, $V_{mid}$ also shifts (Fig.~1c); it is this signature that forms the basis of our experiment.%and the $N$th level is occupied half the time.
+When $\mu_N$ shifts with temperature, $V_{mid}$ also shifts (Fig.~1c); it is this signature that forms the basis of our experiment.
 
@@
 The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$, depend on degeneracy of the $N-1$ and $N$ ground states.
-%Consider the filling of the first electron state, which has a single, unpaired spin-$\frac{1}{2}$ and, therefore, a degeneracy of 2.
 Consider, for example, the first electron tunneling into an empty dot: both spin-up and -down states are available.
@@
 The ratio $g_{N}/g_{N-1}$ is given by the shift in $V_{mid}$ with temperature, giving $\Delta S_{N-1\rightarrow N}$ via the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
-Previous works have explored the relationship between tunnel rates and degeneracy using AFM coupling and time-resolved transport spectroscopy \cite{Cockins2010, Bennett2010, Beckel2014, Hofmann2016}.
+Previous works have explored the relationship between tunnel rates and degeneracy using time-resolved transport spectroscopy and coupling of quantum dots to atomic force microscope oscillations \cite{Cockins2010, Bennett2010, Beckel2014, Hofmann2016}.
 The approach presented here illustrates the thermodynamic equivalent of the rate measurement, and extends entropy measurements to a wide set of applications where tunneling processes may not be possible to observe in real-time.
-
-%%%%%%%%%%%%%%%%%%%%%%%
 
@@
         \caption{\label{fig:fig2}(a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater.
-(b) Lock-in measurement of $\delta g_{sens}$ with $\delta T = \SI{32}{\milli\kelvin}$.
-Fits to $\delta g_{sens}$ are shown with $\epsilon$ as a free parameter (solid) or fixed at $\epsilon=0$ (dashed) (c) Transition width, $\Theta$, was linear in $T_{MC}$ above 100 mK.
-The lever arm $\alpha$ is calculated by fitting a straight line to this region.
-(d) $\Theta$ grows DC current through the QPC heater.
-Fit is used to convert between $I_{heat}$ and $\delta T$, with $R_{QPC} = \SI{20}{\kilo\ohm}$ [CITATION OF FIT] (e) Change in entropy as a function of AC current through the QPC heater [IN GENERAL I DO NOT LIKE RESTATING AXES OF GRAPHS IN CAPTIONS].
-Top axis shows corresponding $\delta T$.
-Right axis shows shift in $V_{mid}$ per unit temperature.}
+(b) Transition width, $\Theta$, was linear in $T_{MC}$ above 100 mK, for $I_{heat}=0$.
+Lever arm $\alpha$ is calculated by fitting a straight line to this region.
+(c) Lock-in measurement of $\delta g_{sens}$ with $\delta T = \SI{32}{\milli\kelvin}$.
+Fits to $\delta g_{sens}$ are shown with $\epsilon$ as a free parameter (solid) or fixed at $\epsilon=0$ (dashed)  (d) $\Theta$ grows with DC current through the QPC heater.
+A fit to $T = a\sqrt{T^{2}_{MC}+b I_{heat}R_{QPC}}$ is used to convert between $I_{heat}$ and $\delta T$, with $R_{QPC} = \SI{20}{\kilo\ohm}$ \cite{Mittal1996} (e)  Entropy measurements were independent of the magnitude of $I_{heat}$ oscillations.
+Top axis illustrates the corresponding magnitude of $\delta T$, while right axes shows the entropy signal converted to a gate voltage shift.}
 \end{figure}
 
-%%% device setup %%%
 To proceed with the entropy measurement, the quantum dot (Fig.~\ref{fig:fig1}a) was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
 The conductance of the charge sensor was tuned to $g_{sens}{\sim}e^2/h$ where it was most sensitive to charge on the dot.
-The addition of the first electron to the dot was marked by a decrease in $g_{sens}$ that is well fit by the expected form for a thermally-broadened transition (Fig.~\ref{fig:fig2}a):
+The addition of the first electron to the dot was marked by a decrease in $g_{sens}$ that is well fit by the expected form for a thermally-broadened transition:
 %
@@
 where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm $\alpha\equiv\partial \mu_{N}/\partial V_G$, and $G_1$ reflects the cross capacitance between the charge sensor and plunger gate.
+Fig.~\ref{fig:fig2}a shows two such transition curves with the high temperature curve being thermally broadened by driving a current, $I_{heat}$ through the QPC heater.
 With no Joule heating through the heater, $\Theta$ followed $T_{MC}$ down to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b), validating the approximation of thermal broadening used throughout this experiment.
 
-%The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} follows the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
-The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T_{res}$ up to \SI{250}{\milli\kelvin}.
-Measurements of $\Delta S$ are made at $\delta T_{res} = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
-
-%%% figs 2c and d%%%
 The data in Fig.~\ref{fig:fig2}c, and corresponding fits, offer an example of how $\Delta S_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ transition.
-A comparison of the curves in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as temperature rises immediately before the midpoint of the transition ($V_G-V_{mid}<0$), whereas $g_{sens}$ is higher in the warmer curve for $V_G-V_{mid}>0$.
-Oscillating the reservoir temperature by $\delta T_{res}$ using an AC current through the heater while measuring oscillations in $g_{sens}$ with a lock in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
+A comparison of the curves in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as temperature rises immediately before the midpoint of the transition ($V_G-V_{mid}<0$), whereas $g_{sens}$ rises with temperature for $V_G-V_{mid}>0$.
+Oscillating the reservoir temperature by $\delta T$ using an AC current through the heater while measuring oscillations in the charge sensor signal, $\delta g_{sens}$, with a lock in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
 The expected lineshape of such a curve is given by the derivative of Eq.~\ref{eqn:g} with respect to temperature, expressed as $\delta g_{sens}$ due to a temperature change $\delta T$:
@@
 
-From Eqs.~\ref{eqn:dg} and \ref{eqn:delta}, $\delta g_{sens}(V_G)$ would be perfectly antisymmetric around $V_{mid}$ if $\Delta S_{N-1\rightarrow N}$ were zero, whereas the data in Fig.~\ref{fig:fig2}c is clearly not antisymmetric.
-A best fit to Eqs.~\ref{eqn:dg} and \ref{eqn:delta} yields $\Delta S_{0\rightarrow 1}=0.71\times k_B$.
-This is close to what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate one-electron state one expects $S_1=k_B\ln{2}$, giving $\Delta S_{0\rightarrow 1}\equiv S_1 - S_0 =k_B\ln{2}$.
-Fig.~\ref{fig:fig2}e shows that $\Delta S$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T_{res}$ ($I^{AC}_{Heat}$).
-Although the extracted $\epsilon$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $\delta g_{sens}$ without any additional calibration, and without knowing the precise value of $\delta T_{res}$.
+From Eqs.~\ref{eqn:dg} and \ref{eqn:epsilon}, $\delta g_{sens}(V_G)$ would be perfectly antisymmetric around $V_{mid}$ if $\Delta S_{N-1\rightarrow N}$ were zero, whereas the data in Fig.~\ref{fig:fig2}c are clearly not antisymmetric.
+A best fit to Eqs.~\ref{eqn:dg} and \ref{eqn:epsilon} yields $\Delta S_{0\rightarrow 1}=0.72 \pm 0.01 k_B$, close to what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate one-electron state one expects $S_1=k_B\ln{2}$, giving $\Delta S_{0\rightarrow 1}\equiv S_1 - S_0 =k_B\ln{2}$.
+
+Fig.~\ref{fig:fig2}e shows that $\Delta S$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T$ (I$_{heat}$ AC).
+To confirm the measurement lies within the the relevant limits, the magnitude of the temperature change, $\delta T$ is calibrated in Fig.~\ref{fig:fig2}d and the corresponding shift in $V_{mid}$ is plotted long the right side of Fig.~\ref{fig:fig2}e.
+However, it is important to note that the change in entropy, $\Delta S$, is determined from the fit parameter, $\epsilon$, with no further calibration.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_3.pdf}
-        \caption{\label{fig:fig3}(a) Change in entropy, determined from $\delta g_{sens}$ fits at varying parallel magnetic field.
-The $N=0 \rightarrow 1$ and $2 \rightarrow 3$ data are overlaid here to show the similar behavior of these states at low field.
-(b) and (c) show characteristic $\delta g_{sens}$ traces from which the data in (c) were extracted.
-These data points are show as large markers in (c).
-(e) Bias spectroscopy data for $N=0 \rightarrow 1$ transition.
+        \caption{\label{fig:fig3}(a) Changes in entropy for $N=0 \rightarrow 1$ and $2 \rightarrow 3$ transitions, overlaid to highlight similar behaviors.
+Each datapoint corresponds to a fit to a single $\delta g_{sens}(V_G)$ trace; multiple scans are carried out at various parallel magnetic fields.
+(b) and (c) Characteristic $\delta g_{sens}$ traces from which the data in (a) were extracted.
+The two data points corresponding to (b) and (c) are shown as large markers in (a).
+(e) Bias spectroscopy data for the $N=0 \rightarrow 1$ transition.
 Dashed line at $V_{SD}$ = \SI{700}{\micro\electronvolt} shows where data in (f) are taken.
-(f) Fixed bias data showing fits to Zeeman splitting of the ground state (dashed lines) from which $g = -0.44$ is extracted.}
+(f) Fixed bias data showing fits to Zeeman splitting of the ground state (dashed lines) from which $g = -0.42 \pm 0.01$ is extracted.}
 \end{figure}
@@
 The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $\Delta S_{0 \rightarrow 1}$ and $\Delta S_{2 \rightarrow 3}$ are expected to correspond to transitions from total spin zero to total spin one-half.
-%One expects identical field-dependent behaviors for $\Delta S_{0\rightarrow 1}$ and $\Delta S_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies.
 The entropies of the 1- and 3-electron states are suppressed when Zeeman splitting lifts the spin degeneracy of the unpaired electron.
@@
 where $p_{\pm}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_{\parallel}}{k_B T}})^{-1}$ are the probabilities for the unpaired electron to be in the spin up/down states at a given field and temperature.
-Fits to Eq.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, allowing for peak height and the ratio $g/T_{res}$ as free parameters.
+Fits to Eq.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, with the ration $g/T$ and an added scaling $\Delta S(B=0)$ as free parameters.
 
-The entropy measurements yield $\Delta S_{0 \rightarrow 1}=0.93\times k_B \ln{2}$ and $\Delta S_{2 \rightarrow 3}=0.98\times k_B \ln{2}$ at zero magnetic field, collapsing to zero at high field where spin degeneracy is broken.
+The entropy measurements yield $\Delta S_{0 \rightarrow 1}=(0.93 \pm 0.02) k_B \ln{2}$ and $\Delta S_{2 \rightarrow 3}=(0.98 \pm 0.01) k_B \ln{2}$ at zero magnetic field, collapsing to zero at high field where spin degeneracy is broken.
 At a qualitative level, Figs.~\ref{fig:fig3}b and c show $\delta g_{sens}$ crossover from asymmetric to antisymmetric as $\Delta S$ goes to zero at high field.
-Using $T_{res} = \SI{130}{\milli\kelvin}$, midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T$) points of the temperature oscillation, yields $g=-0.39$ and $g=-0.40$ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
-These are consistent with $g=-0.44$ expected for GaAs and measured via bias spectroscopy in Fig.~\ref{fig:fig3}e.
+Choosing $T$ to be midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T_{RMS}$) points of the temperature oscillation for each data set, yields $g=-0.39 \pm 0.01 $ and $g=-0.45 \pm 0.01 $ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
+These are consistent with previous few electron dot measurements and the value measured separately in Fig.~\ref{fig:fig3}e using bias spectroscopy \cite{Cronenwett1998,Hanson2003,Zumbuhl2004}.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_4.pdf}
-        \caption{\label{fig:fig4}(c) Change in entropy, extracted from $\delta g_{sens}$ fits at varying parallel field.
-Dashed line shows fit to Eq.~\ref{eqn:gibbs} (b), (c), and (d) show characteristic $\delta g_{sens}$ traces from which the data in (c) were extracted.
-These data points are show as large markers in (c).
+        \caption{\label{fig:fig4}(a) Change in entropy, extracted from $\delta g_{sens}$ fits at varying parallel field.
+Dashed line shows fit to Eq.~\ref{eqn:gibbs}.
+Values stated for $\Delta S$ are with respect to the vertical offset apparent in the data.
+(b), (c), and (d) show characteristic $\delta g_{sens}$ traces from which the data in (a) were extracted.
+These data points are show as large markers in (a).
 (e) Bias spectroscopy data for the $N=1 \rightarrow 2$ transition.
-Singlet-triplet splitting is \SI{316}{\micro\electronvolt}.
+Transitions to the 2-electron triplet state correspond to the lines appearing at $V_{SD} = \SI{\pm 320}{\micro\electronvolt}$.
 Dashed line at $V_{SD}$ = \SI{1250}{\micro\electronvolt} shows where data in (f) are taken.
 (f) Fixed bias data in parallel field.
-Triplet level is split into $T_+$, $T_0$, and $T_{-}$ (not visible).
-At \SI[input-protect-tokens]{\sim 9}{\tesla} $T_+$ becomes degenerate with $S$.
-$g=-0.40$ is determined using $T_0$ and $T_+$ fits (dashed).}
+Triplet level is split into $T_+$ and $T_0$ levels with a third $T_{-}$ level not visible here.
+At \SI[input-protect-tokens]{9}{\tesla} $T_+$ becomes degenerate with $S$.
+$g=-0.40\pm0.04$ is determined using $T_0$ and $T_+$ fits (dashed).}
 \end{figure}
@@
 The fit allows for an offset from $\Delta S=0$, away from the degenerate points, to compensate for non-linearities in the charge sensor.
-From the fit we find the entropies at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are again within 5\% of the expected values, $\mp k_B \ln{2}$.
-The extracted value of $g = 0.39$ from the low-field peak agrees well with the fit in Fig.~\ref{fig:fig3}a.
-At the high-field singlet-triplet degeneracy we find $g = 0.59$.
+From the fit we find $\Delta S$ at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are $-(1.01\pm0.02) k_B \ln{2}$ and $(1.043 \pm 0.02) k_B \ln{2}$, respectively.
+The extracted value of $g = 0.37 \pm 0.01$ from the low-field peak agrees well with the fit in Fig.~\ref{fig:fig3}a.
+At the high-field singlet-triplet degeneracy we find $g = 0.55 \pm 0.02$.
 This unexpectedly high g-factor can be explained by a shifting of the $T_{0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work \cite{Szafran2004}.
@@
 
-\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.
+\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second} respectively.
 Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability to the device.
 Fine gate structures, including the \SI{200}{\nano\metre} diameter quantum dots, were defined by electron beam lithography and deposition of \SI{20}{\nano\metre} Ti/Au.
-The measurement was carried out in an dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.
+The measurement was carried out in a dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.
 
-The conductance of the charge sensor was measured at a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.
-The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + \delta T$) using AC or DC current biased through the left (heater) QPC, which was gate-tuned to \SI{20}{\kilo\ohm}.
+The conductance of the charge sensor was measured using a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.
+The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + \delta T$) using AC or DC current biased through the heater QPC, which was gate-tuned to \SI{20}{\kilo\ohm}.
 A calibration for $\delta T$ in this mode, using DC current bias $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
-Applying AC current at $f_{Heat} =$ \SI{48.7}{\hertz} yields oscillations in $T_{res}$ at $2f_{heat}$; to leading order $\delta T_{res} \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$.
+Applying AC current at $f_{heat} =$ \SI{48.7}{\hertz} yields oscillations in $T$ at $2f_{heat}$; to leading order $\delta T \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$.
 Variations in $g_{sens}$ with $\delta T$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
@@
 The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
-The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T_{res}$ up to \SI{250}{\milli\kelvin}.
-Measurements of $\Delta S$ are made at $\delta T_{res} = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
+The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T$ up to \SI{250}{\milli\kelvin}.
+Measurements of $\Delta S$ are made at $\delta T \sim $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
 
@@
 \end{document}
+
+%%% old sentences %%%
+
+%Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}.
+A more direct test for the two-channel Kondo state would be a confirmation of its entropy ($\frac{1}{2} k_B \ln{2}$), that should remain down to arbitrarily low temperatures \cite{Alkurtass2016}.
+
+%Entropy can be probed effectively in 3D macroscopic samples via measurements of heat capacity, but the heat capacities of single electrons or quasiparticles are much too small to measure directly; even the 2D sheet of quasiparticles in $\nu = \frac{5}{2}$ fractional quantum Hall samples has a heat capacity that vanishes in comparison to that of the host crystal.
+Rather than attempt to resolve such infinitesimal signals, the problem can be avoided by converting changes in entropy to changes in charge \textemdash a quantity that is easily detected at the single particle level.
+
+%Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states investigated here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
+
+%This shift, $\delta \mu$ as a function of $\delta T$, is the quantity probed directly in the experiment described below.
+From these measurements the entropies of the first three quantum dot levels are built up, demonstrating a direct entropy measurement is possible on a few-particle system.
+In the future, the method can be utilized to probe the nature of more exotic systems, such as topologically non-trivial Majorana and other non-Abelian states.
+
+%Consider the filling of the first electron state, which has a single, unpaired spin-$\frac{1}{2}$ and, therefore, a degeneracy of 2.
+
+%One expects identical field-dependent behaviors for $\Delta S_{0\rightarrow 1}$ and $\Delta S_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies
+
+%The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} follows the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
+The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T$ up to \SI{250}{\milli\kelvin}.
+Measurements of $\Delta S$ are made at $\delta T = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
+
+%Although the extracted $\epsilon$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $\delta g_{sens}$ without any additional calibration, and without knowing the precise value of $\delta T$.

### 2018-02-23 data_tools.py

@@ -303,7 +303,29 @@ def i_sense_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, 
                           
     return df
 
-def di_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, fix = None, span = None):
+def di_fit_simultaneous(x, z, centers, widths, x0bounds, 
+                        constrain = None, fix = None, span = None, 
+                        nboot=None, bootstat='bounds'):
+    
+    def di_bootstrap_eps(mboot, xx, zz, fit_params, jlow, jhigh, pp0, bbounds):
+        """ bootstrap estimate of errors on epsilon for single curve fit 
+            Following this: http://www.phas.ubc.ca/~oser/p509/Lec_20.pdf """
+        
+        # create zfit and resid, both of which have shape=z.shape
+        zfit = di_sense_simple(xx, *fit_params)
+        resid = zz - zfit
+        
+        boot_results = np.zeros((mboot,len(fit_params)))
+        for k in range(mboot):
+            ztest = zfit + np.random.choice(resid.flatten(), size=zfit.shape)
+            out, _ = curve_fit(di_sense_simple, xx[jlow:jhigh], 
+                                ztest[jlow:jhigh], p0=pp0, bounds=bbounds)
+            boot_results[k] = out
+        
+        if bootstat=='bounds':
+            return np.percentile(boot_results[:,-1], [2.5, 97.5])
+        elif bootstat=='std':
+            return np.array([boot_results[:,-1].std(), boot_results[:,-1].std()])
     
     def di_dataset(params, i, xx):
         
@@ -368,8 +390,11 @@ def di_fit_simultaneous(x, z, centers, widths, x0bounds, constrain = None, fix =
             fit_params.add('x0_{0:d}'.format(i), value=centers[i], min=x0bounds[0], max=x0bounds[1])
             fit_params.add('theta_{0:d}'.format(i), value=widths[i], min=0.05, max=10.0)
             fit_params.add('di0_{0:d}'.format(i), 
-                               value=0.5*max(abs(z[i,ilow[i]:ihigh[i]].min()), abs(z[i,ilow[i]:ihigh[i]].max())), min=0.0, max=0.5)
-            fit_params.add('di2_{0:d}'.format(i), value=(z[i,ilow[i]]+z[i,ihigh[i]])/2.0, min=-0.01, max=0.01)
[…]

### 2018-02-23 paper/draft.tex
text updates

@@
 For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, could be clearly distinguished from the Abelian case by an entropy measurement \cite{Cooper2009, Smirnov2015}.
-Such measurements are typically based on bulk properties, like heat capacity, that are straightforward to observe in macroscopic samples but difficult to access in mesoscopic systems that may consist of only a few electrons.
-Here, we develop a mesoscopic circuit to make a direct entropy measurement on the first, second, and third electron occupations in a GaAs quantum dot.
+Such measurements are typically based on bulk properties, like heat capacity, that are clearly observed in macroscopic samples but are immeasurably small in systems that may consist of only a few electrons.
+Here, we develop a mesoscopic circuit to make direct entropy measurements of the first, second, and third electron ground states in a GaAs quantum dot.
 This system is chosen for having well-known entropy based on simple spin states\cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-The precision of this technique, quantifying the entropy of a single spin-$\frac{1}{2}$ to within 5\% of the expected value ($k_B \ln{2}$), shows its future potential for probing more exotic systems, from Majorana states to non-Fermi liquid Kondo states, that are clearly identified by a residual low-temperature entropy\cite{Alkurtass2016}.}
+The precision of this technique, quantifying the entropy of a single spin-$\frac{1}{2}$ to within 5\% of the expected value ($k_B \ln{2}$), shows its future potential for probing more exotic systems, from Majorana states to non-Fermi liquid Kondo states, that are clearly identified by their residual low-temperature entropy\cite{Alkurtass2016}.}
 
@@
 
-Our approach is analogous to the milestone of spin-to-charge conversion achieved over a decade ago, by which unmeasurably-small magnetic moments of a single spin were detected indirectly by transforming into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
-Instead, we perform an entropy-to-charge conversion, making use of the Maxwell relation
+Our approach is analogous to the milestone of spin-to-charge conversion achieved over a decade ago, in which the infinitesimal magnetic moments of a single spin were detected by transforming them into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
+Following this logic, we perform an entropy-to-charge conversion, making use of the Maxwell relation
 %
@@
 
-The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to measure non-Abelian exchange of quasiparticles in the the $\nu = \frac{5}{2}$ state, by detecting changes in the quasiparticle chemical potential with temperature, which are proportional to the entropy derivative, $\frac{\partial S}{\partial N}$ \cite{Cooper2009,Ben-Shach2013}.
-Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured through the shift with temperature in the electrochemical potential, $\mu_N$, needed to add the $N$th electron to the dot; the gate voltage at which the $N-1$ to $N$ transition is observed shifts linearly with $\mu_{N}$.
+The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to measure non-Abelian exchange of quasiparticles in the the $\nu = \frac{5}{2}$ state, by detecting a change in quasiparticle chemical potential with temperature, which is proportional to the entropy derivative, $\frac{\partial S}{\partial N}$ \cite{Cooper2009,Ben-Shach2013}.
+Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured through the shift with temperature in the electrochemical potential, $\mu_N$, needed to add the $N$th electron to the dot; the gate voltage at which the $N-1$ to $N$ transition is observed is  proportional to $\mu_{N}$.
 
@@
 The reservoir temperature, $T$, could be rapidly (up to at least \SI{100}{\hertz}) increased above the mixing chamber temperature, $T_{MC}$, by Joule heating through the QPC (``heater") on the left side.
-The occupation of the dot was measured using an adjacent quantum point contact (``charge sensor")\cite{Staring2007, Thierschmann2015} [change these references/add additional].
+The occupation of the dot was measured using an adjacent quantum point contact (``charge sensor") \cite{Field1993, Staring2007, Thierschmann2015} [change these references/add additional].
 Applying a more positive voltage to the gate adds the $N$th electron to the dot when $\mu_{N}$ drops below the Fermi level of the reservoir, $E_F$.
-Figure 1b illustrates such a transition \textemdash a step in the charge sensor conductance \textemdash thermally broadened by the reservoir temperature.
+Figure~\ref{fig:fig1}b illustrates such a transition \textemdash seen as a step in the charge sensor conductance \textemdash that is thermally broadened by the reservoir temperature.
 The gate voltage corresponding to the midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ or $N$ electrons on the dot are equal.
-When $\mu_N$ shifts with temperature, $V_{mid}$ also shifts (Fig.~1c); it is this signature that forms the basis of our experiment.
+When $\mu_N$ shifts with temperature, $V_{mid}$ also shifts (Fig.~\ref{fig:fig1}c); it is the measurement of this signature that forms the basis of our experiment.
 
-The relation between entropy and any temperature-induced shift in $\mu_{N}$ with respect to $E_F$ can also be understood in the language of detailed balance.
-The $N$th electron tunnels back and forth between an $N-1$-electron dot and reservoir when there are available states in both the dot and reservoir, that is, when $\mu_{N}$ is within thermal broadening of $E_F$.
+The relation between entropy and any temperature-induced shift in $\mu_{N}$ with respect to $E_F$ can be understood through detailed balance.
+The $N$th electron tunnels back and forth between an $N-1$-electron dot and reservoir when there are available states in both the dot and reservoir, that is, when $\mu_{N}$ is within thermal broadening ($\sim k_B T$) of $E_F$.
 The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$, depend on degeneracy of the $N-1$ and $N$ ground states.
-Consider, for example, the first electron tunneling into an empty dot: both spin-up and -down states are available.
+Consider, for example, the first electron tunneling into an empty dot: both spin-up and -down states are available on the dot.
 Tunneling out, the electron (whether spin-up or -down) must tunnel into reservoir states with the same spin, that is, only half of the empty reservoir states are available.
 As a result, $\Gamma_{in} = 2\Gamma_{out}$ when $\mu_{N}=E_F$.
-Extending this logic to a general case gives the result derived from detailed balance \cite{Gustavsson2009, Beenakker1991},
+Extending this logic to a general case gives the result derived from detailed balance \cite{Beenakker1991, Gustavsson2009},
 %
@@
 
-The equal probability condition for $N-1/N$ at $V_{mid}$ corresponds to  incoming and outgoing rates being equal.
-From Eq.~\ref{eqn:rates}$, \Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N} = E_F$ as long as $g_{N-1}=g_{N}$, but to $\mu_{N} > E_F$ when $g_{N-1} > g_{N}$ and vice versa.
-The ratio $g_{N}/g_{N-1}$ is given by the shift in $V_{mid}$ with temperature, giving $\Delta S_{N-1\rightarrow N}$ via the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
+The equal probability condition for $N-1$- and $N$-electrons at $V_{mid}$ corresponds to the incoming and outgoing rates being equal.
+From Eq.~\ref{eqn:rates}$, \Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N} = E_F$ only in the case $g_{N-1}=g_{N}$, but to $\mu_{N} > E_F$ when $g_{N-1} > g_{N}$ and to $\mu_{N} < E_F$ when $g_{N-1} < g_{N}$.
+The ratio $g_{N}/g_{N-1}$ is given by the shift in $V_{mid}$ ($\propto \mu_{N}$) with temperature, giving $\Delta S_{N-1\rightarrow N}$ via the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
 Previous works have explored the relationship between tunnel rates and degeneracy using time-resolved transport spectroscopy and coupling of quantum dots to atomic force microscope oscillations \cite{Cockins2010, Bennett2010, Beckel2014, Hofmann2016}.
 The approach presented here illustrates the thermodynamic equivalent of the rate measurement, and extends entropy measurements to a wide set of applications where tunneling processes may not be possible to observe in real-time.
+
+%%%%%%%%%%
 
@@
 
-To proceed with the entropy measurement, the quantum dot (Fig.~\ref{fig:fig1}a) was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
-The conductance of the charge sensor was tuned to $g_{sens}{\sim}e^2/h$ where it was most sensitive to charge on the dot.
+To proceed with the entropy measurement, the quantum dot was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
+The conductance of the charge sensor was tuned to $g_{sens}{\sim}e^2/h$, where it was most sensitive to charge on the dot.
 The addition of the first electron to the dot was marked by a decrease in $g_{sens}$ that is well fit by the expected form for a thermally-broadened transition:
@@
 %
-where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha$ is the lever arm $\alpha\equiv\partial \mu_{N}/\partial V_G$, and $G_1$ reflects the cross capacitance between the charge sensor and plunger gate.
+where $G_0$ represents the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening (expressed in units of gate voltage), $\alpha\equiv d \mu_{N}/d V_G$ is the lever arm, and $G_1$ reflects the cross capacitance between the charge sensor and plunger gate.
 Fig.~\ref{fig:fig2}a shows two such transition curves with the high temperature curve being thermally broadened by driving a current, $I_{heat}$ through the QPC heater.
@@
 
-The data in Fig.~\ref{fig:fig2}c, and corresponding fits, offer an example of how $\Delta S_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ transition.
+The data in Fig.~\ref{fig:fig2}c, and corresponding fits, offer an example of how $\Delta S_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ electron transition.
 A comparison of the curves in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as temperature rises immediately before the midpoint of the transition ($V_G-V_{mid}<0$), whereas $g_{sens}$ rises with temperature for $V_G-V_{mid}>0$.
-Oscillating the reservoir temperature by $\delta T$ using an AC current through the heater while measuring oscillations in the charge sensor signal, $\delta g_{sens}$, with a lock in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
-The expected lineshape of such a curve is given by the derivative of Eq.~\ref{eqn:g} with respect to temperature, expressed as $\delta g_{sens}$ due to a temperature change $\delta T$:
+Oscillating the reservoir temperature by $\delta T$ using an AC current through the heater while measuring oscillations in the charge sensor signal, $\delta g_{sens}$, with a lock-in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
+The expected lineshape of such a curve is given by $\delta g = \frac{\partial g}{\partial T} \delta T$, where $g(V;T)$ is defined by Eq.~\ref{eqn:g} and $\delta T$ is determined by the RMS value of $I_{heat}$:
 %
@@
 %
+% 
+%
 \begin{align}
@@
 From Eqs.~\ref{eqn:dg} and \ref{eqn:epsilon}, $\delta g_{sens}(V_G)$ would be perfectly antisymmetric around $V_{mid}$ if $\Delta S_{N-1\rightarrow N}$ were zero, whereas the data in Fig.~\ref{fig:fig2}c are clearly not antisymmetric.
-A best fit to Eqs.~\ref{eqn:dg} and \ref{eqn:epsilon} yields $\Delta S_{0\rightarrow 1}=0.72 \pm 0.01 k_B$, close to what would be expected for the $0 \rightarrow 1$ electron transition at zero magnetic field: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate one-electron state one expects $S_1=k_B\ln{2}$, giving $\Delta S_{0\rightarrow 1}\equiv S_1 - S_0 =k_B\ln{2}$.
+A best fit to Eqs.~\ref{eqn:dg} and \ref{eqn:epsilon} yields $\Delta S_{0\rightarrow 1}=(1.02 \pm 0.01) k_B \ln{2}$.
+For the $0 \rightarrow 1$ electron transition at zero magnetic field, one expects the following: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate 1-electron state one expects $S_1=k_B\ln{2}$, giving $\Delta S_{0\rightarrow 1}\equiv S_1 - S_0 =k_B\ln{2}$, matching the very well with the measured value.
 
-Fig.~\ref{fig:fig2}e shows that $\Delta S$,  determined from fits to data analogous to Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T$ (I$_{heat}$ AC).
-To confirm the measurement lies within the the relevant limits, the magnitude of the temperature change, $\delta T$ is calibrated in Fig.~\ref{fig:fig2}d and the corresponding shift in $V_{mid}$ is plotted long the right side of Fig.~\ref{fig:fig2}e.
-However, it is important to note that the change in entropy, $\Delta S$, is determined from the fit parameter, $\epsilon$, with no further calibration.
+Figure~\ref{fig:fig2}e shows that $\Delta S$, determined from fits analogous to those in Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T$ ($I_{heat}$ AC).
+The calibration for $\delta T$ with respect to $I_{heat}$ is shown in Figure~\ref{fig:fig2}d; a DC heater current was applied and fits to \label{eqn:g} yield $\delta T$ through $\Theta$; the calibration holds for AC currents when referring to the RMS value of $I_{heat}$ AC, as we do throughout this discussion.
+An important point is illustrated in Figure~\ref{fig:fig2}e; the change in entropy, $\Delta S$, is determined entirely by the fit parameter, $\epsilon$, with no further calibration necessary.
 
@@
         \caption{\label{fig:fig3}(a) Changes in entropy for $N=0 \rightarrow 1$ and $2 \rightarrow 3$ transitions, overlaid to highlight similar behaviors.
-Each datapoint corresponds to a fit to a single $\delta g_{sens}(V_G)$ trace; multiple scans are carried out at various parallel magnetic fields.
+Each data point corresponds to a single $\delta g_{sens}(V_G)$ fit; multiple scans are carried out at various parallel magnetic fields.
 (b) and (c) Characteristic $\delta g_{sens}$ traces from which the data in (a) were extracted.
@@
 
-Confirmation that the measured $\Delta S$ derives from spin degeneracy can be seen in its evolution with in-plane magnetic field, $B_\parallel$.
-Figure \ref{fig:fig3}a compares $\Delta S(B_\parallel)$ for the 0-1 and 2-3 electron transitions.
+Confirmation that the measured $\Delta S$ derives from spin degeneracy can be seen through its evolution with in-plane magnetic field, $B_\parallel$.
+Figure \ref{fig:fig3}a compares $\Delta S(B_\parallel)$ for the $0 \rightarrow1 $ and $2 \rightarrow 3$ electron transitions.
 The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $\Delta S_{0 \rightarrow 1}$ and $\Delta S_{2 \rightarrow 3}$ are expected to correspond to transitions from total spin zero to total spin one-half.
@@
 where $p_{\pm}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_{\parallel}}{k_B T}})^{-1}$ are the probabilities for the unpaired electron to be in the spin up/down states at a given field and temperature.
-Fits to Eq.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, with the ration $g/T$ and an added scaling $\Delta S(B=0)$ as free parameters.
+Fits to Eq.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, with the ratio $g/T$ and an added scaling $\Delta S(B=0)$ as free parameters.
 
@@
 At a qualitative level, Figs.~\ref{fig:fig3}b and c show $\delta g_{sens}$ crossover from asymmetric to antisymmetric as $\Delta S$ goes to zero at high field.
-Choosing $T$ to be midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T_{RMS}$) points of the temperature oscillation for each data set, yields $g=-0.39 \pm 0.01 $ and $g=-0.45 \pm 0.01 $ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
+Choosing $T$ to be midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T_{RMS}$) points of the temperature oscillation for each data set yields $g=-0.39 \pm 0.01 $ and $g=-0.45 \pm 0.01 $ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
 These are consistent with previous few electron dot measurements and the value measured separately in Fig.~\ref{fig:fig3}e using bias spectroscopy \cite{Cronenwett1998,Hanson2003,Zumbuhl2004}.
@@
 (f) Fixed bias data in parallel field.
-Triplet level is split into $T_+$ and $T_0$ levels with a third $T_{-}$ level not visible here.
-At \SI[input-protect-tokens]{9}{\tesla} $T_+$ becomes degenerate with $S$.
-$g=-0.40\pm0.04$ is determined using $T_0$ and $T_+$ fits (dashed).}
+Triplet level is split into $\mathit{T_+}$ and $\mathit{T_0}$ levels with a third $\mathit{T_-}$ level not visible here.
+At \SI[input-protect-tokens]{9}{\tesla} $\mathit{T_+}$ becomes degenerate with $\mathit{S}$.
+$g=-0.40\pm0.04$ is determined using $\mathit{T_0}$ and $\mathit{T_+}$ fits (dashed).}
 \end{figure}
@@
 The $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}a) can be understood as the inverse of Fig \ref{fig:fig3}a for $B_\parallel < \SI{5}{\tesla}$.
-There, the 2-electron ground state remains a spin singlet ($S_2=0$) while the 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
-At higher field, the 1-electron ground state remains non-degenerate ($S_1=0$) while the 2-electron ground state becomes two-fold degenerate where the spin singlet ($S$) and triplet ($T_+$) states cross.
+There, the 2-electron ground state remains a spin singlet ($\mathit{S_2}=0$) while the 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
+At higher field, the 1-electron ground state remains non-degenerate ($\mathit{S_1}=0$) while the 2-electron ground state becomes two-fold degenerate where the spin singlet ($\mathit{S}$) and triplet ($\mathit{T_+}$) states cross.
 The singlet-triplet crossing is seen clearly around at \SI{9}{\tesla} in bias spectroscopy data for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}e).
@@
 The fit allows for an offset from $\Delta S=0$, away from the degenerate points, to compensate for non-linearities in the charge sensor.
-From the fit we find $\Delta S$ at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are $-(1.01\pm0.02) k_B \ln{2}$ and $(1.043 \pm 0.02) k_B \ln{2}$, respectively.
-The extracted value of $g = 0.37 \pm 0.01$ from the low-field peak agrees well with the fit in Fig.~\ref{fig:fig3}a.
+From this we find $\Delta S$ at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are $-(1.01\pm0.02) k_B \ln{2}$ and $(1.043 \pm 0.02) k_B \ln{2}$, respectively.
+The extracted value of $g = 0.37 \pm 0.01$ from the low-field peak agrees well with the expected value and the bias spectroscopy data in Fig.~\ref{fig:fig4}e.
 At the high-field singlet-triplet degeneracy we find $g = 0.55 \pm 0.02$.
-This unexpectedly high g-factor can be explained by a shifting of the $T_{0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work \cite{Szafran2004}.
+This unexpectedly high g-factor can be explained by a shifting of the $\mathit{T_0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work \cite{Szafran2004}.
 The high quality of the Gibbs entropy fit confirms $\Delta S$ and illustrates a tunable degeneracy in the system.
@@
 In conclusion, we show that the entropy of few-particle states in mesoscopic devices can be measured directly.
-Using the well-understood spin degeneracy of  few-electron ground states states in a GaAs quantum dot for calibration, the entropy can be quantified within 5\% of the expected $\pm k_B\ln{2}$.
-Future work may take advantage of this strategy to look for thermodynamic signatures of non-trival electron and quasiparticle states, eliminating the uncertainty found in typical transport data.
+Looking at the well-understood spin degeneracy of  few-electron ground states states in a GaAs quantum dot for calibration, the entropy can be quantified within 5\% of the expected $\pm k_B\ln{2}$.
+Future work may take advantage of this strategy to search for thermodynamic signatures of non-trival electron and quasiparticle states, eliminating the uncertainty found in typical transport data.
 
-\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second} respectively.
+\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined in a separate chip/measurement) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second} respectively.
 Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability to the device.
@@
 
-The conductance of the charge sensor was measured using a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.
-The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + \delta T$) using AC or DC current biased through the heater QPC, which was gate-tuned to \SI{20}{\kilo\ohm}.
-A calibration for $\delta T$ in this mode, using DC current bias $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c.
+The conductance of the charge sensor was measured using a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lock-in amplifier.
+The temperature of the reservoir could be raised above $T_{MC}$ using AC or DC current biased through the heater QPC, which was gate-tuned to \SI{20}{\kilo\ohm}.
 Applying AC current at $f_{heat} =$ \SI{48.7}{\hertz} yields oscillations in $T$ at $2f_{heat}$; to leading order $\delta T \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$.
-Variations in $g_{sens}$ with $\delta T$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
+Variations in $g_{sens}$ with $\delta T$ are captured with a lock-in amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
 

### 2018-03-02 paper/draft.tex
cleaning up
mostly text edits. few small figure changes.

@@
+% manfra comments:
+%         didn't understand how the measurement was done. thought we were measuring Vmid and seeing it shift.  
+%         wanted to know more about how this technique would actually be implemented to realize one of the more exciting proposals.
+
+% mohammad comments:
+% 	    Figure 2 -- (c) make more clear how delta T was obtained
+%         make more clear how the 5/2 measurement relates to what was done here
+%         gate-tuned -- change this phrase in the methods
+%         I_heat looks like it shorts the sample in Figure 1a
+%         Nature Methods -- suggestion for journal
+
 \documentclass[twocolumn,showpacs,amsmath,amssymb,prl,aps,superscriptaddress]{revtex4-1}
@@
 \usepackage{hyperref}
+
+\newcommand{\ket}[1]{\ensuremath{\left|#1\right\rangle}}
 
@@
 \author{Saeed Fallahi}
-	\affiliation{Department of Physics and Astronomy, Purdue University}
-	\affiliation{Station Q Purdue, Purdue University}
+	\affiliation{Department of Physics and Astronomy, Purdue University, West Lafayette, Indiana, USA}
+	\affiliation{Station Q Purdue, Purdue University, West Lafayette, Indiana, USA}
 	\affiliation{Birck Nanotechnology Center, Purdue University, West Lafayette, Indiana, USA}
 \author{Geoffrey C. Gardner}
-	\affiliation{Station Q Purdue, Purdue University}
+	\affiliation{Station Q Purdue, Purdue University, West Lafayette, Indiana, USA}
 	\affiliation{Birck Nanotechnology Center, Purdue University, West Lafayette, Indiana, USA}
@@
 \author{Michael Manfra}
-	\affiliation{Department of Physics and Astronomy, Purdue University}
-	\affiliation{Station Q Purdue, Purdue University}
+	\affiliation{Department of Physics and Astronomy, Purdue University, West Lafayette, Indiana, USA}
+	\affiliation{Station Q Purdue, Purdue University, West Lafayette, Indiana, USA}
 	\affiliation{Birck Nanotechnology Center, Purdue University, West Lafayette, Indiana, USA}
@@
 
-%\begin{abstract}
-%
-%Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
-Such measurements are typically based on bulk properties, such as heat capacity, that are straightforward to observe in macroscopic samples but exceedingly difficult to access in mesoscopic systems that may consist of just a few electrons.
-Taking advantage of a well-known Maxwell relation, we realize a protocol for entropy-to-charge conversation in a gate-defined GaAs quantum dot that enables an entropy measurement of the first three quantum states in to the dot.
-The entropy of a single spin ($k_B \ln{2}$) is measured within 8\% accuracy, as is the entropy arising at the magnetic field-driven singlet-triplet crossing for two electrons.
-%
-%\end{abstract}
-
 \maketitle
@@
 Systems that are difficult to clearly identify through standard conductance measurements may be characterized more precisely with a thermodynamic measurement.
-For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, could be clearly distinguished from the Abelian case by an entropy measurement \cite{Cooper2009, Smirnov2015}.
-Such measurements are typically based on bulk properties, like heat capacity, that are clearly observed in macroscopic samples but are immeasurably small in systems that may consist of only a few electrons.
-Here, we develop a mesoscopic circuit to make direct entropy measurements of the first, second, and third electron ground states in a GaAs quantum dot.
+For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, could be clearly distinguished from the Abelian case by an entropy measurement \cite{Cooper2009, Ben-Shach2013, Smirnov2015}.
+Such measurements are typically based on bulk properties, like heat capacity, that are easily observed in macroscopic samples but are immeasurably small in systems that may consist of only a few electrons.
+Here, we develop a mesoscopic circuit to make direct entropy measurements of single- or few-quasiparticle states---in this case, the first, second, and third electron ground states in a GaAs quantum dot.
 This system is chosen for having well-known entropy based on simple spin states\cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_1_annotated.pdf}
-        \caption{\label{fig:fig1}(a) Scanning electron micrograph of a device similar to the one measured, showing electrostatic gates (gold) used to define a circuit in a 2D electron gas (2DEG).
-Grey gates are grounded.
-Squares show the locations of ohmic contacts to the 2DEG.
-An electron reservoir is formed between the parallel gates running vertically down the image, with a quantum dot coupled to the right side.
-The reservoir can be heated by driving current through the quantum point contact on the left.
-Electrons tunneling between the reservoir and dot are measured with a capacitively-coupled charge sensor.
-(b) and (c) Simulated charge sensor signal for a transition from $N-1 \rightarrow N$ electrons at two temperatures ($T_{Red} > T_{Blue}$), showing two possible cases for $\frac{\partial S}{\partial N}$.}
+        \caption{\label{fig:fig1} \textbf{Entropy measurement protocol.}  (a) Scanning electron micrograph of a device similar to the one measured.
+Electrostatic gates (gold) define the circuit in a 2D electron gas (2DEG), with grey gates grounded.
+Squares indicate ohmic contacts to the 2DEG.
+The temperature of the electron reservoir in the middle (red) is oscillated using AC current, $I_{heat}$, at frequency $f_{heat}$ through the quantum point contact (QPC) on the left.
+A portion of the $5~\mu$m-wide reservoir has been removed here for clarity.
+The occupation of the quantum dot, tunnel coupled to the right side the reservoir, is tuned by $V_p$ and monitored by $I_{sens}$ through the charge sensor QPC.
+$I_{sens}$ is split into DC and AC components, the latter being measured by a lock-in amplifier at $2f_{heat}$.
+(b) and (c) Simulated DC charge sensor signal, $G_{sens}$, for a transition from $N-1 \rightarrow N$ electrons at two temperatures ($T_{Red} > T_{Blue}$), showing two possible cases for $\frac{\partial S}{\partial N}$.
+Insets show the corresponding difference, $\delta G_{sens}$, between hot and cold curves.}
 \end{figure}
@@
 
-The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to measure non-Abelian exchange of quasiparticles in the the $\nu = \frac{5}{2}$ state, by detecting a change in quasiparticle chemical potential with temperature, which is proportional to the entropy derivative, $\frac{\partial S}{\partial N}$ \cite{Cooper2009,Ben-Shach2013}.
-Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured through the shift with temperature in the electrochemical potential, $\mu_N$, needed to add the $N$th electron to the dot; the gate voltage at which the $N-1$ to $N$ transition is observed is  proportional to $\mu_{N}$.
+The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to measure non-Abelian exchange of quasiparticles in  the $\nu = \frac{5}{2}$ state via their entropy
+%, quantified by the change in quasiparticle chemical potential with temperature
+\cite{Cooper2009,Ben-Shach2013}.
+Ref.~\onlinecite{Ben-Shach2013} proposes a strategy by which quasiparticle entropy could be deduced from the temperature-dependent shift of charging events on a local disorder potential, a thermodynamic equivalent of the measurements that established the $e/4$ quasiparticle charge\cite{Venkatachalam2011}.
+As a proof of principle in the viability of measuring localized quasiparticle entropy, and a demonstration of the high accuracy achievable by this technique, we investigate a well-understood system with localized fermions: a few-electron GaAs quantum dot.
+The entropies of the first three electron states in the dot are measured by the temperature-dependent charging scheme laid out in Ref.~\onlinecite{Ben-Shach2013}.
+Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ and $N$ electron ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured via the shift with temperature in the electrochemical potential, $\mu_N$, needed to add the $N$th electron to the dot.
 
-The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a uses electrostatic gates to realize an electron reservoir (central region; hereafter ``reservoir") in thermal and diffusive equilibrium with a few-electron quantum dot (``dot") coupled to its right side.
-The reservoir temperature, $T$, could be rapidly (up to at least \SI{100}{\hertz}) increased above the mixing chamber temperature, $T_{MC}$, by Joule heating through the QPC (``heater") on the left side.
-The occupation of the dot was measured using an adjacent quantum point contact (``charge sensor") \cite{Field1993, Staring2007, Thierschmann2015} [change these references/add additional].
-Applying a more positive voltage to the gate adds the $N$th electron to the dot when $\mu_{N}$ drops below the Fermi level of the reservoir, $E_F$.
-Figure~\ref{fig:fig1}b illustrates such a transition \textemdash seen as a step in the charge sensor conductance \textemdash that is thermally broadened by the reservoir temperature.
-The gate voltage corresponding to the midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ or $N$ electrons on the dot are equal.
-When $\mu_N$ shifts with temperature, $V_{mid}$ also shifts (Fig.~\ref{fig:fig1}c); it is the measurement of this signature that forms the basis of our experiment.
+The measurement relies on the mesoscopic circuit shown in Fig.~\ref{fig:fig1}a, using electrostatic gates to realize an electron reservoir (hereafter ``reservoir") in thermal and diffusive equilibrium with a few-electron quantum dot (``dot") coupled to its right side.
+The occupation of the dot is tuned with the plunger gate voltage, $V_p$, and measured using an adjacent quantum point contact (``charge sensor") \cite{Field1993, Staring2007, Thierschmann2015}.
+Applying more positive $V_p$ lowers $\mu_N$,  bringing the $N$th electron into the dot when $\mu_{N}$ drops below the Fermi level of the reservoir, $E_F$.
+The reservoir temperature, $T$, can be increased above the mixing chamber temperature, $T_{MC}$, by Joule heating from current $I_{heat}$ through the quantum point contact (``heater") on the left side.
+Charge transitions on the dot appear as steps in the charge sensor conductance, $G_{sens}(V_p)$, thermally broadened by the reservoir temperature (Figs.~\ref{fig:fig1}b and c).
+The gate voltage corresponding to the midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ and $N$ electrons on the dot are equal.
 
-The relation between entropy and any temperature-induced shift in $\mu_{N}$ with respect to $E_F$ can be understood through detailed balance.
-The $N$th electron tunnels back and forth between an $N-1$-electron dot and reservoir when there are available states in both the dot and reservoir, that is, when $\mu_{N}$ is within thermal broadening ($\sim k_B T$) of $E_F$.
-The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$, depend on degeneracy of the $N-1$ and $N$ ground states.
-Consider, for example, the first electron tunneling into an empty dot: both spin-up and -down states are available on the dot.
-Tunneling out, the electron (whether spin-up or -down) must tunnel into reservoir states with the same spin, that is, only half of the empty reservoir states are available.
-As a result, $\Gamma_{in} = 2\Gamma_{out}$ when $\mu_{N}=E_F$.
-Extending this logic to a general case gives the result derived from detailed balance \cite{Beenakker1991, Gustavsson2009},
-%
-\begin{align}
-	\Gamma_{in} &=  g_{N} \Gamma f(E_F - \mu_{N}) \nonumber \\
-	\Gamma_{out} &= g_{N-1} \Gamma [1 - f(E_F - \mu_{N})] \label{eqn:rates}
-\end{align}
-%
-where $\Gamma$ is a coupling constant, $f$ is the Fermi function, and $g_{N(N-1)}$ is the degeneracy of the $N(N-1)$ electron state.
+When $\mu_N$ shifts with temperature (Eq.~\ref{eqn:max}), $V_{mid}$ also shifts; it is the shift in $V_{mid}$ with temperature that forms the basis of our experiment (Fig.~\ref{fig:fig1}c).
+In practice, charge noise limits the accuracy to which $V_{mid}$ can be measured, so the measurement is done with a lock-in amplifier, oscillating the temperature using an AC $I_{heat}$ and measuring resultant oscillations in $G_{sens}$.
+As seen in the insets of Figs.~\ref{fig:fig1}b and c, the lineshape of $\delta G_{sens}$ is perfectly antisymmetric when $\partial S/\partial N=0$, but asymmetric when $\partial S/\partial N \neq 0$.
 
-The equal probability condition for $N-1$- and $N$-electrons at $V_{mid}$ corresponds to the incoming and outgoing rates being equal.
-From Eq.~\ref{eqn:rates}$, \Gamma_{in} = \Gamma_{out}$ corresponds to $\mu_{N} = E_F$ only in the case $g_{N-1}=g_{N}$, but to $\mu_{N} > E_F$ when $g_{N-1} > g_{N}$ and to $\mu_{N} < E_F$ when $g_{N-1} < g_{N}$.
-The ratio $g_{N}/g_{N-1}$ is given by the shift in $V_{mid}$ ($\propto \mu_{N}$) with temperature, giving $\Delta S_{N-1\rightarrow N}$ via the Boltzmann entropy, $S_{N}=k_{B} \ln{g_N}$.
-Previous works have explored the relationship between tunnel rates and degeneracy using time-resolved transport spectroscopy and coupling of quantum dots to atomic force microscope oscillations \cite{Cockins2010, Bennett2010, Beckel2014, Hofmann2016}.
-The approach presented here illustrates the thermodynamic equivalent of the rate measurement, and extends entropy measurements to a wide set of applications where tunneling processes may not be possible to observe in real-time.
-
-%%%%%%%%%%
+The temperature-induced shift in the dot chemical potential with respect to reservoir $E_F$ can also be understood in terms of detailed balance.
+At $V_{mid}$, with equal probabilities for $N$ and $N-1$ electrons on the dot, the tunnel rates $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$ must also be equal.
+These rates depend on the number of available states in the tunneling process, and therefore on the degeneracies of the $N-1$ and $N$ ground states \cite{Beenakker1991, Gustavsson2009}.
+The condition $\Gamma_{in} = \Gamma_{out}$ leads to a simple relationship between the degeneracies, $d_{N-1}$ and $d_{N}, of the $N-1$ and $N$ electron states and the thermally broadened Fermi function $f$: $d_{N-1}/d_{N}=f/(1-f)$.
+Using the Boltzman entropy, $S_{N}=k_{B} \ln{d_N}$, and the form of the Fermi function, this relationship becomes $\Delta S_{N-1\rightarrow N}= (\mu_{N}-E_F)/T$, clearly demonstrating the connection between entropy, temperature, and the shift in $\mu_N$ relative to $E_F$ at $V_{mid}$.
+Previous experiments have explored the relationship between tunnel rates and degeneracy using time-resolved transport spectroscopy and by coupling quantum dots to atomic force cantilever oscillations \cite{Cockins2010, Bennett2010, Beckel2014, Hofmann2016}.
+The approach presented here is a thermodynamic equivalent of these, and extends entropy measurements to a much wider set of applications where tunnelling processes may not be possible to observe in real-time.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_2.pdf}
-        \caption{\label{fig:fig2}(a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater.
+        \caption{\label{fig:fig2} \textbf{Entropy measurement for a single spin $\frac{1}{2}$.} (a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater.
 (b) Transition width, $\Theta$, was linear in $T_{MC}$ above 100 mK, for $I_{heat}=0$.
 Lever arm $\alpha$ is calculated by fitting a straight line to this region.
-(c) Lock-in measurement of $\delta g_{sens}$ with $\delta T = \SI{32}{\milli\kelvin}$.
-Fits to $\delta g_{sens}$ are shown with $\epsilon$ as a free parameter (solid) or fixed at $\epsilon=0$ (dashed)  (d) $\Theta$ grows with DC current through the QPC heater.
-A fit to $T = a\sqrt{T^{2}_{MC}+b I_{heat}R_{QPC}}$ is used to convert between $I_{heat}$ and $\delta T$, with $R_{QPC} = \SI{20}{\kilo\ohm}$ \cite{Mittal1996} (e)  Entropy measurements were independent of the magnitude of $I_{heat}$ oscillations.
-Top axis illustrates the corresponding magnitude of $\delta T$, while right axes shows the entropy signal converted to a gate voltage shift.}
+(c) Lock-in measurement of $\delta G_{sens}$ with $\delta T = \SI{32}{\milli\kelvin}$, determined from the calibration in panel (d).
+Fits to $\delta G_{sens}$ (Eq.~\ref{eqn:dg-sens}) are shown with $\Delta S / k_B$  as a free parameter (solid) and fixed at $\Delta S / k_B=0$ (dashed).
+(d) $\Theta$ grows with DC current through the QPC heater.
+A fit to $T = a\sqrt{T^{2}_{MC}+b I^2_{heat}R_{QPC}}$ is used to convert between $I_{heat}$ and $\delta T$\cite{Mittal1996}.
+(e)  Entropy measurements were independent of the magnitude of $I_{heat}$ oscillations over a large range.
+The top axis indicates the corresponding magnitude of $\delta T$, while the right axis shows the entropy signal converted to a gate voltage shift per unit temperature.}
 \end{figure}
 
-To proceed with the entropy measurement, the quantum dot was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
-The conductance of the charge sensor was tuned to $g_{sens}{\sim}e^2/h$, where it was most sensitive to charge on the dot.
-The addition of the first electron to the dot was marked by a decrease in $g_{sens}$ that is well fit by the expected form for a thermally-broadened transition:
+%To proceed with the entropy measurement,
+The dot was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
+The conductance of the charge sensor was tuned to $G_{sens}{\sim}e^2/h$, where it was most sensitive to charge on the dot.
+The addition of the first electron to the dot was marked by a decrease in $G_{sens}$ that is well described as a thermally-broadened two-level transition (Fig.~\ref{fig:fig2}a):
 %
 \begin{align}
-\label{eqn:g}
-        g_{sens}(V,\Theta) &= G_0 \tanh\left(\frac{V-V_{mid}(\Theta)}{2\Theta}\right)  \\
-                        &\quad + G_1\left[V-V_{mid}(\Theta)\right] + G_2 \nonumber
+\label{eqn:g-sens}
+        G_{sens}(V_p,\Theta) &= G_0 \tanh\left(\frac{V_p - V_{mid}(\Theta)}{2\Theta}\right)  \\
+                        &\quad + G_1 V_{G} + G_2 \nonumber
 \end{align}
 %
-where $G_0$ represents the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening (expressed in units of gate voltage), $\alpha\equiv d \mu_{N}/d V_G$ is the lever arm, and $G_1$ reflects the cross capacitance between the charge sensor and plunger gate.
-Fig.~\ref{fig:fig2}a shows two such transition curves with the high temperature curve being thermally broadened by driving a current, $I_{heat}$ through the QPC heater.
-With no Joule heating through the heater, $\Theta$ followed $T_{MC}$ down to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b), validating the approximation of thermal broadening used throughout this experiment.
+where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening (expressed in units of gate voltage), $\alpha\equiv d \mu_{N}/d V_p$ is the lever arm,  $G_1$ reflects the cross capacitance between the charge sensor and plunger gate, and $G_2$ is an offset.
+Figure~\ref{fig:fig2}a shows two such transition curves with thermal broadening set by the current, $I_{heat}$ through the heater.
+For $I_{heat}=0$, $\Theta$ followed $T_{MC}$ down to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b), validating the approximation of thermal broadening used throughout this experiment.
 
-The data in Fig.~\ref{fig:fig2}c, and corresponding fits, offer an example of how $\Delta S_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ electron transition.
-A comparison of the curves in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as temperature rises immediately before the midpoint of the transition ($V_G-V_{mid}<0$), whereas $g_{sens}$ rises with temperature for $V_G-V_{mid}>0$.
-Oscillating the reservoir temperature by $\delta T$ using an AC current through the heater while measuring oscillations in the charge sensor signal, $\delta g_{sens}$, with a lock-in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
-The expected lineshape of such a curve is given by $\delta g = \frac{\partial g}{\partial T} \delta T$, where $g(V;T)$ is defined by Eq.~\ref{eqn:g} and $\delta T$ is determined by the RMS value of $I_{heat}$:
+The data in Fig.~\ref{fig:fig2}c, and corresponding fits, illustrate a measurement of $\Delta S_{0\rightarrow 1}$ across the $0 \rightarrow 1$ electron transition.
+The lock-in measurement of $\delta G_{sens}$ due to temperature oscillations $\delta T$ yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c, corresponding the difference between the two $G_{sens}$ curves in Fig.~\ref{fig:fig2}a.
+The expected lineshape of such a curve is $\delta G_{sens} = \frac{\partial G_{sens}}{\partial T} \delta T$, with $G_{sens}$ defined by Eq.
+\ref{eqn:g-sens}.
+This lineshape depends in a simple way on $\Delta S$, recognizing (via Eq.~\ref{eqn:max}) that $\frac{\partial V_{mid}}{\partial \Theta}=\frac{1}{k_B}\frac{\partial \mu}{\partial T} =\frac{1}{k_B}\Delta S_{N-1\rightarrow N}$:
 %
 \begin{align}
-\label{eqn:dg}
-        \delta g_{sens}(V_G, \Theta) &\propto -\delta T \left[ \frac{V_G-V_{mid}(\Theta)}{2\Theta} + \frac{\epsilon}{2} \right]\times \\
-        				      &\quad\cosh^{-2}\left(\frac{V_G-V_{mid}(\Theta)}{2\Theta}\right) + const. \nonumber
-\end{align}
-%
-where $\epsilon=\frac{\partial V_{mid}}{\partial \Theta}$.
-Using the lever arm to convert $V_{mid}$ to electrochemical potential, $\epsilon$ is simply the change in entropy (scaled by $k_B$) through Eq.~\ref{eqn:max}:
-%
-% 
-%
-\begin{align}
-\label{eqn:epsilon}
-        \epsilon &= \frac{\partial V_{mid}}{\partial \Theta} = 
-        \frac{1}{k_B} \frac{\partial \mu}{\partial T} = 
-        -\frac{1}{k_B} \Delta S_{N-1\rightarrow N}
+\label{eqn:dg-sens}
+        \delta G_{sens}(V_p, \Theta) &\propto -\delta T \left[ \frac{V_p - V_{mid}(\Theta)}{2\Theta} - \frac{\Delta S}{2k_B} \right]\times \\
+        				      &\quad\cosh^{-2}\left(\frac{V_p - V_{mid}(\Theta)}{2\Theta}\right) + const. \nonumber
 \end{align}
@@
 
-From Eqs.~\ref{eqn:dg} and \ref{eqn:epsilon}, $\delta g_{sens}(V_G)$ would be perfectly antisymmetric around $V_{mid}$ if $\Delta S_{N-1\rightarrow N}$ were zero, whereas the data in Fig.~\ref{fig:fig2}c are clearly not antisymmetric.
-A best fit to Eqs.~\ref{eqn:dg} and \ref{eqn:epsilon} yields $\Delta S_{0\rightarrow 1}=(1.02 \pm 0.01) k_B \ln{2}$.
-For the $0 \rightarrow 1$ electron transition at zero magnetic field, one expects the following: $S_0$ for the empty state should be $k_B \ln{1}=0$ whereas for the spin degenerate 1-electron state one expects $S_1=k_B\ln{2}$, giving $\Delta S_{0\rightarrow 1}\equiv S_1 - S_0 =k_B\ln{2}$, matching the very well with the measured value.
+\noindent As expected  from Figs.~\ref{fig:fig1}b,c, $\delta G_{sens}(V_p)$ is antisymmetric around $V_{mid}$ for $\Delta S=0$, and asymmetric for $\Delta S\neq 0$.
+A fit of the data in Fig.~\ref{fig:fig2}c to Eq.~\ref{eqn:dg-sens} yields $\Delta S_{0\rightarrow 1}=(1.02 \pm 0.03) k_B \ln{2}$, closely matching the expected $\Delta S_{0 \rightarrow 1} = S_1 - S_0 =k_B\ln{2}$ for transitions between an empty dot ($S_0=0$) and the two-fold degenerate 1-electron state ($d_1=2$) with entropy $S_1=k_B \ln{2}$.
 
-Figure~\ref{fig:fig2}e shows that $\Delta S$, determined from fits analogous to those in Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T$ ($I_{heat}$ AC).
-The calibration for $\delta T$ with respect to $I_{heat}$ is shown in Figure~\ref{fig:fig2}d; a DC heater current was applied and fits to \label{eqn:g} yield $\delta T$ through $\Theta$; the calibration holds for AC currents when referring to the RMS value of $I_{heat}$ AC, as we do throughout this discussion.
-An important point is illustrated in Figure~\ref{fig:fig2}e; the change in entropy, $\Delta S$, is determined entirely by the fit parameter, $\epsilon$, with no further calibration necessary.
+It is important to note that extracting $\Delta S$ from fits to Eq.~\ref{eqn:dg-sens} can be done just from the asymmetry of the lineshape, with no calibration of measurement parameters (such as $\delta T$ or the lever arm $\alpha$) required.
+We can, however, estimate $\delta T$ and $\alpha$ by measuring $T(I_{heat})$, using a DC $I_{heat}$ to raise the reservoir temperature and fitting to Eq.~\ref{eqn:g-sens}  (Fig.~\ref{fig:fig2}d); the calibration holds for AC currents below 100 Hz.
+Measurements of $\Delta S$ remained constant over a broad range of $\delta T$ (Fig.~\ref{fig:fig2}e), as expected for temperatures low enough not to excite orbital degrees of freedom on the dot.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_3.pdf}
-        \caption{\label{fig:fig3}(a) Changes in entropy for $N=0 \rightarrow 1$ and $2 \rightarrow 3$ transitions, overlaid to highlight similar behaviors.
-Each data point corresponds to a single $\delta g_{sens}(V_G)$ fit; multiple scans are carried out at various parallel magnetic fields.
-(b) and (c) Characteristic $\delta g_{sens}$ traces from which the data in (a) were extracted.
+        \caption{\label{fig:fig3} \textbf{Magnetic field dependence.} (a) Changes in entropy for $N=0 \rightarrow 1$ and $2 \rightarrow 3$ transitions, overlaid to highlight similar behaviors.
+Each data point corresponds to a single $\delta G_{sens}(V_p)$ fit; multiple scans are carried out at various parallel magnetic fields.
+(b) and (c) Characteristic $\delta G_{sens}$ traces from which the data in (a) were extracted.
 The two data points corresponding to (b) and (c) are shown as large markers in (a).
@@
 
-Confirmation that the measured $\Delta S$ derives from spin degeneracy can be seen through its evolution with in-plane magnetic field, $B_\parallel$.
-Figure \ref{fig:fig3}a compares $\Delta S(B_\parallel)$ for the $0 \rightarrow1 $ and $2 \rightarrow 3$ electron transitions.
-The 2-electron ground state is a spin singlet, while the 3-electron ground state adds an additional unpaired electron, so both $\Delta S_{0 \rightarrow 1}$ and $\Delta S_{2 \rightarrow 3}$ are expected to correspond to transitions from total spin zero to total spin one-half.
-The entropies of the 1- and 3-electron states are suppressed when Zeeman splitting lifts the spin degeneracy of the unpaired electron.
-This behavior is described by the Gibbs entropy for a two-level system:
+Confirmation that the measured $\Delta S$ derives from spin degeneracy is seen through its evolution with in-plane magnetic field, $B_\parallel$.
+Figure \ref{fig:fig3}a compares $\Delta S(B_\parallel)$ for the $0 \rightarrow1 $ and $2 \rightarrow 3$ transitions, both of which correspond to transitions from total spin zero to total spin one-half.
+The entropies of the $\ket{S=1/2}$ states go to zero as when Zeeman splitting lifts the spin degeneracy, given by the Gibbs entropy for a two-level system:
 %
@@
 where $p_{\pm}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_{\parallel}}{k_B T}})^{-1}$ are the probabilities for the unpaired electron to be in the spin up/down states at a given field and temperature.
-Fits to Eq.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a for both transitions, with the ratio $g/T$ and an added scaling $\Delta S(B=0)$ as free parameters.
-
-The entropy measurements yield $\Delta S_{0 \rightarrow 1}=(0.93 \pm 0.02) k_B \ln{2}$ and $\Delta S_{2 \rightarrow 3}=(0.98 \pm 0.01) k_B \ln{2}$ at zero magnetic field, collapsing to zero at high field where spin degeneracy is broken.
-At a qualitative level, Figs.~\ref{fig:fig3}b and c show $\delta g_{sens}$ crossover from asymmetric to antisymmetric as $\Delta S$ goes to zero at high field.
-Choosing $T$ to be midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T_{RMS}$) points of the temperature oscillation for each data set yields $g=-0.39 \pm 0.01 $ and $g=-0.45 \pm 0.01 $ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
-These are consistent with previous few electron dot measurements and the value measured separately in Fig.~\ref{fig:fig3}e using bias spectroscopy \cite{Cronenwett1998,Hanson2003,Zumbuhl2004}.
+Fits to Eq.~\ref{eqn:gibbs}, with the ratio $g/T$ and an added scaling $\Delta S(B=0)$ as free parameters, give $\Delta S_{0 \rightarrow 1}(B=0)=(0.94 \pm 0.03) k_B \ln{2}$ and $\Delta S_{2 \rightarrow 3}(B=0)=(0.98 \pm 0.02) k_B \ln{2}$ (Fig.~\ref{fig:fig3}), and reflect the collapse to zero at high field where spin degeneracy is broken.
+This collapse can also be seen qualitatively, as a crossover from asymmetric to antisymmetric lineshapes for $\delta G_{sens}(V_p)$ (Figs.~\ref{fig:fig3}b and c).
+Estimating an average $T$ for each data set using the calibration in Fig.~\ref{fig:fig2}d yields $|g|=0.48 \pm 0.02$ and $|g|=0.44 \pm 0.01 $ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
+Errors in the g-factor measurement are likely due to the difficulty of estimating temperature oscillations.
+Still, the g-factors are consistent with reported values\cite{Cronenwett1998,Hanson2003,Zumbuhl2004} and the value measured separately in Fig.~\ref{fig:fig3}e using bias spectroscopy.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_4.pdf}
-        \caption{\label{fig:fig4}(a) Change in entropy, extracted from $\delta g_{sens}$ fits at varying parallel field.
+        \caption{\label{fig:fig4}  \textbf{Entropic signature of a singlet-triplet crossing.} (a) Change in entropy, extracted from $\delta G_{sens}$ fits at varying parallel field.
 Dashed line shows fit to Eq.~\ref{eqn:gibbs}.
 Values stated for $\Delta S$ are with respect to the vertical offset apparent in the data.
-(b), (c), and (d) show characteristic $\delta g_{sens}$ traces from which the data in (a) were extracted.
+(b), (c), and (d) show characteristic $\delta G_{sens}$ traces from which the data in (a) were extracted.
 These data points are show as large markers in (a).
@@
 (f) Fixed bias data in parallel field.
-Triplet level is split into $\mathit{T_+}$ and $\mathit{T_0}$ levels with a third $\mathit{T_-}$ level not visible here.
-At \SI[input-protect-tokens]{9}{\tesla} $\mathit{T_+}$ becomes degenerate with $\mathit{S}$.
-$g=-0.40\pm0.04$ is determined using $\mathit{T_0}$ and $\mathit{T_+}$ fits (dashed).}
+Triplet level is split into $\ket{T_+}$ and $\ket{T_0}$ levels with a third $\ket{T_-}$ level not visible here.
+At \SI{8.4}{\tesla} $\ket{T_+}$ becomes degenerate with $\ket{S}$.
+$g=-0.40\pm0.04$ is determined using $\ket{T_0}$ and $\ket{T_+}$ fits (dashed).}
 \end{figure}
 
-The $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}a) can be understood as the inverse of Fig \ref{fig:fig3}a for $B_\parallel < \SI{5}{\tesla}$.
-There, the 2-electron ground state remains a spin singlet ($\mathit{S_2}=0$) while the 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
-At higher field, the 1-electron ground state remains non-degenerate ($\mathit{S_1}=0$) while the 2-electron ground state becomes two-fold degenerate where the spin singlet ($\mathit{S}$) and triplet ($\mathit{T_+}$) states cross.
-The singlet-triplet crossing is seen clearly around at \SI{9}{\tesla} in bias spectroscopy data for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}e).
+The $1\rightarrow 2$ transition can be understood as the inverse of the $0 \rightarrow 1$ transition for $B_\parallel < \SI{5}{\tesla}$, comparing Figs~\ref{fig:fig3}a and \ref{fig:fig4}a.
+For relatively low fields, the 2-electron ground state remains a spin singlet ($\ket{S=0}$) with zero entropy, while the 1-electron entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
+At higher fields, the 1-electron ground state remains non-degenerate while the 2-electron ground state gains a two-fold degeneracy when the singlet and triplet \ket{T_+} states cross.
+This singlet-triplet crossing is seen in bias spectroscopy data (Fig.~\ref{fig:fig4}f) at \SI{8.4}{\tesla}, and in the appearance of a peak in $\Delta S_{1\rightarrow 2}$ at \SI{9}{\tesla}.
+The discrepancy between the fields required to drive the singlet-triplet degeneracy in Figs.~\ref{fig:fig4}a and f can be explained by the change in dot configuration from one to two open tunnel barriers.
 
-The field-dependent entropy measurement for the 1-2 transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{S/T}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
-The fit allows for an offset from $\Delta S=0$, away from the degenerate points, to compensate for non-linearities in the charge sensor.
-From this we find $\Delta S$ at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are $-(1.01\pm0.02) k_B \ln{2}$ and $(1.043 \pm 0.02) k_B \ln{2}$, respectively.
-The extracted value of $g = 0.37 \pm 0.01$ from the low-field peak agrees well with the expected value and the bias spectroscopy data in Fig.~\ref{fig:fig4}e.
-At the high-field singlet-triplet degeneracy we find $g = 0.55 \pm 0.02$.
-This unexpectedly high g-factor can be explained by a shifting of the $\mathit{T_0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work \cite{Szafran2004}.
-The high quality of the Gibbs entropy fit confirms $\Delta S$ and illustrates a tunable degeneracy in the system.
+The field-dependent entropy measurement for the $1 \rightarrow 2$ transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{\ket{S}/\ket{T}}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
+The fit in Fig.~\ref{fig:fig4}a allows for an offset from $\Delta S=0$ away from the degenerate points to compensate for non-linearities in the charge sensor.
+From the fit, we find $\Delta S_{1\rightarrow 2}$ at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are $-(1.01\pm0.03) k_B \ln{2}$ and $(1.04 \pm 0.04) k_B \ln{2}$, respectively.
+The extracted g-factor, $g = 0.47 \pm 0.02$, from the peak at $B=0$ is consistent with the $0\rightarrow 1$ transition.
+At the high-field singlet-triplet degeneracy we find $g = 0.69 \pm 0.04$, an unexpectedly high g-factor that may be explained by a shift of the $\ket{T_0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work \cite{Szafran2004}.
+The high quality of the Gibbs entropy fit, over a large range of field, confirms that the measured signal is the change in entropy $\Delta S$, and illustrates a tuneable degeneracy.
 
 %%% conclusion %%%
-In conclusion, we show that the entropy of few-particle states in mesoscopic devices can be measured directly.
-Looking at the well-understood spin degeneracy of  few-electron ground states states in a GaAs quantum dot for calibration, the entropy can be quantified within 5\% of the expected $\pm k_B\ln{2}$.
-Future work may take advantage of this strategy to search for thermodynamic signatures of non-trival electron and quasiparticle states, eliminating the uncertainty found in typical transport data.
+%In conclusion, we have presented a direct entropy measurement of the few-particle states in a few electron states in a GaAs was quantified within 5\% of the expected $k_B \ln{2}$.
+Future work may take advantage of this strategy to search for thermodynamic signatures of quantum states with non-trival correlations or topology, eliminating the uncertainty found in typical transport data.
 
 \paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined in a separate chip/measurement) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second} respectively.
-Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability to the device.
-Fine gate structures, including the \SI{200}{\nano\metre} diameter quantum dots, were defined by electron beam lithography and deposition of \SI{20}{\nano\metre} Ti/Au.
-The measurement was carried out in a dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.
+Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability in the device.
+Fine gate structures, shown in Fig.~\ref{fig:fig1}a, were defined by electron beam lithography and deposition of \SI{3/18}{\nano\metre} Ti/Au.
 
-The conductance of the charge sensor was measured using a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lock-in amplifier.
-The temperature of the reservoir could be raised above $T_{MC}$ using AC or DC current biased through the heater QPC, which was gate-tuned to \SI{20}{\kilo\ohm}.
-Applying AC current at $f_{heat} =$ \SI{48.7}{\hertz} yields oscillations in $T$ at $2f_{heat}$; to leading order $\delta T \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$.
-Variations in $g_{sens}$ with $\delta T$ are captured with a lock-in amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
+The measurement was carried out in a dilution refrigerator with a two-axis magnet.
+The 2DEG was aligned parallel to the main axis with the second axis used to compensate for sample misalignment.
+In practice, perpendicular fields up to \SI{100}{\milli\tesla} showed no effect on our data.
+[ADD DESCRIPTION OF THE CHANGE OF CONFIGURATION FOR BIAS SPECTROSCOPY, AND DETAILS OF SETTINGS FOR ENTROPY MEASUREMENT]  Charge sensor conductance was measured using a DC voltage bias of \SI{200}{\micro\volt}, with the current, measured at DC ($I_{sens}$) using an analog-digital convertor and at AC ($\delta I_{sens}$) using a lock-in amplifier.
+The DC conductance reported here is $G_{sens}=I_{sens}/V_{sens}$ while $\delta G_{sens}$ is $G_{sens}=(\delta I_{sens})/V_{sens}$.
 
-The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
+The temperature of the reservoir could be raised above $T_{MC}$ using $I_{heat}$ at AC or DC, with the heater set by gate voltages to \SI{20}{\kilo\ohm}.
+Applying AC current at $f_{heat} =$ \SI{48.7}{\hertz} yields an oscillating Joule power, $P_{heat} = I^2_{heat}R_{QPC}$.
+To leading order this gives oscillations in temperature, and therefore $\delta G_{sens}$, at $2f_{heat}$.
+These are  captured by the lock-in amplifier at the second harmonic of $I_{heat}$.
+Except where noted, measurements of $\Delta S$ were made at $\delta T \sim $ \SI{50}{\milli\kelvin}, although the error bars in Fig.~\ref{fig:fig2} demonstrate that the measurements would have been just as accurate with $\delta T$ set to \SI{30}{\milli\kelvin}.
+
+%The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g-sens} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
 The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T$ up to \SI{250}{\milli\kelvin}.
-Measurements of $\Delta S$ are made at $\delta T \sim $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
 
-%\acknowledgments
+\acknowledgments
+The authors acknowledge John Martinis for a helpful discussion on the interpretation of our measurements.
 
@@
 \end{document}
+
+%%% old abstract %%%
+
+%\begin{abstract}
+%
+%Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.
+Such measurements are typically based on bulk properties, such as heat capacity, that are straightforward to observe in macroscopic samples but exceedingly difficult to access in mesoscopic systems that may consist of just a few electrons.
+Taking advantage of a well-known Maxwell relation, we realize a protocol for entropy-to-charge conversation in a gate-defined GaAs quantum dot that enables an entropy measurement of the first three quantum states in to the dot.
+The entropy of a single spin ($k_B \ln{2}$) is measured within 8\% accuracy, as is the entropy arising at the magnetic field-driven singlet-triplet crossing for two electrons.
+%
+%\end{abstract}
 
@@
 
-%Although the extracted $\epsilon$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $\delta g_{sens}$ without any additional calibration, and without knowing the precise value of $\delta T$.
+%Although the extracted $\Delta S / k_B$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $\delta G_{sens}$ without any additional calibration, and without knowing the precise value of $\delta T$.
+
+%
+% \begin{align}
+% \label{eqn:epsilon}
+%         \epsilon &= \frac{\partial V_{mid}}{\partial \Theta} = 
+%         \frac{1}{k_B} \frac{\partial \mu}{\partial T} = 
+%         -\frac{1}{k_B} \Delta S_{N-1\rightarrow N}
+% \end{align}
+%
+
+%A comparison of the curves in Fig.~\ref{fig:fig2}a shows that $G_{sens}$ drops as temperature rises immediately before the midpoint of the transition ($V_p-V_{mid}<0$), whereas $G_{sens}$ rises with temperature for $V_p-V_{mid}>0$.
+
+% The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$, depend on the number of available states in the tunneling process, and therefore on the degeneracies of the $N-1$ and $N$ ground states\cite{Beenakker1991, Gustavsson2009}.
+Looking specifically at the ratio of those rates:
+%
+% \begin{equation}
+% 	\frac{\Gamma_{in}}{\Gamma_{out}} =  \frac{g_{N}}{g_{N-1}} \frac{f(E_F - \mu_{N})}{1-f(E_F - \mu_{N})} \label{eqn:rates}
+% \end{equation}
+%
+% where $f$ is the Fermi function and $g_{N(N-1)}$ is the degeneracy of the $N(N-1)$ electron state.
+The equal probability condition for $N-1$ and $N$ electrons at $V_{mid}$ corresponds to the incoming and outgoing rates being equal, giving $g_{N-1}/g_{N}=f/(1-f)$.

### 2018-03-02 paper/draft_j.tex
mostly text edits. few small figure changes.

% make text changes noted throughout text

% go through the whole thing once for clarity

% manfra comments:
%         didn?t understand how the measurement was done. thought we were measuring Vmid and seeing it shift.  
%         wanted to know more about how this technique would actually be implemented to realize one of the more exciting proposals.

% mohammad comments:
% 	    Figure 2 -- (c) make more clear how delta T was obtained (d) consider changing delta T to T
%         make more clear how the 5/2 measurement relates to what was done here
%         gate-tuned -- change this phrase in the methods
%         I_heat looks like it shorts the sample in Figure 1a
%         Nature Methods -- suggestion for journal

% consider plotting equation 2 as insets in top right of Figures 1b and 1c-- if we need to
% less discussion of rates -- move to a supplement?

\documentclass[twocolumn,showpacs,amsmath,amssymb,prl,aps,superscriptaddress]{revtex4-1}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{hyperref}

\newcommand{\ket}[1]{\ensuremath{\left|#1\right\rangle}}

\begin{document}

\title{Direct Entropy Measurement in a Mesoscopic Quantum System}
\author{Nikolaus Hartman}
\email{nik.hartman@gmail.com}
\thanks{The raw data and Python code used for all figures and analysis can be found at \url{https://github.com/nikhartman/spin_entropy}}
	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
\author{Christian Olsen}
	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
\author{Silvia Folk}
	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
\author{Mohammad Samani}
	\altaffiliation{The Hospital for Sick Children, Toronto, ON, Canada}
	\altaffiliation{Fields Institute for Research in Mathematical Sciences, Toronto, ON, Canada}
	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
\author{Saeed Fallahi}
	\affiliation{Department of Physics and Astronomy, Purdue University}
	\affiliation{Station Q Purdue, Purdue University}
	\affiliation{Birck Nanotechnology Center, Purdue University, West Lafayette, Indiana, USA}
\author{Geoffrey C. Gardner}
	\affiliation{Station Q Purdue, Purdue University}
	\affiliation{Birck Nanotechnology Center, Purdue University, West Lafayette, Indiana, USA}
    	\affiliation{School of Materials Engineering, Purdue University, West Lafayette, Indiana, USA}
\author{Michael Manfra}
	\affiliation{Department of Physics and Astronomy, Purdue University}
	\affiliation{Station Q Purdue, Purdue University}
	\affiliation{Birck Nanotechnology Center, Purdue University, West Lafayette, Indiana, USA}
	\affiliation{School of Electrical and Computer Engineering,  Purdue University, West Lafayette, Indiana, USA}
    	\affiliation{School of Materials Engineering, Purdue University, West Lafayette, Indiana, USA}
\author{Joshua Folk}
\email{jfolk@physics.ubc.ca}
	\affiliation{Stewart Blusson Quantum Matter Institute, University of British Columbia, Vancouver, British Columbia, V6T1Z4, Canada}
	\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver, British Columbia, V6T1Z1, Canada}
\date{\today}

\maketitle

%%%%%%% intro material %%%%%%%%%
\textbf{The thermodynamic properties of electronic systems offer important insights into the nature of their ground states, and can probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.  Systems that are difficult to clearly identify through standard conductance measurements may be characterized more precisely with a thermodynamic measurement. For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, could be clearly distinguished from the Abelian case by an entropy measurement \cite{Cooper2009, Smirnov2015}.  Such measurements are typically based on bulk properties, like heat capacity, that are clearly observed in macroscopic samples but are immeasurably small in systems that may consist of only a few electrons.  Here, we develop a mesoscopic circuit to make direct entropy measurements of the first, second, and third electron ground states in a GaAs quantum dot.  This system is chosen for having well-known entropy based on simple spin states\cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.  The precision of this technique, quantifying the entropy of a single spin-$\frac{1}{2}$ to within 5\% of the expected value ($k_B \ln{2}$), shows its future potential for probing more exotic systems, from Majorana states to non-Fermi liquid Kondo states, that are clearly identified by their residual low-temperature entropy\cite{Alkurtass2016}.}

%%% figure 1 %%%
\begin{figure}[!]
        \includegraphics[width=1.0\columnwidth]{../figures/figure_1_annotated.pdf}
        \caption{\label{fig:fig1}(a) Scanning electron micrograph of a device similar to the one measured, showing electrostatic gates (gold) used to define a circuit in a 2D electron gas (2DEG). Grey gates are grounded. Squares show the locations of ohmic contacts to the 2DEG. An electron reservoir is formed between the parallel gates running vertically down the image, with a quantum dot coupled to the right side. The reservoir can be heated by driving current through the quantum point contact on the left.  Electrons tunneling between the reservoir and dot are measured with a capacitively-coupled charge sensor. (b) and (c) Simulated charge sensor signal for a transition from $N-1 \rightarrow N$ electrons at two temperatures ($T_{Red} > T_{Blue}$), showing two possible cases for $\frac{\partial S}{\partial N}$.}
\end{figure}

Our approach is analogous to the milestone of spin-to-charge conversion achieved over a decade ago, in which the infinitesimal magnetic moments of a single spin were detected by transforming them into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.  Following this logic, we perform an entropy-to-charge conversion, making use of the Maxwell relation
%
\begin{align}
\label{eqn:max}
        \left(\frac{\partial \mu}{\partial T}\right)_{p,N} &= -\left(\frac{\partial S}{\partial N}\right)_{p,T}
\end{align}
%
that connects changes in entropy, particle number, and temperature ($S$, $N$, and $T$, respectively) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control. The fixed pressure condition of Eq.~\ref{eqn:max} is met by working well below the Fermi temperature of the 2DEG, $T_F \sim \SI{5}{\kelvin}$, where degeneracy pressure dominates \cite{Landau1969}.

The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to measure non-Abelian exchange of quasiparticles in the the $\nu = \frac{5}{2}$ state, by detecting a change in quasiparticle chemical potential with temperature, which is proportional to the entropy derivative, $\frac{\partial S}{\partial N}$ \cite{Cooper2009,Ben-Shach2013}. Applying the language of quantum dots to Eq.~\ref{eqn:max}, the entropy difference between the $N-1$ to $N$ quantum dot ground states ($\Delta S_{N-1\rightarrow N}$ for $\Delta N=1$) is measured via the shift with temperature in the electrochemical potential, $\mu_N$, needed to add the $N$th electron to the dot.

The mesoscopic circuit shown in Fig.~\ref{fig:fig1}a uses electrostatic gates to realize an electron reservoir (central region; hereafter ``reservoir") in thermal and diffusive equilibrium with a few-electron quantum dot (``dot") coupled to its right side.  The occupation of the dot is tuned with the plunger gate voltage $V_G$, and measured using an adjacent quantum point contact (``charge sensor") \cite{Field1993, Staring2007, Thierschmann2015}.  Applying more positive $V_G$ lowers $\mu_N$, and brings the $N$th electron into the dot when $\mu_{N}$ drops below the Fermi level of the reservoir, $E_F$. The reservoir temperature, $T$, can be increased above the mixing chamber temperature, $T_{MC}$, by Joule heating through the QPC (``heater") on the left side.  Figure~\ref{fig:fig1}b illustrates a charge transition on the dot, seen as a step in the charge sensor conductance as a function of $V_G$ that is thermally broadened by the reservoir temperature.  The gate voltage corresponding to the midpoint of the transition, $V_{mid}$, marks the electrochemical potential at which the probabilities of finding $N-1$ and $N$ electrons on the dot are equal.

When $\mu_N$ shifts with temperature (Eq.~\ref{eqn:max}), $V_{mid}$ also shifts; it is this shift $V_{mid}$ with temperature that forms the basis of our experiment (Fig.~\ref{fig:fig1}c).  In practice, charge noise limits the accuracy to which $V_{mid}$ can be measured, so the measurement is done with a lockin amplifier, oscillating the temperature and measuring resultant changes in the charge sensor conductance.  As seen from the grey shaded regions of Figs.~\ref{fig:fig1}b,c, this change is perfectly antisymmetric when $\partial S/\partial N=0$, but asymmetric when $\partial S/\partial N \neq 0$.

The relation between entropy and the temperature-induced shift in $\mu_{N}$ with respect to $E_F$ can be understood through detailed balance.  The tunnel rates into and out of the dot, $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$, depend on the number of available states in the tunneling process, and therefore on the degeneracies of the $N-1$ and $N$ ground states\cite{Beenakker1991, Gustavsson2009}.  Looking specifically at the ratio of those rates: 
%
\begin{equation}
	\frac{\Gamma_{in}}{\Gamma_{out}} =  \frac{g_{N}}{g_{N-1}} \frac{f(E_F - \mu_{N})}{1-f(E_F - \mu_{N})} \label{eqn:rates}
\end{equation}
%
where $f$ is the Fermi function and $g_{N(N-1)}$ is the degeneracy of the $N(N-1)$ electron state.  The equal probability condition for $N-1$ and $N$ electrons at $V_{mid}$ corresponds to the incoming and outgoing rates being equal, giving $g_{N-1}/g_{N}=f/(1-f)$. From the Boltzman entropy equation, $S_{N}=k_{B} \ln{g_N}$, and the form of the Fermi function, one finds $\Delta S_{N-1\rightarrow N}=e^{(\mu_{N}-E_F)/kT}$ at $V_{mid}$. It is straightforward to see from this relation that, when $\Delta S_{N-1\rightarrow N} \neq 0$, $\mu_N$ at $V_{mid}$ will shift relative to $E_F$ by an amount that is proportional to $T$. Previous experiments have explored the relationship between tunnel rates and degeneracy using time-resolved transport spectroscopy and coupling of quantum dots to atomic force microscope oscillations \cite{Cockins2010, Bennett2010, Beckel2014, Hofmann2016}. The approach presented here illustrates the thermodynamic equivalent of the rate measurement, and extends entropy measurements to a wide set of applications where tunneling processes may not be possible to observe in real-time.

%%% figure 2 %%%
\begin{figure}[!]
        \includegraphics[width=1.0\columnwidth]{../figures/figure_2.pdf}
        \caption{\label{fig:fig2}(a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater. (b) Transition width, $\Theta$, was linear in $T_{MC}$ above 100 mK, for $I_{heat}=0$. Lever arm $\alpha$ is calculated by fitting a straight line to this region.  (c) Lock-in measurement of $\delta g_{sens}$ with $\delta T = \SI{32}{\milli\kelvin}$. Fits to $\delta g_{sens}$ (Eq.~\ref{eqn:dg-sens}) are shown with $\epsilon=-\Delta S / k_B$  (Eq.\ref{eqn:epsilon}) as a free parameter (solid) or fixed at $\epsilon=0$ (dashed)  (d) $\Theta$ grows with DC current through the QPC heater. A fit to $T = a\sqrt{T^{2}_{MC}+b I^2_{heat}R_{QPC}}$ is used to convert between $I_{heat}$ and $\delta T$ \cite{Mittal1996} (e)  Entropy measurements were independent of the magnitude of $I_{heat}$ oscillations. Top axis illustrates the corresponding magnitude of $\delta T$, while right axes shows the entropy signal converted to a gate voltage shift.}
\end{figure}

To proceed with the entropy measurement, the dot was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.  The conductance of the charge sensor was tuned to $g_{sens}{\sim}e^2/h$, where it was most sensitive to charge on the dot.  The addition of the first electron to the dot was marked by a decrease in $g_{sens}$ that is well fit by the form for a thermally-broadened two-level transition (Fig.~\ref{fig:fig2}a):
%
\begin{align}
\label{eqn:g-sens}
        g_{sens}(V,\Theta) &= G_0 \tanh\left(\frac{V-V_{mid}(\Theta)}{2\Theta}\right)  \\
                        &\quad + G_1\left[V-V_{mid}(\Theta)\right] + G_2 \nonumber
\end{align}
%
where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening (expressed in units of gate voltage), $\alpha\equiv d \mu_{N}/d V_G$ is the lever arm, and $G_1$ reflects the cross capacitance between the charge sensor and plunger gate. Figure~\ref{fig:fig2}a shows two such transition curves with thermal broadening determined by the current, $I_{heat}$ through the heater. With no Joule heating through the heater, $\Theta$ followed $T_{MC}$ down to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b), validating the approximation of thermal broadening used throughout this experiment.

The data in Fig.~\ref{fig:fig2}c, and corresponding fits, illustrate an example of how $\Delta S_{0\rightarrow 1}$ was measured across the $0 \rightarrow 1$ electron transition.  A comparison of the curves in Fig.~\ref{fig:fig2}a shows that $g_{sens}$ drops as temperature rises immediately before the midpoint of the transition ($V_G-V_{mid}<0$), whereas $g_{sens}$ rises with temperature for $V_G-V_{mid}>0$.   Oscillating the reservoir temperature by $\delta T$ using an AC current through the heater while measuring oscillations in the charge sensor signal, $\delta g_{sens}$, with a lock-in amplifier (see Methods) yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c. The expected lineshape of such a curve is given by $\delta g_{sens} = \frac{\partial g_{sens}}{\partial T} \delta T$, where $g_{sens}$ is defined by Eq. \ref{eqn:g-sens}:
%
\begin{align}
\label{eqn:dg-sens}
        \delta g_{sens}(V_G, \Theta) &\propto -\delta T \left[ \frac{V_G-V_{mid}(\Theta)}{2\Theta} + \frac{\epsilon}{2} \right]\times \\
        				      &\quad\cosh^{-2}\left(\frac{V_G-V_{mid}(\Theta)}{2\Theta}\right) + const. \nonumber
\end{align}
%
where $\epsilon=\frac{\partial V_{mid}}{\partial \Theta}$. Using the lever arm to convert $V_{mid}$ to electrochemical potential, $\epsilon$ is simply the change in entropy (scaled by $k_B$) through Eq.~\ref{eqn:max}:
%
\begin{align}
\label{eqn:epsilon}
        \epsilon &= \frac{\partial V_{mid}}{\partial \Theta} = 
        \frac{1}{k_B} \frac{\partial \mu}{\partial T} = 
        -\frac{1}{k_B} \Delta S_{N-1\rightarrow N}
\end{align}
%
From Eqs.~\ref{eqn:dg-sens} and \ref{eqn:epsilon}, $\delta g_{sens}(V_G)$ would be perfectly antisymmetric around $V_{mid}$ if $\Delta S_{N-1\rightarrow N}$ were zero, whereas the data in Fig.~\ref{fig:fig2}c are clearly not antisymmetric. A best fit to Eqs.~\ref{eqn:dg-sens} and \ref{eqn:epsilon} yields $\Delta S_{0\rightarrow 1}=(1.02 \pm 0.03) k_B \ln{2}$. For the $0 \rightarrow 1$ electron transition, at zero magnetic field, $g_0=1$ giving $S_0=k_B \ln{1}=0$ and $g_1=2$ so $S_1=k_B \ln{2}$, giving $\Delta S_{0 \rightarrow 1} = S_1 - S_0 =k_B\ln{2}$.

Figure~\ref{fig:fig2}e shows that $\Delta S$, determined from fits analogous to those in Fig.~\ref{fig:fig2}c, remains constant over a range of $\delta T$ ($I_{heat}$ AC). The calibration for $\delta T$ with respect to $I_{heat}$ is shown in Fig.~\ref{fig:fig2}d; a DC heater current was applied and fits to Eq.~\ref{eqn:g-sens} yield $\delta T$ through $\Theta$; the calibration holds for AC currents when referring to the RMS value of $I_{heat}$ AC, as we do throughout this discussion. The parameter $\epsilon$ is entirely determined by the asymmetry of $\delta g$ as a function of $V_G$, as seen in Eqs.~\ref{eqn:dg-sens} and \ref{eqn:epsilon}, ad no further calibration is necessary for the entropy measurement. Figure~\ref{fig:fig2} shows that, as long as $\delta T$ is small enough to not excite any orbital levels on the dot, the measured entropy is independent of $T$.

%%% figure 3 %%%
\begin{figure}
        \includegraphics[width=1.0\columnwidth]{../figures/figure_3.pdf}
        \caption{\label{fig:fig3}(a) Changes in entropy for $N=0 \rightarrow 1$ and $2 \rightarrow 3$ transitions, overlaid to highlight similar behaviors.  Each data point corresponds to a single $\delta g_{sens}(V_G)$ fit; multiple scans are carried out at various parallel magnetic fields.   (b) and (c) Characteristic $\delta g_{sens}$ traces from which the data in (a) were extracted. The two data points corresponding to (b) and (c) are shown as large markers in (a). (e) Bias spectroscopy data for the $N=0 \rightarrow 1$ transition. Dashed line at $V_{SD}$ = \SI{700}{\micro\electronvolt} shows where data in (f) are taken. (f) Fixed bias data showing fits to Zeeman splitting of the ground state (dashed lines) from which $g = -0.42 \pm 0.01$ is extracted.}
\end{figure}

Confirmation that the measured $\Delta S$ derives from spin degeneracy can be seen through its evolution with in-plane magnetic field, $B_\parallel$. Figure \ref{fig:fig3}a compares $\Delta S(B_\parallel)$ for the $0 \rightarrow1 $ and $2 \rightarrow 3$, both of which correspond to transitions from total spin zero to total spin one-half. The entropies of the $\ket{S=1/2}$ states are suppressed when Zeeman splitting lifts the spin degeneracy. This behavior is described by the Gibbs entropy for a two-level system:
%
\begin{align}
\label{eqn:gibbs}
        S &= k_B \sum_{i=\pm} p_{i}(B_\parallel, T) \ln{ p_{i}(B_\parallel,T) }
\end{align}
%
where $p_{\pm}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_{\parallel}}{k_B T}})^{-1}$ are the probabilities for the unpaired electron to be in the spin up/down states at a given field and temperature. Fits to Eq.~\ref{eqn:gibbs} are shown in Fig.~\ref{fig:fig3}a, with the ratio $g/T$ and an added scaling $\Delta S(B=0)$ as free parameters.

%%% changes in here %%%
The entropy measurements yield $\Delta S_{0 \rightarrow 1}=(0.94 \pm 0.03) k_B \ln{2}$ and $\Delta S_{2 \rightarrow 3}=(0.98 \pm 0.02) k_B \ln{2}$ at zero magnetic field, collapsing to zero at high field where spin degeneracy is broken.

% discuss below why g may be wrong due to inaccuracies in T measurement, but that this in no way affects the entropy measurement, which is our focus
Choosing $T$ to be midway between the low ($T_{MC}$) and high ($T_{MC}+\delta T$) points of the temperature oscillation for each data set yields $g=-0.48 \pm 0.02$ and $g=-0.44 \pm 0.01 $ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively. These are consistent with previous few electron dot measurements and the value measured separately in Fig.~\ref{fig:fig3}e using bias spectroscopy \cite{Cronenwett1998,Hanson2003,Zumbuhl2004}.

% move some discussion from figure 3 caption down to here emphasize what you can see from just a quick look at the curves in figs b and c
At a qualitative level, Figs.~\ref{fig:fig3}b and c show $\delta g_{sens}$ crossover from asymmetric to antisymmetric as $\Delta S$ goes to zero at high field.
%%%%%%%%%%%%%%%

%%% figure 4 %%%
\begin{figure}
        \includegraphics[width=1.0\columnwidth]{../figures/figure_4.pdf}
        \caption{\label{fig:fig4}(a) Change in entropy, extracted from $\delta g_{sens}$ fits at varying parallel field. Dashed line shows fit to Eq.~\ref{eqn:gibbs}. Values stated for $\Delta S$ are with respect to the vertical offset apparent in the data. (b), (c), and (d) show characteristic $\delta g_{sens}$ traces from which the data in (a) were extracted. These data points are show as large markers in (a). (e) Bias spectroscopy data for the $N=1 \rightarrow 2$ transition. Transitions to the 2-electron triplet state correspond to the lines appearing at $V_{SD} = \SI{\pm 320}{\micro\electronvolt}$. Dashed line at $V_{SD}$ = \SI{1250}{\micro\electronvolt} shows where data in (f) are taken. (f) Fixed bias data in parallel field. Triplet level is split into $\ket{T_+}$ and $\ket{T_0}$ levels with a third $\ket{T_-}$ level not visible here. At \SI{8.4}{\tesla} $\ket{T_+}$ becomes degenerate with $\ket{S}$. $g=-0.40\pm0.04$ is determined using $\ket{T_0}$ and $\ket{T_+}$ fits (dashed).}
\end{figure}

%%%%%%%%%%%%%
The $1\rightarrow 2$ transition can be understood as the inverse of the $0 \rightarrow 1$ transition aor $B_\parallel < \SI{5}{\tesla}$ (comparing Figs~\ref{fig:fig3}a and \ref{fig:fig4}a).

% clear this up and make more reference to entropy
There, the 2-electron ground state remains a spin singlet $\ket{S_2=0}$ while the 1-electron ground state entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting. 
At higher field, the 1-electron ground state remains non-degenerate $\ket{S_1=0}$ while the 2-electron ground state becomes two-fold degenerate where the spin singlet $\ket{S}$ and triplet $\ket{T_+}$ states cross.

The singlet-triplet crossing is seen clearly at \SI{8.4}{\tesla} in bias spectroscopy data for the $1\rightarrow 2$ transition (Fig.~\ref{fig:fig4}f). 
%%%%%%%%%%%%%%

The field-dependent entropy measurement for the 1-2 transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{S/T}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field. The fit allows for an offset from $\Delta S=0$, away from the degenerate points, to compensate for non-linearities in the charge sensor. From this we find $\Delta S$ at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are $-(1.01\pm0.03) k_B \ln{2}$ and $(1.04 \pm 0.04) k_B \ln{2}$, respectively. % The discrepancy between the ST degenerate points in 4a and 4f can be explained by the change in dot configuration from one to two open tunnel barriers.
The extracted value of $g = 0.47 \pm 0.02$ from the low-field peak agrees well with the expected value and the bias spectroscopy data in Fig.~\ref{fig:fig4}f. At the high-field singlet-triplet degeneracy we find $g = 0.69 \pm 0.04$. This unexpectedly high g-factor can be explained by a shifting of the $\ket{T_0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work \cite{Szafran2004}. 
%%%%%
The high quality of the Gibbs entropy fit, over a large range of field, confirms the measured signal is the change in entropy $\Delta S$, as described above, and illustrates a tunable degeneracy in the system.
%%%%%

%%% conclusion %%%
In conclusion, have presented a direct entropy measurement of the few-particle states in mesoscopic devices can be measured directly. The spin entropy of the well understood few electron states in a GaAs was quantified within 5\% of the expected $k_B \ln{2}$.  Future work may take advantage of this strategy to search for thermodynamic signatures of quantum states with non-trival correlations or topology, eliminating the uncertainty found in typical transport data.

\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined in a separate chip/measurement) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second} respectively.   Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability in the device. Fine gate structures, shown in Fig.~\ref{fig:fig1}a, were defined by electron beam lithography and deposition of \SI{3/18}{\nano\metre} Ti/Au.

The measurement was carried out in a dilution refrigerator with a two-axis magnet. The sample was aligned parallel to the main axis. and the second axis could be used to compensate for sample misalignment. In practice, perpendicular fields up to \SI{100}{\milli\tesla} showed no affect on our results. The conductance of the charge sensor was measured using a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lock-in amplifier.  The temperature of the reservoir could be raised above $T_{MC}$ using AC or DC current biased through the heater QPC, which was gate-tuned to \SI{20}{\kilo\ohm}. Applying AC current at $f_{heat} =$ \SI{48.7}{\hertz} yields an oscillating Joule power, $P_{heat} = I^2_{heat}R_{QPC}$. To leading order this gives oscillations in temperature, and therefore $g_{sens}$, at $2f_{heat}$ which are captured with a lock-in amplifier. Measurements of $\Delta S$ are made at $\delta T \sim $ \SI{60}{\milli\kelvin}.

The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g-sens} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b). The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T$ up to \SI{250}{\milli\kelvin}.

\acknowledgments
The authors would like to acknowledge John Martinis for a helpful discussion on the interpretation of our measurements.

\bibliography{qdentropy}{}
\bibliographystyle{apsrev4-1}

\end{document}

%%% old abstract %%%

%\begin{abstract}
%
%Measuring the entropy of an electronic state is a powerful tool for identifying its underlying microscopic character.  Such measurements are typically based on bulk properties, such as heat capacity, that are straightforward to observe in macroscopic samples but exceedingly difficult to access in mesoscopic systems that may consist of just a few electrons. Taking advantage of a well-known Maxwell relation, we realize a protocol for entropy-to-charge conversation in a gate-defined GaAs quantum dot that enables an entropy measurement of the first three quantum states in to the dot. The entropy of a single spin ($k_B \ln{2}$) is measured within 8\% accuracy, as is the entropy arising at the magnetic field-driven singlet-triplet crossing for two electrons.
%
%\end{abstract}

%%% old sentences %%%

%Similarly, the two-channel Kondo state that is believed to arise in carefully tuned GaAs devices has so far been identified through a particular temperature dependence in the device conductance \cite{Potok2007}. A more direct test for the two-channel Kondo state would be a confirmation of its entropy ($\frac{1}{2} k_B \ln{2}$), that should remain down to arbitrarily low temperatures \cite{Alkurtass2016}.

%Entropy can be probed effectively in 3D macroscopic samples via measurements of heat capacity, but the heat capacities of single electrons or quasiparticles are much too small to measure directly; even the 2D sheet of quasiparticles in $\nu = \frac{5}{2}$ fractional quantum Hall samples has a heat capacity that vanishes in comparison to that of the host crystal.  Rather than attempt to resolve such infinitesimal signals, the problem can be avoided by converting changes in entropy to changes in charge \textemdash a quantity that is easily detected at the single particle level.

%Unlike the $\nu = \frac{5}{2}$ quasiparticles described in the theoretical work, the few-electron quantum dot states investigated here have an entropy that is well-understood from the spin degree of freedom \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.

%This shift, $\delta \mu$ as a function of $\delta T$, is the quantity probed directly in the experiment described below. From these measurements the entropies of the first three quantum dot levels are built up, demonstrating a direct entropy measurement is possible on a few-particle system. In the future, the method can be utilized to probe the nature of more exotic systems, such as topologically non-trivial Majorana and other non-Abelian states.

%Consider the filling of the first electron state, which has a single, unpaired spin-$\frac{1}{2}$ and, therefore, a degeneracy of 2.

%One expects identical field-dependent behaviors for $\Delta S_{0\rightarrow 1}$ and $\Delta S_{2\rightarrow 3}$ as long as $g \mu_{B} B_\parallel$ is less than the excited state energies

%The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} follows the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b). The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T$ up to \SI{250}{\milli\kelvin}. Measurements of $\Delta S$ are made at $\delta T = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.

%Although the extracted $\epsilon$ can be converted to gate-voltage-per-temperature units using a value for $\alpha$ measured separately (right axis of Fig.~\ref{fig:fig2}e), the entropy itself, $\Delta S$, is determined directly from the fit to $\delta g_{sens}$ without any additional calibration, and without knowing the precise value of $\delta T$.

### 2018-03-02 paper/draft_n_03-01.tex
mostly text edits. few small figure changes.

--- 2018-03-02 paper/draft.tex
@@
 \usepackage{siunitx}
+\sisetup{range-phrase=--}
+\sisetup{range-units=single}
 \usepackage{hyperref}
@@
 %%%%%%% intro material %%%%%%%%%
-\textbf{The thermodynamic properties of electronic systems offer important insights into the nature of their ground states, and can probe exotic quasiparticles that may emerge due to interactions or non-trivial topology.
-Systems that are difficult to clearly identify through standard conductance measurements may be characterized more precisely with a thermodynamic measurement.
-For example, the purported non-Abelian exchange statistics of Moore-Read quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, or of Majorana quasiparticles in a topological superconductor, could be clearly distinguished from the Abelian case by an entropy measurement \cite{Cooper2009, Ben-Shach2013, Smirnov2015}.
-Such measurements are typically based on bulk properties, like heat capacity, that are easily observed in macroscopic samples but are immeasurably small in systems that may consist of only a few electrons.
-Here, we develop a mesoscopic circuit to make direct entropy measurements of single- or few-quasiparticle states---in this case, the first, second, and third electron ground states in a GaAs quantum dot.
-This system is chosen for having well-known entropy based on simple spin states\cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
-The precision of this technique, quantifying the entropy of a single spin-$\frac{1}{2}$ to within 5\% of the expected value ($k_B \ln{2}$), shows its future potential for probing more exotic systems, from Majorana states to non-Fermi liquid Kondo states, that are clearly identified by their residual low-temperature entropy\cite{Alkurtass2016}.}
+\textbf{The thermodynamic properties of electronic systems offer important insights into the nature of their quantum mechanical ground states, especially those
+%, and can probe exotic quasiparticle statistics that emerge due to interactions or non-trivial topology.  Systems
+that are difficult to identify through standard conductance measurements.
+For example, the purported non-Abelian exchange statistics of quasiparticles in the $\nu = \frac{5}{2}$ fractional quantum Hall state, the presence of Majorana bound states in a topological superconductor, and entanglement in two-channel Kondo states could all be clearly identified by their residual low-temperature entropy \cite{Cooper2009, Ben-Shach2013, Smirnov2015, Hou2012, Alkurtass2016}.
+Traditionally, entropy measurements are based on bulk properties, such as heat capacity, that are easily observed in macroscopic samples but are immeasurably small in systems that consist of only a few electrons.
+In this work, we develop a mesoscopic circuit to measure directly the entropy of single- or few-quasiparticle states, studying the first, second, and third electron ground states in a GaAs quantum dot.
+This system is chosen for having well-understood statistics based on electron spin \cite{Tarucha1996, Ciorga2000, Duncan2000, Lindemann2002, Potok2003, Hofmann2016}.
+The precision of this technique, quantifying the entropy of a single spin-$\frac{1}{2}$ to within 5\% of the expected value ($k_B \ln{2}$), shows its potential for probing more exotic systems.}
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_1_annotated.pdf}
-        \caption{\label{fig:fig1} \textbf{Entropy measurement protocol.}  (a) Scanning electron micrograph of a device similar to the one measured.
+        \caption{\label{fig:fig1} \textbf{Measurement protocol}  (a) Scanning electron micrograph of a device similar to the one measured.
 Electrostatic gates (gold) define the circuit in a 2D electron gas (2DEG), with grey gates grounded.
@@
 Our approach is analogous to the milestone of spin-to-charge conversion achieved over a decade ago, in which the infinitesimal magnetic moments of a single spin were detected by transforming them into the presence or absence of an electron charge \cite{Elzerman2004, Ono2004}.
-Following this logic, we perform an entropy-to-charge conversion, making use of the Maxwell relation
+Following this example, we perform an entropy-to-charge conversion, making use of the Maxwell relation
 %
@@
 that connects changes in entropy, particle number, and temperature ($S$, $N$, and $T$, respectively) to changes in the chemical potential, $\mu$, a quantity that is simple to measure and control.
-The fixed pressure condition of Eq.~\ref{eqn:max} is met by working well below the Fermi temperature of the 2DEG, $T_F \sim \SI{5}{\kelvin}$, where degeneracy pressure dominates \cite{Landau1969}.
 
-The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to measure non-Abelian exchange of quasiparticles in  the $\nu = \frac{5}{2}$ state via their entropy
-%, quantified by the change in quasiparticle chemical potential with temperature
-\cite{Cooper2009,Ben-Shach2013}.
-Ref.~\onlinecite{Ben-Shach2013} proposes a strategy by which quasiparticle entropy could be deduced from the temperature-dependent shift of charging events on a local disorder potential, a thermodynamic equivalent of the measurements that established the $e/4$ quasiparticle charge\cite{Venkatachalam2011}.
-As a proof of principle in the viability of measuring localized quasiparticle entropy, and a demonstration of the high accuracy achievable by this technique, we investigate a well-understood system with localized fermions: a few-electron GaAs quantum dot.
+The Maxwell relation in Eq.~\ref{eqn:max} forms the basis of two theoretical proposals to measure non-Abelian exchange of Moore-Read quasiparticles in  the $\nu = \frac{5}{2}$ state via their entropy \cite{Cooper2009,Ben-Shach2013}.
+Reference~\onlinecite{Ben-Shach2013} proposes a strategy by which quasiparticle entropy could be deduced from the temperature-dependent shift of charging events on a local disorder potential; a thermodynamic equivalent of the measurements that established the $e/4$ quasiparticle charge\cite{Venkatachalam2011}.
+As a demonstration of the viability and the high accuracy achievable by this technique, we investigate a well-understood system with localized fermions in place of more exotic quasiparticles: a few-electron GaAs quantum dot.
 The entropies of the first three electron states in the dot are measured by the temperature-dependent charging scheme laid out in Ref.~\onlinecite{Ben-Shach2013}.
@@
 Applying more positive $V_p$ lowers $\mu_N$,  bringing the $N$th electron into the dot when $\mu_{N}$ drops below the Fermi level of the reservoir, $E_F$.
-The reservoir temperature, $T$, can be increased above the mixing chamber temperature, $T_{MC}$, by Joule heating from current $I_{heat}$ through the quantum point contact (``heater") on the left side.
+The reservoir temperature, $T$, can be increased above the GaAs substrate temperature by Joule heating from current, $I_{heat}$, through the quantum point contact (``heater") on the left side.
 Charge transitions on the dot appear as steps in the charge sensor conductance, $G_{sens}(V_p)$, thermally broadened by the reservoir temperature (Figs.~\ref{fig:fig1}b and c).
@@
 
-When $\mu_N$ shifts with temperature (Eq.~\ref{eqn:max}), $V_{mid}$ also shifts; it is the shift in $V_{mid}$ with temperature that forms the basis of our experiment (Fig.~\ref{fig:fig1}c).
-In practice, charge noise limits the accuracy to which $V_{mid}$ can be measured, so the measurement is done with a lock-in amplifier, oscillating the temperature using an AC $I_{heat}$ and measuring resultant oscillations in $G_{sens}$.
+When $\mu_N$ shifts with temperature, $V_{mid}$ also shifts; it is the shift in $V_{mid}$ with temperature that forms the basis of our experiment (Fig.~\ref{fig:fig1}c).
+In practice, charge noise limits the accuracy to which $V_{mid}$ can be measured.
+To overcome this, the measurement is done with a lock-in amplifier, oscillating the temperature using an AC $I_{heat}$ and measuring resultant oscillations in $G_{sens}$, which we label $\delta G_{sens}$.
 As seen in the insets of Figs.~\ref{fig:fig1}b and c, the lineshape of $\delta G_{sens}$ is perfectly antisymmetric when $\partial S/\partial N=0$, but asymmetric when $\partial S/\partial N \neq 0$.
@@
 The temperature-induced shift in the dot chemical potential with respect to reservoir $E_F$ can also be understood in terms of detailed balance.
-At $V_{mid}$, with equal probabilities for $N$ and $N-1$ electrons on the dot, the tunnel rates $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$ must also be equal.
-These rates depend on the number of available states in the tunneling process, and therefore on the degeneracies of the $N-1$ and $N$ ground states \cite{Beenakker1991, Gustavsson2009}.
-The condition $\Gamma_{in} = \Gamma_{out}$ leads to a simple relationship between the degeneracies, $d_{N-1}$ and $d_{N}, of the $N-1$ and $N$ electron states and the thermally broadened Fermi function $f$: $d_{N-1}/d_{N}=f/(1-f)$.
-Using the Boltzman entropy, $S_{N}=k_{B} \ln{d_N}$, and the form of the Fermi function, this relationship becomes $\Delta S_{N-1\rightarrow N}= (\mu_{N}-E_F)/T$, clearly demonstrating the connection between entropy, temperature, and the shift in $\mu_N$ relative to $E_F$ at $V_{mid}$.
+At $V_{mid}$, where probabilities for $N$ and $N-1$ electrons on the dot are equal, the tunnel rates $\Gamma_{in}=\Gamma_{N-1\rightarrow N}$ and $\Gamma_{out}=\Gamma_{N\rightarrow N-1}$ must also be equal.
+These rates depend on the number of available states in the tunneling process, and therefore on the degeneracies, $d_{N-1}$ and $d_{N}$, of the $N-1$ and $N$ ground states \cite{Beenakker1991, Gustavsson2009}.
+The condition $\Gamma_{in} = \Gamma_{out}$ leads to a simple relationship between degeneracy and the thermally broadened Fermi function, $f(\mu_{N}-E_{F}, T)$: $d_{N-1}/d_{N}=f/(1-f)$.
+Using the Boltzman entropy, $S_{N}=k_{B} \ln{d_N}$, this relationship becomes $\Delta S_{N-1\rightarrow N}= (\mu_{N}-E_F)/T$, clearly demonstrating the connection between entropy, temperature, and the shift in $\mu_N$ at $V_{mid}$.
 Previous experiments have explored the relationship between tunnel rates and degeneracy using time-resolved transport spectroscopy and by coupling quantum dots to atomic force cantilever oscillations \cite{Cockins2010, Bennett2010, Beckel2014, Hofmann2016}.
-The approach presented here is a thermodynamic equivalent of these, and extends entropy measurements to a much wider set of applications where tunnelling processes may not be possible to observe in real-time.
+The approach presented here is a thermodynamic analogue, and extends entropy measurements to a wider set of applications where tunneling processes may not be observable in real-time.
 
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_2.pdf}
-        \caption{\label{fig:fig2} \textbf{Entropy measurement for a single spin $\frac{1}{2}$.} (a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater.
+        \caption{\label{fig:fig2} \textbf{Entropy measurement for a single spin-$\mathbf{\frac{1}{2}}$} (a) Charge sensor data for $N=0 \rightarrow 1$ at two temperatures set by DC current through the QPC heater.
 (b) Transition width, $\Theta$, was linear in $T_{MC}$ above 100 mK, for $I_{heat}=0$.
@@
 (d) $\Theta$ grows with DC current through the QPC heater.
-A fit to $T = a\sqrt{T^{2}_{MC}+b I^2_{heat}R_{QPC}}$ is used to convert between $I_{heat}$ and $\delta T$\cite{Mittal1996}.
+A fit to $T = a\sqrt{T^{2}_{MC}+b I^2_{heat}R_{QPC}}$ is used to convert between $I_{heat}$ and $\delta T$, where $T_{MC}$ is the mixing chamber temperature\cite{Mittal1996}.
 (e)  Entropy measurements were independent of the magnitude of $I_{heat}$ oscillations over a large range.
@@
 
-%To proceed with the entropy measurement,
-The dot was tuned such that the source was weakly tunnel coupled to the reservoir with the drain closed.
+The dot was tuned such that the source was weakly tunnel-coupled to the reservoir with the drain closed.
 The conductance of the charge sensor was tuned to $G_{sens}{\sim}e^2/h$, where it was most sensitive to charge on the dot.
-The addition of the first electron to the dot was marked by a decrease in $G_{sens}$ that is well described as a thermally-broadened two-level transition (Fig.~\ref{fig:fig2}a):
+The addition of the first electron to the dot was marked by a decrease in $G_{sens}$ that is consistent with a thermally-broadened two-level transition (Fig.~\ref{fig:fig2}a):
 %
@@
         G_{sens}(V_p,\Theta) &= G_0 \tanh\left(\frac{V_p - V_{mid}(\Theta)}{2\Theta}\right)  \\
-                        &\quad + G_1 V_{G} + G_2 \nonumber
+                        &\quad + \gamma_1 V_{p} + G_2 \nonumber
 \end{align}
 %
-where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening (expressed in units of gate voltage), $\alpha\equiv d \mu_{N}/d V_p$ is the lever arm,  $G_1$ reflects the cross capacitance between the charge sensor and plunger gate, and $G_2$ is an offset.
-Figure~\ref{fig:fig2}a shows two such transition curves with thermal broadening set by the current, $I_{heat}$ through the heater.
-For $I_{heat}=0$, $\Theta$ followed $T_{MC}$ down to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b), validating the approximation of thermal broadening used throughout this experiment.
+where $G_0$ quantifies the sensor sensitivity, $\Theta = \frac{k_B T}{\alpha e}$ is the thermal broadening expressed in units of gate voltage, $\alpha\equiv d \mu_{N}/d V_p$ is the lever arm,  $\gamma_1$ reflects the cross capacitance between the charge sensor and plunger gate, and $G_2$ is an offset.
+Figure~\ref{fig:fig2}a shows two such transition curves with thermal broadening set by $I_{heat}$.
+For $I_{heat}=0$, $\Theta$ followed $T_{MC}$ down to \SI{\sim100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b), validating the approximation of thermal broadening used throughout this experiment.
 
 The data in Fig.~\ref{fig:fig2}c, and corresponding fits, illustrate a measurement of $\Delta S_{0\rightarrow 1}$ across the $0 \rightarrow 1$ electron transition.
-The lock-in measurement of $\delta G_{sens}$ due to temperature oscillations $\delta T$ yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c, corresponding the difference between the two $G_{sens}$ curves in Fig.~\ref{fig:fig2}a.
+The lock-in measurement of $\delta G_{sens}$, due to temperature oscillations $\delta T$, yields the characteristic peak-dip structure seen in Fig.~\ref{fig:fig2}c.
+%, corresponding to the difference between the two $G_{sens}$ curves in Fig.~\ref{fig:fig2}a.
 The expected lineshape of such a curve is $\delta G_{sens} = \frac{\partial G_{sens}}{\partial T} \delta T$, with $G_{sens}$ defined by Eq.
 \ref{eqn:g-sens}.
-This lineshape depends in a simple way on $\Delta S$, recognizing (via Eq.~\ref{eqn:max}) that $\frac{\partial V_{mid}}{\partial \Theta}=\frac{1}{k_B}\frac{\partial \mu}{\partial T} =\frac{1}{k_B}\Delta S_{N-1\rightarrow N}$:
+This lineshape depends explicitly on $\Delta S$, recognizing (via Eq.~\ref{eqn:max}) that $\frac{\partial V_{mid}}{\partial \Theta}=\frac{1}{k_B}\frac{\partial \mu}{\partial T} =\frac{1}{k_B}\Delta S_{N-1\rightarrow N}$:
 %
@@
 %
+\noindent As expected  from Figs.~\ref{fig:fig1}b and c, $\delta G_{sens}(V_p)$ is antisymmetric around $V_{mid}$ for $\Delta S=0$, and asymmetric for $\Delta S\neq 0$.
+A fit of the data in Fig.~\ref{fig:fig2}c to Eq.~\ref{eqn:dg-sens} yields $\Delta S_{0\rightarrow 1}=(1.02 \pm 0.03) k_B \ln{2}$, closely matching the expected $\Delta S_{0 \rightarrow 1} = S_1 - S_0 =k_B\ln{2}$ for transitions between an empty dot with zero entropy ($S_0=0$) and the two-fold degenerate 1-electron state ($d_1=2$) with entropy $S_1=k_B \ln{2}$.
 
-\noindent As expected  from Figs.~\ref{fig:fig1}b,c, $\delta G_{sens}(V_p)$ is antisymmetric around $V_{mid}$ for $\Delta S=0$, and asymmetric for $\Delta S\neq 0$.
-A fit of the data in Fig.~\ref{fig:fig2}c to Eq.~\ref{eqn:dg-sens} yields $\Delta S_{0\rightarrow 1}=(1.02 \pm 0.03) k_B \ln{2}$, closely matching the expected $\Delta S_{0 \rightarrow 1} = S_1 - S_0 =k_B\ln{2}$ for transitions between an empty dot ($S_0=0$) and the two-fold degenerate 1-electron state ($d_1=2$) with entropy $S_1=k_B \ln{2}$.
-
-It is important to note that extracting $\Delta S$ from fits to Eq.~\ref{eqn:dg-sens} can be done just from the asymmetry of the lineshape, with no calibration of measurement parameters (such as $\delta T$ or the lever arm $\alpha$) required.
-We can, however, estimate $\delta T$ and $\alpha$ by measuring $T(I_{heat})$, using a DC $I_{heat}$ to raise the reservoir temperature and fitting to Eq.~\ref{eqn:g-sens}  (Fig.~\ref{fig:fig2}d); the calibration holds for AC currents below 100 Hz.
+It is important to note that $\Delta S$ is extracted from fits to Eq.~\ref{eqn:dg-sens} based solely on the asymmetry of the lineshape, with no calibration of measurement parameters (such as $\delta T$ or the lever arm $\alpha$) required.
+We can, however, estimate $\alpha$ and $\delta T$ by determining $\Theta$ from fits to Eq.~\ref{eqn:g-sens} for varying substrate temperature (Fig.~\ref{fig:fig2}b) and $I_{heat}$ (Fig.~\ref{fig:fig2}d).
 Measurements of $\Delta S$ remained constant over a broad range of $\delta T$ (Fig.~\ref{fig:fig2}e), as expected for temperatures low enough not to excite orbital degrees of freedom on the dot.
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_3.pdf}
-        \caption{\label{fig:fig3} \textbf{Magnetic field dependence.} (a) Changes in entropy for $N=0 \rightarrow 1$ and $2 \rightarrow 3$ transitions, overlaid to highlight similar behaviors.
-Each data point corresponds to a single $\delta G_{sens}(V_p)$ fit; multiple scans are carried out at various parallel magnetic fields.
+        \caption{\label{fig:fig3} \textbf{Magnetic field dependence} (a) Changes in entropy for $N=0 \rightarrow 1$ and $2 \rightarrow 3$ transitions, overlaid to highlight similar behaviors.
+Each data point corresponds to a single $\delta G_{sens}(V_p)$ fit; multiple scans are carried out at various in-plane magnetic fields.
 (b) and (c) Characteristic $\delta G_{sens}$ traces from which the data in (a) were extracted.
@@
 Dashed line at $V_{SD}$ = \SI{700}{\micro\electronvolt} shows where data in (f) are taken.
-(f) Fixed bias data showing fits to Zeeman splitting of the ground state (dashed lines) from which $g = -0.42 \pm 0.01$ is extracted.}
+(f) Fixed bias data showing fits to Zeeman splitting of the ground state (dashed lines) from which $|g| = 0.42 \pm 0.01$ is extracted.}
 \end{figure}
@@
 Figure \ref{fig:fig3}a compares $\Delta S(B_\parallel)$ for the $0 \rightarrow1 $ and $2 \rightarrow 3$ transitions, both of which correspond to transitions from total spin zero to total spin one-half.
-The entropies of the $\ket{S=1/2}$ states go to zero as when Zeeman splitting lifts the spin degeneracy, given by the Gibbs entropy for a two-level system:
+The entropies of the 1- and 3-electron states go to zero as Zeeman splitting lifts the spin degeneracy, following the Gibbs entropy for a two-level system:
 %
@@
 Fits to Eq.~\ref{eqn:gibbs}, with the ratio $g/T$ and an added scaling $\Delta S(B=0)$ as free parameters, give $\Delta S_{0 \rightarrow 1}(B=0)=(0.94 \pm 0.03) k_B \ln{2}$ and $\Delta S_{2 \rightarrow 3}(B=0)=(0.98 \pm 0.02) k_B \ln{2}$ (Fig.~\ref{fig:fig3}), and reflect the collapse to zero at high field where spin degeneracy is broken.
-This collapse can also be seen qualitatively, as a crossover from asymmetric to antisymmetric lineshapes for $\delta G_{sens}(V_p)$ (Figs.~\ref{fig:fig3}b and c).
+This collapse can also be seen qualitatively, in the crossover from asymmetric to antisymmetric lineshapes of $\delta G_{sens}(V_p)$ (Figs.~\ref{fig:fig3}b and c).
 Estimating an average $T$ for each data set using the calibration in Fig.~\ref{fig:fig2}d yields $|g|=0.48 \pm 0.02$ and $|g|=0.44 \pm 0.01 $ for the $0\rightarrow 1$ and $2\rightarrow 3$ transitions, respectively.
@@
         \includegraphics[width=1.0\columnwidth]{../figures/figure_4.pdf}
-        \caption{\label{fig:fig4}  \textbf{Entropic signature of a singlet-triplet crossing.} (a) Change in entropy, extracted from $\delta G_{sens}$ fits at varying parallel field.
-Dashed line shows fit to Eq.~\ref{eqn:gibbs}.
+        \caption{\label{fig:fig4}  \textbf{Entropic signature of a singlet-triplet crossing} (a) Change in entropy, extracted from $\delta G_{sens}$ fits at varying in-plane field.
+Dashed line shows fit to Eq.~\ref{eqn:gibbs}, allowing for an offset from $\Delta S=0$ away from the degenerate points to compensate for non-linearities in the charge sensor.
 Values stated for $\Delta S$ are with respect to the vertical offset apparent in the data.
@@
 Dashed line at $V_{SD}$ = \SI{1250}{\micro\electronvolt} shows where data in (f) are taken.
-(f) Fixed bias data in parallel field.
-Triplet level is split into $\ket{T_+}$ and $\ket{T_0}$ levels with a third $\ket{T_-}$ level not visible here.
-At \SI{8.4}{\tesla} $\ket{T_+}$ becomes degenerate with $\ket{S}$.
-$g=-0.40\pm0.04$ is determined using $\ket{T_0}$ and $\ket{T_+}$ fits (dashed).}
+(f) Fixed bias data in in-plane field.
+Triplet level is split into $\ket{\mathcal{T_+}}$ and $\ket{\mathcal{T_0}}$ levels with a third $\ket{\mathcal{T_-}}$ level not visible here.
+At \SI{8.4}{\tesla} $\ket{\mathcal{T_+}}$ becomes degenerate with $\ket{\mathcal{S}}$.
+$|g|=0.40\pm0.04$ is determined using $\ket{\mathcal{T_0}}$ and $\ket{\mathcal{T_+}}$ fits (dashed).}
 \end{figure}
 
-The $1\rightarrow 2$ transition can be understood as the inverse of the $0 \rightarrow 1$ transition for $B_\parallel < \SI{5}{\tesla}$, comparing Figs~\ref{fig:fig3}a and \ref{fig:fig4}a.
-For relatively low fields, the 2-electron ground state remains a spin singlet ($\ket{S=0}$) with zero entropy, while the 1-electron entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
-At higher fields, the 1-electron ground state remains non-degenerate while the 2-electron ground state gains a two-fold degeneracy when the singlet and triplet \ket{T_+} states cross.
-This singlet-triplet crossing is seen in bias spectroscopy data (Fig.~\ref{fig:fig4}f) at \SI{8.4}{\tesla}, and in the appearance of a peak in $\Delta S_{1\rightarrow 2}$ at \SI{9}{\tesla}.
+The $1\rightarrow 2$ transition can be understood as the inverse of the $0 \rightarrow 1$ transition for $B_\parallel < \SI{5}{\tesla}$, comparing Figs.~\ref{fig:fig3}a and \ref{fig:fig4}a.
+For relatively low fields, the 2-electron ground state remains a spin singlet with zero entropy, while the 1-electron entropy goes from $k_B\ln{2}$ to zero due to Zeeman splitting.
+At higher fields, the 1-electron ground state remains non-degenerate while the 2-electron ground state gains a two-fold degeneracy when the singlet $\ket{\mathcal{S}}$ and triplet \ket{\mathcal{T_{+}}} states cross.
+This singlet-triplet crossing is seen in bias spectroscopy data (Fig.~\ref{fig:fig4}f) at \SI{8.4}{\tesla}, and in the appearance of a peak in $\Delta S_{1\rightarrow 2}$ at \SI{9}{\tesla} (Fig.~\ref{fig:fig4}a).
 The discrepancy between the fields required to drive the singlet-triplet degeneracy in Figs.~\ref{fig:fig4}a and f can be explained by the change in dot configuration from one to two open tunnel barriers.
 
-The field-dependent entropy measurement for the $1 \rightarrow 2$ transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{\ket{S}/\ket{T}}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
-The fit in Fig.~\ref{fig:fig4}a allows for an offset from $\Delta S=0$ away from the degenerate points to compensate for non-linearities in the charge sensor.
+The field-dependent entropy measurement for the $1 \rightarrow 2$ transition can again be fit using Eq.~\ref{eqn:gibbs}, with probabilities as before for the 1-electron states and $p_{\ket{\mathcal{S}}/\ket{\mathcal{T_{+}}}}(B_\parallel, T) = (1+ e^{\mp \frac{g\mu_B B_\parallel - \Delta_{ST}}{k_B T}})^{-1}$ for the 2-electron states, where $\Delta_{ST}$ is the singlet-triplet splitting at zero field.
 From the fit, we find $\Delta S_{1\rightarrow 2}$ at the two-fold degenerate points, $B=0$ and \SI{9}{\tesla}, are $-(1.01\pm0.03) k_B \ln{2}$ and $(1.04 \pm 0.04) k_B \ln{2}$, respectively.
-The extracted g-factor, $g = 0.47 \pm 0.02$, from the peak at $B=0$ is consistent with the $0\rightarrow 1$ transition.
-At the high-field singlet-triplet degeneracy we find $g = 0.69 \pm 0.04$, an unexpectedly high g-factor that may be explained by a shift of the $\ket{T_0}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work \cite{Szafran2004}.
-The high quality of the Gibbs entropy fit, over a large range of field, confirms that the measured signal is the change in entropy $\Delta S$, and illustrates a tuneable degeneracy.
+The extracted g-factor, $|g| = 0.47 \pm 0.02$, from the peak at $B=0$ is consistent with the $0\rightarrow 1$ transition.
+At the high-field singlet-triplet degeneracy we find $|g| = 0.69 \pm 0.04$, an unexpectedly high g-factor that is explained by a shift of the $\ket{\mathcal{T_0}}$ state with magnetic field, as seen in Fig.~\ref{fig:fig4}f and previous work \cite{Szafran2004}.
+%The high quality of the Gibbs entropy fit, over a large range of field, confirms that the measured signal is the change in entropy $\Delta S$, and illustrates a tunable degeneracy.
 
 %%% conclusion %%%
-%In conclusion, we have presented a direct entropy measurement of the few-particle states in a few electron states in a GaAs was quantified within 5\% of the expected $k_B \ln{2}$.
-Future work may take advantage of this strategy to search for thermodynamic signatures of quantum states with non-trival correlations or topology, eliminating the uncertainty found in typical transport data.
+The measurement protocol outlined above can be used to quantify entropy in a wide range of mesoscopic systems.
+The only requirements are variable temperature, measurable $\delta \mu$, and $k_B \delta T$  smaller than the splitting between ground and excited states of the system.
+Measurements of localized states in more complex systems are the obvious extension of our work.
+The entropy of $\nu=5/2$ quasiparticles localized on potential disorder could be measured with a capacitive charge sensor, analogous to Ref.~\onlinecite{Venkatachalam2011}, or using antidots as in Ref.~\onlinecite{Kataoka1999}.
+Capacitively coupling a charge sensor to quantum wires believed to host Majorana bound states and carrying out the measurement described above would allow for the unambiguous identification of their non-Abelian character \cite{Suominen2017, Nichele2017, CITEOTHERS}.
+Or, entanglement entropy in the two-channel Kondo state could be measured by coupling two additional finite-size reservoirs to the quantum dot in Fig.~\ref{fig:fig1}a \cite{Potok2007}.
+In each of these systems, as in the system studied here, the defining statistical characteristics are manifest in the low temperature entropy.
 
-\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined in a separate chip/measurement) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second} respectively.
+\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second} respectively, determined in a separate measurement.
 Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability in the device.
@@
 
+% add sentence about why the charge sensor does not heat the dot as well
 The measurement was carried out in a dilution refrigerator with a two-axis magnet.
 The 2DEG was aligned parallel to the main axis with the second axis used to compensate for sample misalignment.
-In practice, perpendicular fields up to \SI{100}{\milli\tesla} showed no effect on our data.
-[ADD DESCRIPTION OF THE CHANGE OF CONFIGURATION FOR BIAS SPECTROSCOPY, AND DETAILS OF SETTINGS FOR ENTROPY MEASUREMENT]  Charge sensor conductance was measured using a DC voltage bias of \SI{200}{\micro\volt}, with the current, measured at DC ($I_{sens}$) using an analog-digital convertor and at AC ($\delta I_{sens}$) using a lock-in amplifier.
-The DC conductance reported here is $G_{sens}=I_{sens}/V_{sens}$ while $\delta G_{sens}$ is $G_{sens}=(\delta I_{sens})/V_{sens}$.
+In practice, out-of-plane fields up to \SI{100}{\milli\tesla} showed no effect on our data.
+A retuning of the quantum dot gates was necessary to capture the bias spectroscopy data in Figs.~\ref{fig:fig3}d,e and \ref{fig:fig4}e,f.
+The rightmost gate (Fig.~\ref{fig:fig1}a) on the quantum dot was used to tune between the one and two lead configurations, for the entropy and bias spectroscopy measurements respectively.
+This tuning had a significant effect on the shape of the potential well, accounting for variations in parameters such as $g$ and $\Delta_{ST}$ between the two measurement configurations.
+Charge sensor conductance was measured using a DC voltage bias of \SIrange{200}{350}{\micro\volt}; we find that Joule heating through the sensor does not affect our reservoir temperatures up to $V_{sens}\sim\SI{500}{\micro\volt}$.
+The DC current ($I_{sens}$) was measured using an analog-digital convertor while AC current ($\delta I_{sens}$) was measured using a lock-in amplifier.
+The DC conductance reported here is $G_{sens}=I_{sens}/V_{sens}$ while the oscillations are defined as $\delta G_{sens}=(\delta I_{sens})/V_{sens}$.
 
@@
 Except where noted, measurements of $\Delta S$ were made at $\delta T \sim $ \SI{50}{\milli\kelvin}, although the error bars in Fig.~\ref{fig:fig2} demonstrate that the measurements would have been just as accurate with $\delta T$ set to \SI{30}{\milli\kelvin}.
-
-%The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g-sens} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
-The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T$ up to \SI{250}{\milli\kelvin}.
+The fixed pressure condition of Eq.~\ref{eqn:max} is met by working well below the Fermi temperature of the 2DEG, $T_F \sim \SI{5}{\kelvin}$, where degeneracy pressure dominates \cite{Landau1969}.
 
@@
 %%% old sentences %%%
+
+%In conclusion, we have presented a direct entropy measurement of the few-particle states in a few electron states in a GaAs was quantified within 5\% of the expected $k_B \ln{2}$.
+Future work may take advantage of this strategy to search for thermodynamic signatures of quantum states with non-trival correlations or topology, eliminating the uncertainty found in typical transport data.
+
+%The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g-sens} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b).
+The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T$ up to \SI{250}{\milli\kelvin}.
 
